### 2021-06-21 supp_file/supp_file.Rmd
as

---
title: "Supplemental File"
author: "Maxwel Coura Oliveira"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE
)
```

```{r message=FALSE, include=FALSE}
# Packages
options(scipen = 999)
library(tidyverse)
library(kableExtra)

```

```{r}
read_csv("bf.csv") %>% 
  kableExtra::kable(., booktabs = T, longtable = T, 
                    caption = "Bayes Factor interpretation",
                    linesep = "") %>%
  kable_styling(latex_options = c("striped", "repeat_header")) 
```

```{r echo=FALSE}
read_csv("inswath_bf.csv") %>% 
  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
  kableExtra::kable(., booktabs = T, longtable = T, 
                    caption = "Treatment contrasts for inswath spray solution deposition. Bayes Factor is used to test contrast hypothesis",
                    linesep = "") %>%
  kable_styling(latex_options = c("striped", "repeat_header")) 
```

## AUC Bayes Factor contrasts

```{r echo=FALSE}
read_csv("auc_bf.csv") %>% 
  mutate_if(is.double, ~round(., 2)) %>% 
  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
  kableExtra::kable(., booktabs = T, longtable = T, 
                    caption = "Treatment contrasts for Area Under the Curve. Bayes Factor is used to test contrast hypothesis",
                    linesep = "") %>%
  kable_styling(latex_options = c("striped", "repeat_header")) 
```

### 2021-06-21 supp_file/table.Rmd
as

---
title: "Supplemental File"
author: "Maxwel Coura Oliveira"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE
)
```

```{r message=FALSE}
# Packages
options(scipen = 999)
library(tidyverse)
library(reactable)
library(webshot2)
library(reactablefmtr)
```

$$\\[0.25in]$$
This is a supplemental material for the manuscript entitled: "XXXX". The Bayes Factor (BF) interpretation of Table 1 is based on Lee and Wagenmakers (2013). The H0 and H1 mean that treatments are the same or different, respectively.

$$\\[0.1in]$$

```{r}
read_csv("data/bf.csv") %>% 
  reactable(., theme = fivethirtyeight(), 
            filterable = TRUE,
            resizable = TRUE,
            searchable = FALSE,
            wrap = TRUE,
            defaultPageSize = 11,
            defaultColDef = colDef(minWidth = 200)) %>% 
  add_title("Table 1. Bayes Factor interpretation", font_size = 15)
```

$$\\[0.1in]$$
The treatment contrasts of inswath spray solution deposition are compared (Table 2). See the BF and make an interpretation based on Table 1.

$$\\[0.1in]$$

```{r}
read_csv("data/inswath_bf.csv") %>% 
  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
  dplyr::select(-"Std_Difference") %>% 
  reactable(., theme = fivethirtyeight(),
            filterable = FALSE,
            resizable = TRUE,
            pagination = FALSE,
            wrap = TRUE,
            groupBy = "Level1",
            searchable = FALSE,
            defaultPageSize = 20,
            showSortable = TRUE,
            columns = list(
            Level1 = colDef(filterable = TRUE),
            Level2 = colDef(filterable = TRUE),
            BF = colDef(
              #cell = #function(value) {
#                if (value > 1) paste0("+", value) 
#                else value
#                },
              style = function(value) {
                color <- if (value > 1) {
                  "#008000"
                  } else if (value < 1) {
                    "#e00000"
                  }
                list(fontWeight = 600, color = color)}),
            Difference = colDef(align = "center", 
                                cell = data_bars_pos_neg(., 
                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
  add_title("Table 2. Treatment contrasts for inswath spray solution deposition. Bayes Factor is used to test contrast hypothesis", font_size = 15)
```

$$\\[0.1in]$$
The treatment contrasts of Area Under the Curve are compared (Table 3). See the BF and make an interpretation based on Table 1.
$$\\[0.1in]$$

```{r}
read_csv("data/auc_bf.csv") %>% 
  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
  dplyr::select(-"Std_Difference") %>% 
  mutate_if(is.double, ~round(.,2)) %>% 
  reactable(., theme = fivethirtyeight(),
            filterable = FALSE,
            resizable = TRUE,
            pagination = FALSE,
            wrap = TRUE,
            groupBy = "Level1",
            searchable = FALSE,
            defaultPageSize = 20,
             showSortable = TRUE,
            columns = list(
            Level1 = colDef(filterable = TRUE),
            Level2 = colDef(filterable = TRUE),
            BF = colDef(
              #cell = #function(value) {
#                if (value > 1) paste0("+", value) 
#                else value
#                },
              style = function(value) {
                color <- if (value > 1) {
                  "#008000"
                  } else if (value < 1) {
                    "#e00000"
                  }
                list(fontWeight = 600, color = color)}),
#            BF = colDef(align = "center",
#                        cell = color_tiles(., colors = ifelse(. > 1.00, "blue",
#                                                         "red"))),
            Difference = colDef(align = "center", 
                                cell = data_bars_pos_neg(., 
                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
  add_title("Table 3. Treatment contrasts for Area Under the Curve. Bayes Factor is used to test contrast hypothesis", font_size = 15)
```

```{r}
read_csv("data/bf_dv10.csv") %>% 
  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
  dplyr::select(-"Std_Difference") %>% 
  mutate_if(is.double, ~round(.,2)) %>% 
  reactable(., theme = fivethirtyeight(),
            filterable = FALSE,
            resizable = TRUE,
            pagination = FALSE,
            wrap = TRUE,
            groupBy = "Level1",
            searchable = FALSE,
            defaultPageSize = 20,
             showSortable = TRUE,
            columns = list(
            Level1 = colDef(filterable = TRUE),
            Level2 = colDef(filterable = TRUE),
            BF = colDef(
              #cell = #function(value) {
#                if (value > 1) paste0("+", value) 
#                else value
#                },
              style = function(value) {
                color <- if (value > 1) {
                  "#008000"
                  } else if (value < 1) {
                    "#e00000"
                  }
                list(fontWeight = 600, color = color)}),
#            BF = colDef(align = "center",
#                        cell = color_tiles(., colors = ifelse(. > 1.00, "blue",
#                                                         "red"))),
            Difference = colDef(align = "center", 
                                cell = data_bars_pos_neg(., 
                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
  add_title("Table 3. Treatment contrasts for DV10. Bayes Factor is used to test contrast hypothesis", font_size = 15)
```

```{r}
read_csv("data/bf_dv50.csv") %>% 
  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
  dplyr::select(-"Std_Difference") %>% 
  mutate_if(is.double, ~round(.,2)) %>% 
  reactable(., theme = fivethirtyeight(),
            filterable = FALSE,
            resizable = TRUE,
            pagination = FALSE,
            wrap = TRUE,
            groupBy = "Level1",
            searchable = FALSE,
            defaultPageSize = 20,
             showSortable = TRUE,
            columns = list(
            Level1 = colDef(filterable = TRUE),
            Level2 = colDef(filterable = TRUE),
            BF = colDef(
              #cell = #function(value) {
#                if (value > 1) paste0("+", value) 
#                else value
#                },
              style = function(value) {
                color <- if (value > 1) {
                  "#008000"
                  } else if (value < 1) {
                    "#e00000"
                  }
                list(fontWeight = 600, color = color)}),
#            BF = colDef(align = "center",
#                        cell = color_tiles(., colors = ifelse(. > 1.00, "blue",
#                                                         "red"))),
            Difference = colDef(align = "center", 
                                cell = data_bars_pos_neg(., 
                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
  add_title("Table 4. Treatment contrasts for DV50. Bayes Factor is used to test contrast hypothesis", font_size = 15)
```

```{r}
read_csv("data/bf_dv90.csv") %>% 
  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
  dplyr::select(-"Std_Difference") %>% 
  mutate_if(is.double, ~round(.,2)) %>% 
  reactable(., theme = fivethirtyeight(),
            filterable = FALSE,
            resizable = TRUE,
            pagination = FALSE,
            wrap = TRUE,
            groupBy = "Level1",
            searchable = FALSE,
            defaultPageSize = 20,
             showSortable = TRUE,
            columns = list(
            Level1 = colDef(filterable = TRUE),
            Level2 = colDef(filterable = TRUE),
            BF = colDef(
              #cell = #function(value) {
#                if (value > 1) paste0("+", value) 
#                else value
#                },
              style = function(value) {
                color <- if (value > 1) {
                  "#008000"
                  } else if (value < 1) {
                    "#e00000"
                  }
                list(fontWeight = 600, color = color)}),
#            BF = colDef(align = "center",
#                        cell = color_tiles(., colors = ifelse(. > 1.00, "blue",
#                                                         "red"))),
            Difference = colDef(align = "center", 
                                cell = data_bars_pos_neg(., 
                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
  add_title("Table 5. Treatment contrasts for DV90. Bayes Factor is used to test contrast hypothesis", font_size = 15)
```

#### Reference

- Lee M.D. and Wagenmakers E.J. (2014) Bayesian Cognitive Modeling. Cambridge University Press. ISBN: 9781107018457, 1107018455

### 2021-06-21 analysis/bayes_droplet.Rmd
as

---
title: "bayes_droplet"
author: "Maxwel Coura Oliveira"
date: "6/11/2021"
output: html_document
---

```{r}
library(tidyverse)
library(emmeans)
library(brms)
library(bayestestR)
library(modelbased)
library(ggtext)
library(patchwork)
library(ggthemes)
```

```{r}
readxl::read_excel("droplet_size_data.xlsx") %>% 
  janitor::clean_names() %>% 
  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
  group_by(solution, nozzle) %>% 
  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
  mutate(x200 = x200/100) %>% 
  mutate(rep = row_number()) -> droplet
```

# dv10

```{r eval= FALSE}
model10 <- brm(`dv10` ~ 1,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model11 <- brm(`dv10` ~ solution,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model12 <- brm(`dv10` ~ solution + nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model13 <- brm(`dv10` ~ solution * nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

# dv50

```{r message = FALSE}
model13 <- brm(`dv10` ~ solution * nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

```{r}
library(bayestestR)
#bayesfactor_models(model11, model12, model13, denominator = model10)
# There are extreme evidence for model13 (interaction)
```

```{r}
droplet %>% 
  group_by(nozzle, solution) %>% 
  summarise(mean = mean(`dv10`), median = median(`dv10`))
```

```{r}
rg <- ref_grid(model13)
em <- emmeans(rg, ~ nozzle * solution, type = "response")
summary(em, point.est = mean)
```

```{r}
emmeans1 <- emmeans(model13, ~ nozzle * solution, cont="pairwise", type = "response")
```

```{r}
options(scipen = 999)
estimate_contrasts(model13, test = "bf") %>% 
  as_tibble() -> bf_dv10
write_csv(x = bf_dv10, file = "bf_dv10.csv")
```

# DV 50

```{r}
model21 <- brm(`dv50` ~ solution,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model22 <- brm(`dv50` ~ solution + nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))

model23 <- brm(`dv50` ~ solution * nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

```{r}
# model comparison
bayesfactor_models(model22, model23, denominator = model21)
```

```{r}
rg <- ref_grid(model23)
em <- emmeans(rg, ~ nozzle * solution, type = "response")
summary(em, point.est = mean)
```

```{r}
emmeans2 <- emmeans(model23, ~ nozzle * solution, cont="pairwise", type = "response")
```

```{r}
estimate_contrasts(model23, test = "bf")
```

```{r}
options(scipen = 999)
estimate_contrasts(model23, test = "bf") %>% 
  as_tibble() -> bf_dv50
#write_csv(x = bf_dv50, file = "bf_dv50.csv")
```

# DV 90

```{r}
model33 <- brm(`dv90` ~ solution * nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

```{r}
# model comparison
#bayesfactor_models(model32, model33, denominator = model31)
```

```{r}
rg <- ref_grid(model33)
em <- emmeans(rg, ~ nozzle * solution, type = "response")
summary(em, point.est = mean)
```

```{r}
emmeans3 <- emmeans(model33, ~ nozzle * solution, cont="pairwise", type = "response")
```

```{r}
estimate_contrasts(model33, test = "bf")
```

```{r}
estimate_contrasts(model33, test = "bf") %>% 
  as_tibble() -> bf_dv90
write_csv(x = bf_dv90, file = "bf_dv90.csv")
```

# RS

```{r}
model43 <- brm(rs ~ solution * nozzle,
                  family = hurdle_gamma(link = "log", 
                                        link_shape = "log", 
                                        link_hu = "logit"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.1, 0.5, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

```{r}
# model comparison
#bayesfactor_models(model32, model33, denominator = model31)
```

```{r}
rg <- ref_grid(model43)
em <- emmeans(rg, ~ nozzle * solution, type = "response")
summary(em, point.est = mean)
```

```{r}
emmeans4 <- emmeans(model43, ~ nozzle * solution, cont= "pairwise", type = "response")
```

```{r}
estimate_contrasts(model43, test = "bf")
```

# <200

# RS

```{r}
model53 <- brm(`x200` ~ solution * nozzle,
                  family = Beta(link = "logit", link_phi = "log"),
               warmup = 1000, iter = 2000, chains = 4,
               prior = set_prior("student_t(0.1, 0.5, 2)", class = "b"),
                  data = droplet, save_pars = save_pars(all = TRUE))
```

```{r}
# model comparison
#bayesfactor_models(model32, model33, denominator = model31)
```

```{r}
rg <- ref_grid(model53)
em <- emmeans(rg, ~ nozzle * solution, type = "response")
summary(em, point.est = mean)
```

```{r}
emmeans5 <- emmeans(model53, ~ nozzle * solution, cont= "pairwise", type = "response")
```

```{r}
emmeans5$emmeans %>% 
  as_tibble() %>% 
  unite("trt", c("solution", "nozzle"), sep = " - ") %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response*100)) +
  geom_point() +
  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100)) +
  coord_flip() +
  theme_classic() +
  labs(title = "<200 droptlet")
```

```{r}
estimate_contrasts(model53, test = "bf")
```

```{r}
emmeans1$emmeans %>% as_tibble() %>% mutate(type = "DV10") -> em1
emmeans2$emmeans %>% as_tibble() %>% mutate(type = "DV50") -> em2
emmeans3$emmeans %>% as_tibble() %>% mutate(type = "DV90") -> em3
```
-> emm
```{r}
em1 %>% 
  bind_rows(em2) %>% 
  bind_rows(em3) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  mutate(type = fct_recode(type,
                          "D<sub>v10</sub>" = "DV10",
                          "D<sub>v50</sub>" = "DV50",
                          "D<sub>v90</sub>" = "DV90")) -> emm
```

```{r}
droplet %>% 
  pivot_longer(3:5, names_to = "type", values_to = "response") %>%
  mutate(type = str_to_upper(type)) %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(-rs, -x200, -rep) %>% 
  mutate(type = fct_recode(type,
                          "D<sub>v10</sub>" = "DV10",
                          "D<sub>v50</sub>" = "DV50",
                          "D<sub>v90</sub>" = "DV90")) -> droplet1
```

```{r}
library(ggthemes)
emm %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.3) +
  geom_jitter(data = droplet1, alpha = 0.1, size = 2) +
  facet_grid(~ type) +
  coord_flip() +
  labs(x = NULL, y = "Droplet size (µm)") +
  scale_color_viridis_d(option = "C") +
  theme_few() + 
  theme(strip.text = element_markdown(size = 12),
        legend.position = "none") -> dv
```

```{r}
emmeans4$emmeans %>% as_tibble() -> em4
emmeans5$emmeans %>% as_tibble() -> em5
```
```{r}
droplet %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(trt, rs) %>% 
  rename(response = rs) -> droplet2
```

```{r}
em4 %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.3) +
  geom_jitter(data = droplet2, alpha = 0.1, size = 2) +
  coord_flip() +
  labs(x = NULL, y = "RS") +
  scale_color_viridis_d(option = "C") +
  theme_few() + 
  theme(strip.text = element_markdown(),
        legend.position = "none") -> rs
```

```{r}
droplet %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  dplyr::select(trt, x200) %>% 
  rename(response = x200) -> droplet3
```

```{r}
(
em5 %>% 
  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
  ggplot(aes(x = fct_reorder(trt, response*100), y = response*100, color = trt)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100), size = 1.3) +
  geom_jitter(data = droplet3, alpha = 0.1, size = 2) +
  coord_flip() +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8)) +
  labs(x = NULL, y = "% drifable fines < 200 µm") +
  scale_color_viridis_d(option = "C") +
  theme_few() + 
  theme(strip.text = element_markdown(),
        legend.position = "none") -> x200
)
```

```{r}
rs + x200 -> fig
dv / fig -> fig1

ggsave("Figure 4.png", width = 9, height = 6)
```

### 2021-06-21 analysis/combined.Rmd
as

---
title: "combined"
author: "Maxwel Coura Oliveira"
date: "5/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	fig.align = "center",
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	include = FALSE
)
```

```{r message = FALSE}
# Packages
options(scipen = 999)
library(rstanarm)
library(brms)
library(scales)
library(tidyverse)
library(emmeans)
library(ggthemes)
library(ggpmisc)
library(cowplot)
library(patchwork)
library(multcomp)
library(ggtext)
library(ggeffects)
library(agricolae)
library(extrafont)
library(showtext)
showtext_auto()
font_add_google("Playfair Display", ## name of Google font
                "Playfair")  ## name that will be used in R
font_add_google("Bangers", "Bangers")

```

```{r}
new_dt <- read_csv("deposition.csv")
```

```{r}
new_dt %>% 
  unite("trt", c("solution", "sprayer", "nozzle"), 
        sep = "-", remove = FALSE) -> new_dt 
```

## Deposition inswath

```{r}
### Filter deposition dataset inswath
inswath <-  new_dt %>% 
  filter(type == "inswath") %>% 
  filter(!is.na(deposition)) %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) 
```

```{r}
### Test ANOVA assumptions
#### Normal distribution
inswath %>% 
  ggplot(aes(x = deposition)) +
  geom_histogram()
# data has normal distribution
```

```{r}
#### Homogeneity of variances
bartlett.test(deposition ~ location, data = inswath)
# can't compare locations
```

```{r eval=FALSE}
### Data analysis
#### Model

model1 <- lmer(deposition ~  trt +
                (1|block/location), 
              data = inswath)
```

```{r eval=FALSE}
isSingular(model1)
```

```{r}
brm(deposition ~  trt +
                (1|block/location), 
    data = inswath,
    control = list(adapt_delta = 0.95),
    family = gaussian(),
    warmup = 1000, iter = 2000, chains = 4,
    prior = set_prior("student_t(0.5, 3, 11)", class = "b")) -> model1
#    prior = set_prior("normal(0, 100)", class = "b")) -> model1
```

```{r}
summary(model1, waic = TRUE)
```

```{r}
#plot(model1)
```

```{r}
rg <- ref_grid(model1)
em <- emmeans(rg, "trt")
summary(em, point.est = mean)

epred <- emmeans(model1, "trt", dpar = "mean", cont="pairwise")
summary(epred$emmeans, point.est = mean)
```

```{r}
#https://easystats.github.io/bayestestR/articles/bayes_factors.html
#https://www.statisticshowto.com/bayes-factor-definition/
groups <- emmeans(model1, ~trt)
group_diff <- pairs(groups)
(groups_all <- rbind(groups, group_diff))

# pass the original model via prior

library(modelbased)
estimate_contrasts(model1, test = "bf")
```

```{r}
estimate_contrasts(model1, test = "bf") -> inswath_bf
inswath_bf %>% 
  tibble() -> inswath_bf
#readr::write_csv(path = "inswath_bf.csv", x = inswath_bf)
```

```{r}
em %>% as_tibble() %>% 
  left_join(inswath) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer)) +
  geom_point(size = 3) +
  geom_jitter(data = inswath %>% 
                rename(emmean = deposition), alpha = 0.1) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  ylim(0, 1550) +
  theme_few() +
  labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none") -> figA
figA +
  ggsave("Figure 1.png", width = 5, height = 5)
```

## Deposition upwind

```{r}
### Filter deposition dataset upwind
upwind <- new_dt %>% 
  filter(type == "upwind") %>% 
  filter(!is.na(deposition))
```

```{r}
### Test ANOVA assumptions
#### Normal distribution
upwind %>% 
  ggplot(aes(x = deposition)) +
  geom_histogram() 
# not normalized
```

```{r}
##### Log scale
upwind %>% 
  ggplot(aes(x = log(deposition))) +
  geom_histogram()
# yes!
```

```{r}
brm(deposition ~  trt +
                (1|block/location), 
    data = upwind,
    control = list(adapt_delta = 0.99),
    family = gaussian(),
    warmup = 1000, iter = 2000, chains = 4,
    prior = set_prior("student_t(0.5, 3, 11)", class = "b")) -> model2
```

```{r}
rg2 <- ref_grid(model2)
em2 <- emmeans(rg2, "trt", point.est = mean)
summary(em2, point.est = mean)

epred2 <- emmeans(model2, "trt", dpar = "mean", cont="pairwise", type = "response")
summary(epred2$emmeans, point.est = mean)
```

```{r}
#library(bayestestR)
#bayesfactor_parameters(groups_all, prior = model1)
```

```{r}
#https://easystats.github.io/bayestestR/articles/bayes_factors.html
#https://www.statisticshowto.com/bayes-factor-definition/
groups <- emmeans(model1, ~trt)
group_diff <- pairs(groups)
(groups_all <- rbind(groups, group_diff))

# pass the original model via prior

library(modelbased)
estimate_contrasts(model2, test = "bf") -> upwind_bf
upwind_bf %>% 
  tibble() -> upwind_bf
#readr::write_csv(path = "upwind_bf.csv", x = upwind_bf)
```

```{r eval = FALSE}
em2 %>% as_tibble() %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt)) +
  geom_point(size = 3) +
  geom_jitter(data = upwind %>% 
                rename(emmean = deposition), alpha = 0.05) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
#  ylim(0, 0.5) +
  theme_few() +
  labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none") -> figB
figB +
  ggsave("Figure 1B.png", width = 10, height = 5)
```

```{r eval = FALSE}
library(patchwork)

figB + figA + plot_annotation(tag_levels = 'A') -> figC

ggsave("Figure 1.png", width = 10, height = 5)
```

# Deposition downwind

```{r}
## Filter data
data_dw <- new_dt %>% 
  filter(type == "downwind") %>% 
  mutate(pass = factor(pass)) %>% 
  group_by(location, pass, block) 
```

```{r}
## Visualize
data_dw %>% 
  ggplot(aes(x = distance_m, y = deposition, color = nozzle)) +
  geom_point() +
  facet_grid(~ location)
# some trt have rapid decrease and some trt have linear trend
```

```{r}
## Visualize (log scale)
data_dw %>% 
#  unite("trt", c("solution", "sprayer", "nozzle")) %>% 
  ggplot(aes(x = log(distance_m), y = log(deposition), color = nozzle)) +
  geom_point() +
  facet_grid(sprayer ~ solution) +
  geom_smooth(method = "lm") 
# better go with log scale
```

```{r}
## Normal distribution
data_dw %>% 
  ggplot(aes(x = log(deposition))) +
  geom_histogram()
```

```{r}
# Linear Model
## Arrange dataset
data_dw1 <- data_dw %>% 
  group_by(trt) %>% 
  nest()

data_dw1
```

```{r}
pr <- prior(normal(0, 1), class = 'b')
### Model function
model3 <- function(df){
  brm(log(deposition) ~ log(distance_m) + 
         (1|block/location), data = df,

       prior = pr, cores=4)
}
```

```{r}
### Model function
model3 <- function(df){
  brm(log(deposition) ~ log(distance_m) + 
         (1|block/location), data = df,
      control = list(adapt_delta = 0.95),
      family = gaussian(),
      warmup = 1000, iter = 2000, chains = 4,
    prior = set_prior("student_t(0.5, 3, 11)", class = "b"))
}
```

```{r warning=FALSE, message = FALSE, warning = FALSE}
### Fit model and confidence intervals
data_dw2 <- data_dw1 %>% 
  mutate(model = map(data, model3),
         summary = map(model, broom.mixed::tidy))
```

```{r}
### Get parameters from models
params <- data_dw2 %>% 
  unnest(summary) %>% 
  filter(effect == "fixed") %>% 
  mutate(estimate_exp = exp(estimate),
         estimate_exp = case_when(
           term == "log(distance_m)" ~ -estimate_exp,
           TRUE                      ~ estimate_exp
         )) %>% 
  dplyr::select(trt, term, estimate, std.error, conf.low, conf.high) %>% 
  mutate(term = fct_recode(term,
                           slope = "logdistance_m"),
         term = fct_recode(term,
                           Intercept = "(Intercept)")) %>% 
  mutate(estimate = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high))

params
```

```{r}
params %>%

  pivot_wider(id_cols = trt,
              names_from = "term", 
              values_from = "estimate") %>% 
  mutate(slope = - slope) -> distance_final
```

```{r}
distance_function <- function(int, slope, y = 0) {
  distance = (y - int) / slope
  return(distance)
}

distance_final1 <- distance_final %>% 
  mutate(distance_m = map2_dbl(Intercept, slope, distance_function),
         distance_m = round(distance_m, 10)) %>% 
  mutate( y = Intercept + slope * distance_m)
```

```{r}
linear <- function(a, b, d) {
  y = a + b*d
  return(y)
}

linear(distance_final1$Intercept, distance_final1$slope, distance_final1$distance_m)
```

### Intercept

```{r include=TRUE, eval = FALSE}
a <- params %>% 
  filter(term == "Intercept") %>% 
  ggplot(aes(x = fct_reorder(trt, estimate), y = estimate, color = trt)) +
  geom_point(size = 2, stroke = 1) +
  scale_color_viridis_d(option = "H") +
  geom_linerange(aes(ymin = conf.low, ymax = conf.high), size = 1.5) +
  coord_flip() +
  labs(y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")")),
       x = NULL) +
  theme_few() +
  theme(legend.position = "none")
a
```

### Slope

```{r include=TRUE, eval = FALSE}}
b <- params %>% 
  filter(term == "slope") %>% 
  ggplot(aes(x = fct_reorder(trt, -estimate), 
             y = -estimate, color = trt)) +
  geom_point(size = 2, stroke = 1) +
  scale_color_viridis_d(option = "H") +
  geom_linerange(aes(ymin = -conf.low, ymax = -conf.high), size = 1.5) +
  coord_flip() +
  labs(y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")")),
       x = NULL) +
  theme_few() +
  theme(legend.position = "none") 
b
```

```{r eval = FALSE}
a + b + plot_annotation(tag_levels = 'A') -> figZ

ggsave("Figure 2.png", width = 10, height = 5)
```

### Predicted downwind distance

```{r include=TRUE}
c <- distance_final1 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = fct_reorder(trt, distance_m), 
             y = distance_m,
             label = distance_m, color = trt, shape = hood)) +
  geom_point(size = 3, stroke = 1) +
  scale_shape_manual(values = c(16, 1)) +
  geom_segment(aes(x= trt, xend= trt, y=0, yend=distance_m), size = 2) +
  coord_flip() +
  scale_color_viridis_d(option = "H") + 
  labs(y = "Predicted distance (m)", x = NULL) +
  ylim(0,60) +
  theme_few() +
  theme(legend.position = "none")  
c
```

```{r}
fig <- data_dw2 %>% 
  dplyr::select(trt, model)
```

```{r warning=FALSE, message = FALSE}
fig_model <- function(model){
  ggpredict(model, terms = "distance_m", back.transform = TRUE) %>% 
    as_tibble()
}

fig1 <- fig %>% 
  mutate(estimates = map(model, fig_model)) %>% 
  unnest(estimates) %>% 
  rename(distance_m = x) %>% 
  mutate_if(is_character, as_factor) 
```

```{r}
fig1 %>% 
  distinct(trt) %>%
  ungroup() %>% 
  mutate(id = row_number()) -> id_col

fig1 %>% 
  left_join(id_col) -> fig1
```

```{r eval=FALSE, include=FALSE}
library(sjstats)
performance::r2(fig1$model[[2]]) -> m1
m1
```

```{r eval=FALSE, include=FALSE}
rsquared <- function(trt){
  performance::r2(fig1$model[[trt]])$R2_Bayes
}
```

```{r eval=FALSE, include=FALSE}
fig1 %>% 
  mutate(rsquared = map(id, rsquared)) %>% 
  unnest(rsquared) -> fig1
```

```{r}
label <- distance_final %>% 
  mutate(Intercept = round(Intercept, 1),
         slope = round(slope, 2)) %>% 
  mutate(y = "y = ",
         x = "x") %>% 
  unite("formula", c("y", "Intercept", "slope"), sep = " ") %>% 
  unite("formula", c("formula", "x"), sep = "")
```

```{r}
fig2 <- fig1 %>% 
  left_join(label)
```

### Back-transformed linear models

```{r include=TRUE}
figs <- fig2 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = distance_m, y = predicted, color = trt, 
             fill = trt, label = formula, shape = hood)) +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  geom_line(fill = NA) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
              alpha = 0.3, color = NA) +
  facet_wrap(~ trt, ncol = 3) +
  scale_shape_manual(values = c(16, 1)) + 
  theme_few() +
  geom_label(aes(label = formula), x = 30, y = 20, color = "white") +
  labs(x = "Distance (m)", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_textbox(
          size = 12,
          color = "white", 
          fill = "#494949", 
          box.color = "#282728",
          halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
          padding = margin(2, 0, 1, 0), 
          margin = margin(3, 3, 3, 3))) +
  ggsave("Figure 2.png", width = 6, height = 9)
figs
```

### AUC

```{r}
(id_df <- data_dw %>% 
  distinct(pass, block, location) %>% 
  ungroup() %>% 
  mutate(id = as_factor(dplyr::row_number()))
)
```

```{r}
id_df1 <- data_dw %>% 
  left_join(id_df) 
```

```{r}
auc_cal <- function(number){
  df <- id_df1 %>% 
    filter(id == number)

  audps(df$deposition, df$distance_m, type="absolute") 
}

auc_data <- id_df1 %>% 
  group_by(id) %>% 
  nest() %>% 
  mutate(auc = map_dbl(id, auc_cal)) %>% 
  ungroup(id) %>% 
  unnest() %>% 
  filter(!is.na(auc)) %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) 
```

```{r}
auc_data1 <- auc_data %>% 
  filter(distance_m == 1) %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) 
```

```{r}
auc_data1 %>% 
  ggplot(aes(x = log(auc))) + 
  geom_histogram()
```

```{r}
brm(auc ~  trt +
                (1|block/location), 
    data = auc_data1,
    control = list(adapt_delta = 0.99),
    family = "gaussian",
    warmup = 1000, iter = 2000, chains = 4,
   prior = set_prior("student_t(0.5, 3, 11)", class = "b")) -> auc_model
```

```{r}
rg3 <- ref_grid(auc_model)
em3 <- emmeans(rg3, "trt")
summary(em3, point.est = mean)
```

```{r}
plot(em3, ~ "trt", type="response")
```

```{r}
epred3 <- emmeans(auc_model, "trt", dpar = "mean", 
                  cont="pairwise")
summary(epred3$emmeans, point.est = mean, type = "response")
#https://easystats.github.io/bayestestR/articles/bayes_factors.html
```

```{r}
epred3$emmeans %>% as_tibble() %>% 
  left_join(auc_data1) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer)) +
  geom_point(size = 3) +
  geom_jitter(data = auc_data %>% 
                rename(emmean = auc), alpha = 0.02) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_few() +
  labs(x = NULL, y = "Area under the curve") +
  theme(legend.position = "none") -> figE
figE
```

```{r}
estimate_contrasts(auc_model, test = "bf") -> auc_bf
auc_bf %>% 
  tibble() -> auc_bf
readr::write_csv(path = "auc_bf.csv", x = auc_bf)
```

```{r eval = FALSE}
library(modelbased)
estimate_contrasts(auc_model, test = "bf") %>% 
  kableExtra::kable()
```

```{r}
c + figE + plot_annotation(tag_levels = 'A') -> figU

ggsave("Figure 3.png", width = 10, height = 5)
```

### 2021-06-21 analysis/droplet.Rmd
as

---
title: "droptlet"
author: "Maxwel Coura Oliveira"
date: "6/10/2021"
output: html_document
---

```{r}
library(tidyverse)
library(glmmTMB)
library(emmeans)
library(betareg)
library(lme4)
library(multcomp)
library(lmerTest)
library(car)
library(brms)
```

```{r}
readxl::read_excel("droplet_data.xlsx")
```

```{r}
readxl::read_excel("droplet_size_data.xlsx") %>% 
  janitor::clean_names() %>% 
  mutate_if(is_character, as_factor) %>% 
  group_by(solution, nozzle) %>% 
  mutate(nozzle = fct_recode(nozzle, 
                             "ULD12003" = "ULD11003")) %>% 
  mutate(x200 = x200/100) %>% 
  mutate(rep = row_number()) -> droplet
```

# DV10

```{r}
model1 <- glm(`dv10` ~ solution * nozzle,
                  family = Gamma(link = "inverse"),
                  data = droplet)
```

```{r}
Anova(model1)
```

```{r}
emmeans1 <- emmeans(model1, ~ nozzle * solution, type = "response")
```

```{r}
cld1 <- cld(emmeans1, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble()
cld1
```

# DV50

```{r}
model2 <- glm(`dv50` ~ solution * nozzle,
                  family = Gamma(link = "inverse"),
                  data = droplet)
```

```{r}
Anova(model2)
```

```{r}
emmeans2 <- emmeans(model2, ~ nozzle * solution, type = "response")
```

```{r}
cld2 <- cld(emmeans2, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble()
cld2
```

# DV90

```{r}
model3 <- glm(`dv90` ~ solution * nozzle,
                  family = Gamma(link = "inverse"),
                  data = droplet)
```

```{r}
Anova(model3)
```

```{r}
emmeans3 <- emmeans(model3, ~ nozzle * solution, type = "response")
```

```{r}
cld3 <- cld(emmeans3, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble()
cld3
```

# RS

```{r}
model4 <- glm(rs ~ solution * nozzle,
                  family = Gamma(link = "inverse"),
                  data = droplet)
```

```{r}
Anova(model4)
```

```{r}
emmeans4 <- emmeans(model4, ~ nozzle * solution, type = "response")
```

```{r}
cld4 <- cld(emmeans4, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble()
cld4
```

# x200

```{r}
model5 <- betareg(x200 ~ solution * nozzle, 
                  link = "logit",
                  data = droplet)
```

```{r}
Anova(model5)
```

```{r}
emmeans5 <- emmeans(model5, ~ nozzle * solution, type = "response")
```

```{r}
cld5 <- cld(emmeans5, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble() 
cld5
```

### 2021-06-21 manuscript.Rmd
as

---
title: "Spray particle drift"
author: Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo Werle
date: "`r format(Sys.Date())`"
documentclass: article
linestretch: 2
abstract: "BACKGROUND: "
papersize: "a4"
mainfont: Arial
#monofont: "Arial"
#monofontoptions: "Scale=0.7"
fontsize: "12pt"
geometry:
  margin = 2.54cm
csl: pms.csl
bibliography: biblio.bib
output:
  pdf_document: 
      latex_engine: xelatex

header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
---

```{r include=FALSE}
library(kableExtra)
library(tidyverse)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

## Introduction

## Materials and Methods

Solution, sprayer and nozzle factors were grouped as a single fixed effect (herein treatments) due to missing factor water in Missouri. Resulting in a combination of 12 treatments.

### Statistical analyses

The statistical analyses were conducted with R statistical software version 4.1.0 @LanguageEnvironmentStatistical2021. Data analyses were performed with Bayesian inference with "brms" package @burknerBrmsPackageBayesian2017. Bayesian inference uses Markov chain Monte Carlo algorithms for sampling a probability distribution @burknerBrmsPackageBayesian2017. In addition, Bayesian inference avoid singular fit from frequentist linear models when using complex random effects.

#### Spray solution deposition at upwind and inswath

Data was fitted to a mixed model using *brm* function. Treatments were the fixed effects and block nested within location random effects. Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior summaries (mean and highest posterior density) were estimated with *emmeans* function from "emmeans" package. Treatment means were compared using Bayes Factor (BF) [@leeBayesianCognitiveModeling2014; @kassBayesFactors1995]. In short, if BF > 1 there is evidence for H1 (difference between treatments); whereas, if H0 < 1 there is evidence for H0 (no difference between treatments). If BF = 1, there is no evidence. The level of evidence (anecdotal, moderate, strong, very strong, and extreme) varies as the BF value increase (evidence for H1) or decrease (evidence for H0).

#### Spray solution deposition at downwind

Data was fitted to a Bayesian linear mixed model using *brm* function. Spray solution deposition and distance were log-transformed to meet linearity. A single model was fitted to each treatment. For each model, treatments and distance were the fixed effects and block nested within location random effects. Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom. For clarification, intercepts, slopes were back-transformed with *exponential* function. Moreover, the linear models fitted were used to predict the distance where no spray particle deposition was detected (0 &eta;L cm^-2^) for each treatment, which was also back-transformed to m scale.

The area under the curve (AUC) was used to validate the linear models. The spray solution deposition across distances within a experimental unit were used to calculate the absolute AUC value. The AUC was performed with *audps* function from "agricolae" package. The AUC is commonly used for plant disease progress [@meenaAreaDiseaseProgress2011; @simkoAreaDiseaseProgress2011] but has been used to calculate herbicide injury @striegelSpraySolutionPH2021. Data was fitted to a mixed model using *brm* function. Treatments were the fixed effects and block nested within location random effects. Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior summaries (mean and highest posterior density) were estimated with *emmeans* function from "emmeans" package. Treatment means were compared using Bayes Factor (BF) as above-mentioned.

## Results

### Spray solution deposition at inswath and upwind

In general, Open sprayer treatments resulted in a more variable spray particle deposition than Hood treatments (Figure 1). The inclusion of either DRA or Water strongly impacted spray particle deposition for Open sprayer treatments, regardless nozzle type. The top and bottom three treatments contained either DRA or Water, respectively. For example, treatment DRA-Open-ULD resulted in the highest spray particle deposition (1318.5  &eta;L cm^-2^, Figure 1). In contrast, 911.2 nL cm^-2^ was the lowest spray solution deposition, which was achieved with Water-Open-ULD treatment. Hood sprayer treatments resulted in a more uniform spray particle deposition. Furthermore, there were less than 0.29 &eta;L cm^-2^ spray deposition at upwind with a strong evidence (BF < 0.25) of no difference between all treatments pairwise contrasts (data not shown).

### Spray solution deposition at downwind

  Treatments with highest intercepts, which is the amount of spray particle deposition near the treated area, were Water-Open-AIXR (15.7 &eta;L cm^-2^), followed by DRA-Open-AIXR (15.7 &eta;L cm^-2^), and Water-Open-ULD (12.0 &eta;L cm^-2^; Figure 2). In contrast, DRA-Hood-TTI, DRA-Hood-ULD and DRA-Hood-AIXR treatments resulted in the lowest intercepts (< 2.0 &eta;L cm^-2^). In addition, there is evidence that treatments with Hood sprayer provided highest decay of spray particle deposition (slopes; Figure 2). The treatments with highest decay were Water-Hood-TTI (-0.50), DRA-Hood-TTI (-0.48), DRA-Hood-ULD (-0.44), Water-Hood-AIXR (-0.43), Water-Hood-ULD (-0.43), and DRA-Hood-AIXR (-0.39).

The predicted distance where no spray particle deposition was detected varied upon treatments (Figure 3A). In general, Open sprayer treatments resulted in spray particle deposition at longest distances. For example, the distance of non-detectable spray particle deposition with Open sprayer treatments varied from 9.9 m (DRA-Open-TTI) to 54.9 m with DRA-Open-AIXR; whereas Hood sprayer treatments varied from 1.4 to 8.2 m with DRA-Hood-TTI and Water-Hood-AIXR, respectively.

Treatments with Hood or Open sprayer strongly impacted on AUC values (Figure 3B). The highest AUC values were Water-Open-AIXR (87.4), followed by Water-Open-ULD (72.9) and DRA-Open-AIXR (72.6). In contrast, DRA-Hood-TTI (13.9), DRA-Hood-ULD (14.3) and Water-Open-AIXR (21.9) resulted in lowest AUC values. The impact of Open and Hood sprayer is demonstrated in treatments including AIXR nozzle. There is a high difference in AUC (50.7) between DRA-Open-AIXR vs DRA-Hood-AIXR (BF > 100). Moreover, addition of DRA did reduced AUC values when comparing within fixed factors, sprayer (Hood and Open) and nozzle (AIXR, TTI and ULD); however, addition of DRA were not statistically different for some contrasts, including DRA-Hood-TTI vs Water-Hood-TTI (BF = 0.91), DRA-Open-TTI vs Water-Open-TTI (BF = 0.55), and DRA-Open-AIXR vs Water-Open-AIXR (BF = 0.93).

## Discussion

### Spray solution deposition at inswath and upwind

### Spray solution deposition at downwind

## Conclusion

## Acknowledgments

## Conflict of Interest Declaration

## Tables (each table complete with title and footnotes)

## Figure Legends

## References

### 2021-06-22 manuscript.Rmd
as

@@
       latex_engine: xelatex
+      keep_tex: true
+      toc_depth: 4
+      number_sections: true
 
@@
   - \linenumbers
+#  - \setcounter{section}{1}
 ---
@@
 
-## Introduction
+# Introduction
 
-## Materials and Methods
+# Materials and Methods
 
@@
 
-### Statistical analyses
+## Statistical analyses
 
@@
 Data analyses were performed with Bayesian inference with "brms" package @burknerBrmsPackageBayesian2017.
-Bayesian inference uses Markov chain Monte Carlo algorithms for sampling a probability distribution @burknerBrmsPackageBayesian2017.
-In addition, Bayesian inference avoid singular fit from frequentist linear models when using complex random effects.
+Bayesian inference uses Markov chain Monte Carlo algorithms for sampling a probability distribution @burknerBrmsPackageBayesian2017; and avoid singular fit from frequentist linear models when using complex random effects.
 
-#### Spray solution deposition at upwind and inswath
+### Spray solution deposition at upwind and inswath
 
@@
 
-#### Spray solution deposition at downwind
+### Spray solution deposition at downwind
 
@@
 
-## Results
+### Dv, Relative Span
 
-### Spray solution deposition at inswath and upwind
+# Results
+
+## Spray solution deposition at inswath and upwind
 
 In general, Open sprayer treatments resulted in a more variable spray particle deposition than Hood treatments (Figure 1).
-The inclusion of either DRA or Water strongly impacted spray particle deposition for Open sprayer treatments, regardless nozzle type.
+The inclusion of either DRA or Water strongly impacted spray particle deposition inswath for Open sprayer treatments, regardless nozzle type.
 The top and bottom three treatments contained either DRA or Water, respectively.
@@
 Hood sprayer treatments resulted in a more uniform spray particle deposition.
-Furthermore, there were less than 0.29 &eta;L cm^-2^ spray deposition at upwind with a strong evidence (BF < 0.25) of no difference between all treatments pairwise contrasts (data not shown).
+Furthermore, there were less than 0.29 &eta;L cm^-2^ spray deposition at upwind with a strong evidence (BF < 0.25) of no difference between all pairwise treatments contrasts (data not shown).
 
-### Spray solution deposition at downwind
+## Spray solution deposition at downwind
 
@@
 In contrast, DRA-Hood-TTI, DRA-Hood-ULD and DRA-Hood-AIXR treatments resulted in the lowest intercepts (< 2.0 &eta;L cm^-2^).
-In addition, there is evidence that treatments with Hood sprayer provided highest decay of spray particle deposition (slopes; Figure 2).
-The treatments with highest decay were Water-Hood-TTI (-0.50), DRA-Hood-TTI (-0.48), DRA-Hood-ULD (-0.44), Water-Hood-AIXR (-0.43), Water-Hood-ULD (-0.43), and DRA-Hood-AIXR (-0.39).
+In addition, there is evidence that treatments with Hood sprayer provided faster decay of spray particle deposition (slopes; Figure 2).
+The treatments with highest slope decay were Water-Hood-TTI (-0.50), DRA-Hood-TTI (-0.48), DRA-Hood-ULD (-0.44), Water-Hood-AIXR (-0.43), Water-Hood-ULD (-0.43), and DRA-Hood-AIXR (-0.39).
 
@@
 
+Similar trend was observed to AUC.
 Treatments with Hood or Open sprayer strongly impacted on AUC values (Figure 3B).
@@
 
-## Discussion
+## Dv, Relative Span
 
-### Spray solution deposition at inswath and upwind
+# Discussion
 
-### Spray solution deposition at downwind
+## Spray solution deposition at inswath and upwind
 
-## Conclusion
+## Spray solution deposition at downwind
 
-## Acknowledgments
+# Conclusion
 
-## Conflict of Interest Declaration
+# Acknowledgments
 
-## Tables (each table complete with title and footnotes)
+# Conflict of Interest Declaration
 
-## Figure Legends
+# Tables (each table complete with title and footnotes)
 
-## References
+# Figure Legends
+
+# References

### 2021-06-22 manuscript.tex
as

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Arial}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Spray particle drift},
  pdfauthor={Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo Werle},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin = 2.54cm]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage[left]{lineno}
\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Spray particle drift}
\author{Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo
Werle}
\date{2021-06-22}

\begin{document}
\maketitle
\begin{abstract}
BACKGROUND:
\end{abstract}

\setstretch{2}
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

Solution, sprayer and nozzle factors were grouped as a single fixed
effect (herein treatments) due to missing factor water in Missouri.
Resulting in a combination of 12 treatments.

\hypertarget{statistical-analyses}{%
\subsection{Statistical analyses}\label{statistical-analyses}}

The statistical analyses were conducted with R statistical software
version 4.1.0.\textsuperscript{1} Data analyses were performed with
Bayesian inference with ``brms'' package.\textsuperscript{2} Bayesian
inference uses Markov chain Monte Carlo algorithms for sampling a
probability distribution;\textsuperscript{2} and avoid singular fit from
frequentist linear models when using complex random effects.

\hypertarget{spray-solution-deposition-at-upwind-and-inswath}{%
\subsubsection{Spray solution deposition at upwind and
inswath}\label{spray-solution-deposition-at-upwind-and-inswath}}

Data was fitted to a mixed model using \emph{brm} function. Treatments
were the fixed effects and block nested within location random effects.
Model family was gaussian and prior distribution was set to student-t
with mean 0.5, standard deviation 3 and 11 degrees of freedom. The
posterior summaries (mean and highest posterior density) were estimated
with \emph{emmeans} function from ``emmeans'' package. Treatment means
were compared using Bayes Factor (BF).\textsuperscript{3,4} In short, if
BF \textgreater{} 1 there is evidence for H1 (difference between
treatments); whereas, if H0 \textless{} 1 there is evidence for H0 (no
difference between treatments). If BF = 1, there is no evidence. The
level of evidence (anecdotal, moderate, strong, very strong, and
extreme) varies as the BF value increase (evidence for H1) or decrease
(evidence for H0).

\hypertarget{spray-solution-deposition-at-downwind}{%
\subsubsection{Spray solution deposition at
downwind}\label{spray-solution-deposition-at-downwind}}

Data was fitted to a Bayesian linear mixed model using \emph{brm}
function. Spray solution deposition and distance were log-transformed to
meet linearity. A single model was fitted to each treatment. For each
model, treatments and distance were the fixed effects and block nested
within location random effects. Model family was gaussian and prior
distribution was set to student-t with mean 0.5, standard deviation 3
and 11 degrees of freedom. For clarification, intercepts, slopes were
back-transformed with \emph{exponential} function. Moreover, the linear
models fitted were used to predict the distance where no spray particle
deposition was detected (0 ηL cm\textsuperscript{-2}) for each
treatment, which was also back-transformed to m scale.

The area under the curve (AUC) was used to validate the linear models.
The spray solution deposition across distances within a experimental
unit were used to calculate the absolute AUC value. The AUC was
performed with \emph{audps} function from ``agricolae'' package. The AUC
is commonly used for plant disease progress\textsuperscript{5,6} but has
been used to calculate herbicide injury.\textsuperscript{7} Data was
fitted to a mixed model using \emph{brm} function. Treatments were the
fixed effects and block nested within location random effects. Model
family was gaussian and prior distribution was set to student-t with
mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior
summaries (mean and highest posterior density) were estimated with
\emph{emmeans} function from ``emmeans'' package. Treatment means were
compared using Bayes Factor (BF) as above-mentioned.

\hypertarget{dv-relative-span}{%
\subsubsection{Dv, Relative Span}\label{dv-relative-span}}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{spray-solution-deposition-at-inswath-and-upwind}{%
\subsection{Spray solution deposition at inswath and
upwind}\label{spray-solution-deposition-at-inswath-and-upwind}}

In general, Open sprayer treatments resulted in a more variable spray
particle deposition than Hood treatments (Figure 1). The inclusion of
either DRA or Water strongly impacted spray particle deposition inswath
for Open sprayer treatments, regardless nozzle type. The top and bottom
three treatments contained either DRA or Water, respectively. For
example, treatment DRA-Open-ULD resulted in the highest spray particle
deposition (1318.5 ηL cm\textsuperscript{-2}, Figure 1). In contrast,
911.2 nL cm\textsuperscript{-2} was the lowest spray solution
deposition, which was achieved with Water-Open-ULD treatment. Hood
sprayer treatments resulted in a more uniform spray particle deposition.
Furthermore, there were less than 0.29 ηL cm\textsuperscript{-2} spray
deposition at upwind with a strong evidence (BF \textless{} 0.25) of no
difference between all pairwise treatments contrasts (data not shown).

\hypertarget{spray-solution-deposition-at-downwind-1}{%
\subsection{Spray solution deposition at
downwind}\label{spray-solution-deposition-at-downwind-1}}

Treatments with highest intercepts, which is the amount of spray
particle deposition near the treated area, were Water-Open-AIXR (15.7 ηL
cm\textsuperscript{-2}), followed by DRA-Open-AIXR (15.7 ηL
cm\textsuperscript{-2}), and Water-Open-ULD (12.0 ηL
cm\textsuperscript{-2}; Figure 2). In contrast, DRA-Hood-TTI,
DRA-Hood-ULD and DRA-Hood-AIXR treatments resulted in the lowest
intercepts (\textless{} 2.0 ηL cm\textsuperscript{-2}). In addition,
there is evidence that treatments with Hood sprayer provided faster
decay of spray particle deposition (slopes; Figure 2). The treatments
with highest slope decay were Water-Hood-TTI (-0.50), DRA-Hood-TTI
(-0.48), DRA-Hood-ULD (-0.44), Water-Hood-AIXR (-0.43), Water-Hood-ULD
(-0.43), and DRA-Hood-AIXR (-0.39).

The predicted distance where no spray particle deposition was detected
varied upon treatments (Figure 3A). In general, Open sprayer treatments
resulted in spray particle deposition at longest distances. For example,
the distance of non-detectable spray particle deposition with Open
sprayer treatments varied from 9.9 m (DRA-Open-TTI) to 54.9 m with
DRA-Open-AIXR; whereas Hood sprayer treatments varied from 1.4 to 8.2 m
with DRA-Hood-TTI and Water-Hood-AIXR, respectively.

Similar trend was observed to AUC. Treatments with Hood or Open sprayer
strongly impacted on AUC values (Figure 3B). The highest AUC values were
Water-Open-AIXR (87.4), followed by Water-Open-ULD (72.9) and
DRA-Open-AIXR (72.6). In contrast, DRA-Hood-TTI (13.9), DRA-Hood-ULD
(14.3) and Water-Open-AIXR (21.9) resulted in lowest AUC values. The
impact of Open and Hood sprayer is demonstrated in treatments including
AIXR nozzle. There is a high difference in AUC (50.7) between
DRA-Open-AIXR vs DRA-Hood-AIXR (BF \textgreater{} 100). Moreover,
addition of DRA did reduced AUC values when comparing within fixed
factors, sprayer (Hood and Open) and nozzle (AIXR, TTI and ULD);
however, addition of DRA were not statistically different for some
contrasts, including DRA-Hood-TTI vs Water-Hood-TTI (BF = 0.91),
DRA-Open-TTI vs Water-Open-TTI (BF = 0.55), and DRA-Open-AIXR vs
Water-Open-AIXR (BF = 0.93).

\hypertarget{dv-relative-span-1}{%
\subsection{Dv, Relative Span}\label{dv-relative-span-1}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{spray-solution-deposition-at-inswath-and-upwind-1}{%
\subsection{Spray solution deposition at inswath and
upwind}\label{spray-solution-deposition-at-inswath-and-upwind-1}}

\hypertarget{spray-solution-deposition-at-downwind-2}{%
\subsection{Spray solution deposition at
downwind}\label{spray-solution-deposition-at-downwind-2}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{acknowledgments}{%
\section{Acknowledgments}\label{acknowledgments}}

\hypertarget{conflict-of-interest-declaration}{%
\section{Conflict of Interest
Declaration}\label{conflict-of-interest-declaration}}

\hypertarget{tables-each-table-complete-with-title-and-footnotes}{%
\section{Tables (each table complete with title and
footnotes)}\label{tables-each-table-complete-with-title-and-footnotes}}

\hypertarget{figure-legends}{%
\section{Figure Legends}\label{figure-legends}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-LanguageEnvironmentStatistical2021}{}%
\CSLLeftMargin{1 }
\CSLRightInline{R: {A Language} and {Environment} for {Statistical
Computing}, {R Foundation for Statistical Computing}, {Vienna, Austria}
(2021).}

\leavevmode\hypertarget{ref-burknerBrmsPackageBayesian2017}{}%
\CSLLeftMargin{2 }
\CSLRightInline{Bürkner P-C, \textbf{Brms} : {An} {\emph{R}} {Package}
for {Bayesian Multilevel Models Using} {\emph{Stan}}, \emph{J Stat Soft}
\textbf{80} (2017).}

\leavevmode\hypertarget{ref-leeBayesianCognitiveModeling2014}{}%
\CSLLeftMargin{3 }
\CSLRightInline{Lee MD and Wagenmakers E-J, Bayesian {Cognitive
Modeling}: {A Practical Course}, {Cambridge University Press} (2014).}

\leavevmode\hypertarget{ref-kassBayesFactors1995}{}%
\CSLLeftMargin{4 }
\CSLRightInline{Kass RE and Raftery AE, Bayes {Factors}, \emph{Journal
of the American Statistical Association} \textbf{90}:773--795,
{{[}American Statistical Association, Taylor \& Francis, Ltd.{]}}
(1995).}

\leavevmode\hypertarget{ref-meenaAreaDiseaseProgress2011}{}%
\CSLLeftMargin{5 }
\CSLRightInline{Meena PD, Chattopadhyay C, Meena SS, and Kumar A, Area
under disease progress curve and apparent infection rate of {Alternaria}
blight disease of {Indian} mustard ({Brassica} juncea) at different
plant age, \emph{Archives of Phytopathology and Plant Protection}
\textbf{44}:684--693, {Taylor \& Francis} (2011).}

\leavevmode\hypertarget{ref-simkoAreaDiseaseProgress2011}{}%
\CSLLeftMargin{6 }
\CSLRightInline{Simko I and Piepho H-P, The {Area Under} the {Disease
Progress Stairs}: {Calculation}, {Advantage}, and {Application},
\emph{Phytopathology®} \textbf{102}:381--389, {Scientific Societies}
(2011).}

\leavevmode\hypertarget{ref-striegelSpraySolutionPH2021}{}%
\CSLLeftMargin{7 }
\CSLRightInline{Striegel S, Oliveira MC, Arneson N, Conley SP,
Stoltenberg DE, and Werle R, Spray solution {pH} and soybean injury as
influenced by synthetic auxin formulation and spray additives,
\emph{Weed Technol} \textbf{35}:113--127 (2021).}

\end{CSLReferences}

\end{document}

### 2021-06-22 manuscript.Rmd
s

@@
 Data analyses were performed with Bayesian inference with "brms" package @burknerBrmsPackageBayesian2017.
-Bayesian inference uses Markov chain Monte Carlo algorithms for sampling a probability distribution @burknerBrmsPackageBayesian2017; and avoid singular fit from frequentist linear models when using complex random effects.
+Bayesian inference uses Markov chain Monte Carlo algorithms for sampling a probability distribution @burknerBrmsPackageBayesian2017; and avoids singular fit from frequentist linear models when using complex random effects.
 
@@
 Data was fitted to a mixed model using *brm* function.
-Treatments were the fixed effects and block nested within location random effects.
+Treatments were the fixed effects and blocks nested within location random effects.
 Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom.
-The posterior summaries (mean and highest posterior density) were estimated with *emmeans* function from "emmeans" package.
+The posterior summaries (mean and highest posterior density) were estimated with *emmeans* function from the "emmeans" package.
 Treatment means were compared using Bayes Factor (BF) [@leeBayesianCognitiveModeling2014; @kassBayesFactors1995].
@@
 If BF = 1, there is no evidence.
-The level of evidence (anecdotal, moderate, strong, very strong, and extreme) varies as the BF value increase (evidence for H1) or decrease (evidence for H0).
+The level of evidence (anecdotal, moderate, strong, very strong, and extreme) varies as the BF value increases (evidence for H1) or decreases (evidence for H0).
 
@@
 A single model was fitted to each treatment.
-For each model, treatments and distance were the fixed effects and block nested within location random effects.
+For each model, treatments and distance were the fixed effects and blocks nested within location random effects.
 Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom.
@@
 The area under the curve (AUC) was used to validate the linear models.
-The spray solution deposition across distances within a experimental unit were used to calculate the absolute AUC value.
-The AUC was performed with *audps* function from "agricolae" package.
+The spray solution deposition across distances within an experimental unit were used to calculate the absolute AUC value.
+The AUC was performed with *audps* function from the "agricolae" package.
 The AUC is commonly used for plant disease progress [@meenaAreaDiseaseProgress2011; @simkoAreaDiseaseProgress2011] but has been used to calculate herbicide injury @striegelSpraySolutionPH2021.
 Data was fitted to a mixed model using *brm* function.
-Treatments were the fixed effects and block nested within location random effects.
+Treatments were the fixed effects and blocks nested within location random effects.
 Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom.
-The posterior summaries (mean and highest posterior density) were estimated with *emmeans* function from "emmeans" package.
+The posterior summaries (mean and highest posterior density) were estimated with *emmeans* function from the "emmeans" package.
 Treatment means were compared using Bayes Factor (BF) as above-mentioned.
@@
 Hood sprayer treatments resulted in a more uniform spray particle deposition.
-Furthermore, there were less than 0.29 &eta;L cm^-2^ spray deposition at upwind with a strong evidence (BF < 0.25) of no difference between all pairwise treatments contrasts (data not shown).
+Furthermore, there were less than 0.29 &eta;L cm^-2^ spray deposition at upwind with strong evidence (BF < 0.25) of no difference between all pairwise treatment contrasts (data not shown).
 
@@
 
-Similar trend was observed to AUC.
+Similar trend was observed in AUC.
 Treatments with Hood or Open sprayer strongly impacted on AUC values (Figure 3B).
@@
 In contrast, DRA-Hood-TTI (13.9), DRA-Hood-ULD (14.3) and Water-Open-AIXR (21.9) resulted in lowest AUC values.
-The impact of Open and Hood sprayer is demonstrated in treatments including AIXR nozzle.
+The impact of Open and Hood sprayer is demonstrated in treatments including AIXR nozzles.
 There is a high difference in AUC (50.7) between DRA-Open-AIXR vs DRA-Hood-AIXR (BF > 100).

### 2021-07-14 manuscript.Rmd
h

@@
 # Materials and Methods
+
+## Experimental sites
+
+Field experiments were conducted in three locations: North Platte, NE (geographic coordinates) on September 11-12/2021; Arlington, WI (geographic coordinates) on September 15-16/2021; and city, MO (geographic coordinates) on September 18-20/2021.
+In NE, WI, and MO, applications were made on bare ground, corn stubble (XX cm height) and ????, respectively.
+The fields were flat and with no surrounding trees.
+Samples were processed and analyzed at the Pesticide Application Technology Laboratory of the University of Nebraska-Lincoln located in North Platte, Nebraska.
+
+## Field study
+
+Three factors were evaluated: sprayer type, nozzle type, and spray solution.
+Each experimental treatment was replicated 10 times.
+Two sprayers (Manufacturer, city, state) were employed for this study, the only difference being the inclusion of a hood or no hood.
+These sprayers were 9.1 meters in width and each had a 1130 L polyethylene tank.
+Spray delivery was accomplished via a hydraulic pump driven by the accompanying tractor.
+Each sprayer was connected to its own tractor via the three-point hitch system.
+Nozzle spacing was 51 cm, and boom height was set at 90 cm above the ground level for both sprayers.
+The wind skirt on the hooded sprayer was set slightly above the soil surface or corn stubble.
+The height for each sprayer was maintained throughout the study via the sprayers’ guide wheels and the tractors’ hitch system.
+The hood was constructed of molded, polymer plastic that surrounded the nozzles (Manufacturer, city, state).
+The hood sections reached approximately 30.5 cm below the nozzle orifices, and a plastic curtain reached a further 10 cm below the plastic hood.
+Nozzles were properly attached to the boom in order to get no interference of hood and nozzle plume.
+
+Nozzle types were TTI11003 and AIXR11003 (Teejet Technologies, Wheaton, IL), and ULD12003 (Pentair, Minneapolis, MN).
+All nozzles have air inclusion features and the carrier volume was 140 L ha^-1 applied at 276 kPa operating pressure and 2.6 m s-1 application speed.
+
+The spray solutions were prepared at the same day of applications and were water alone and water plus a drift-reducing adjuvant based on polyethylene glycol, choline chloride, and guar gum (IntactTM, Precision Laboratories, LLC, Waukegan, IL) at a rate of 0.5% v v-1.
+Additionally, a rhodamine fluorescent dye (Red Dye, Cole-Parmer, Vernon Hills, IL) was added to all solutions at a rate of 0.5% v v-1.
+The volumetric median diameter (VMD) of droplets and volume percentage of droplets finer than 200 μm (V200) were measured at the Pesticide Application Technology Laboratory using a Sympatec Helos-Vario K/R laser diffraction system (Sympatec Inc., Clausthal, Germany), setup with a R7 lens, with a dynamic size range of 9 to 1,800 μm.
+The distance from the nozzle tip to the laser was 0.3 m.
+The VMD and V200 for each combination spray solution versus nozzle type are listed in Table 1.
+
+## Application and field layout
+
+Prior to the applications, 27 drift collection stations were placed downwind of the sprayed area in three transects (spaced by 7.6 m) and perpendicular to the spray line (Figure 1).
+For each transect, collectors were positioned at 1, 2, 3, 4, 8, 16, 31, 45, 60 m from the edge of the application zone.
+Additionally, three drift stations were placed 5 m upwind from the edge of the application zone and four petri dishes (150 mm diameter) were placed in-swath.
+All collectors were positioned 10 cm above the ground surface.
+Mylar cards (Grafix Plastics, Cleveland, OH) were used as drift collectors.
+Cards with dimensions of 10 x 10 cm were placed upwind and up to 31 m downwind, whereas cards with dimensions of 20 x 20 cm were placed at 45 and 60 m downwind.
+
+Each replication was considered as one pass of the sprayer, equivalent to 828 m2 in total area (91 m length x 9.1 m wide).
+Before each pass, a new set of mylar cards and petri dishes were placed at the sampling points.
+Five minutes after the end of each application was performed, cards and petri dishes were collected and placed individually into pre-labeled plastic bags.
+All samples were carefully managed to avoid cross-contamination and stored into dark containers until further analysis in laboratory in order to prevent photodegradation of rhodamine dye.
+Samples were collected from the furthest to the nearest downwind distance.
+Different teams were designated to work at downwind, upwind, and in-swath zones, and gloves were changed between application passes.
+
+The targeted wind velocity was between 3.6 to 6.7 m s-1 and ± 30° of being perpendicular to the driveline before applying a treatment.
+When necessary, the driveline and application zone was shifted to maintain the ± 30° wind direction target.
+Meteorological conditions (air temperature, and relative humidity, wind speed, wind direction) were collected at 2 m height and 1-min intervals using a HOBO RX3000 Weather Station (Onset Computer Co., Bourne, MA, USA) positioned upwind of the sprayed area.
+The wind speed and direction data were collected using 2D WindSonic anemometers (Gill Instruments, Lymington, UK).
+The meteorological data for each respective treatment is listed in Figure 2.
+
+## Dye quantification
+
+Samples were taken to the laboratory for dye extraction and quantification using fluorometry technique.
+Distilled water was used as extraction solution added to each bag using a bottle top dispenser (LabSciences Inc., 60000-BTR, Reno, NV).
+Samples collected downwind were rinsed with 50 mL of distilled water, whereas samples collected upwind and in-swath were rinsed with 20 mL of distilled water.
+The samples were agitated for 15 s and then a 1.5 mL aliquot from each sample bag was drawn to fill a glass cuvette.
+The cuvette was placed in a rhodamine module inside a fluorometer (Trilogy 7200.000, Turner Designs, Sunnyvale, CA) using green light.
+Serial dilutions were performed upon each tank sample to generate calibration curves, which allowed the conversion of relative fluorescence unit into mg L-1 and further expressing data into ɳL cm-2.
 

### 2021-07-14 manuscript.tex
h

@@
 Werle}
-\date{2021-06-22}
+\date{2021-07-14}
 
@@
 
+\hypertarget{experimental-sites}{%
+\subsection{Experimental sites}\label{experimental-sites}}
+
+Field experiments were conducted in three locations: North Platte, NE
+(geographic coordinates) on September 11-12/2021; Arlington, WI
+(geographic coordinates) on September 15-16/2021; and city, MO
+(geographic coordinates) on September 18-20/2021. In NE, WI, and MO,
+applications were made on bare ground, corn stubble (XX cm height) and
+????, respectively. The fields were flat and with no surrounding trees.
+Samples were processed and analyzed at the Pesticide Application
+Technology Laboratory of the University of Nebraska-Lincoln located in
+North Platte, Nebraska.
+
+\hypertarget{field-study}{%
+\subsection{Field study}\label{field-study}}
+
+Three factors were evaluated: sprayer type, nozzle type, and spray
+solution. Each experimental treatment was replicated 10 times. Two
+sprayers (Manufacturer, city, state) were employed for this study, the
+only difference being the inclusion of a hood or no hood. These sprayers
+were 9.1 meters in width and each had a 1130 L polyethylene tank. Spray
+delivery was accomplished via a hydraulic pump driven by the
+accompanying tractor. Each sprayer was connected to its own tractor via
+the three-point hitch system. Nozzle spacing was 51 cm, and boom height
+was set at 90 cm above the ground level for both sprayers. The wind
+skirt on the hooded sprayer was set slightly above the soil surface or
+corn stubble. The height for each sprayer was maintained throughout the
+study via the sprayers' guide wheels and the tractors' hitch system. The
+hood was constructed of molded, polymer plastic that surrounded the
+nozzles (Manufacturer, city, state). The hood sections reached
+approximately 30.5 cm below the nozzle orifices, and a plastic curtain
+reached a further 10 cm below the plastic hood. Nozzles were properly
+attached to the boom in order to get no interference of hood and nozzle
+plume.
+
+Nozzle types were TTI11003 and AIXR11003 (Teejet Technologies, Wheaton,
+IL), and ULD12003 (Pentair, Minneapolis, MN). All nozzles have air
+inclusion features and the carrier volume was 140 L ha\^{}-1 applied at
+276 kPa operating pressure and 2.6 m s-1 application speed.
+
+The spray solutions were prepared at the same day of applications and
+were water alone and water plus a drift-reducing adjuvant based on
+polyethylene glycol, choline chloride, and guar gum (IntactTM, Precision
+Laboratories, LLC, Waukegan, IL) at a rate of 0.5\% v v-1. Additionally,
+a rhodamine fluorescent dye (Red Dye, Cole-Parmer, Vernon Hills, IL) was
+added to all solutions at a rate of 0.5\% v v-1. The volumetric median
+diameter (VMD) of droplets and volume percentage of droplets finer than
+200 μm (V200) were measured at the Pesticide Application Technology
+Laboratory using a Sympatec Helos-Vario K/R laser diffraction system
+(Sympatec Inc., Clausthal, Germany), setup with a R7 lens, with a
+dynamic size range of 9 to 1,800 μm. The distance from the nozzle tip to
+the laser was 0.3 m. The VMD and V200 for each combination spray
+solution versus nozzle type are listed in Table 1.
+
+\hypertarget{application-and-field-layout}{%
+\subsection{Application and field
+layout}\label{application-and-field-layout}}
+
+Prior to the applications, 27 drift collection stations were placed
+downwind of the sprayed area in three transects (spaced by 7.6 m) and
+perpendicular to the spray line (Figure 1). For each transect,
+collectors were positioned at 1, 2, 3, 4, 8, 16, 31, 45, 60 m from the
+edge of the application zone. Additionally, three drift stations were
+placed 5 m upwind from the edge of the application zone and four petri
+dishes (150 mm diameter) were placed in-swath. All collectors were
+positioned 10 cm above the ground surface. Mylar cards (Grafix Plastics,
+Cleveland, OH) were used as drift collectors. Cards with dimensions of
+10 x 10 cm were placed upwind and up to 31 m downwind, whereas cards
+with dimensions of 20 x 20 cm were placed at 45 and 60 m downwind.
+
+Each replication was considered as one pass of the sprayer, equivalent
+to 828 m2 in total area (91 m length x 9.1 m wide). Before each pass, a
+new set of mylar cards and petri dishes were placed at the sampling
+points. Five minutes after the end of each application was performed,
+cards and petri dishes were collected and placed individually into
+pre-labeled plastic bags. All samples were carefully managed to avoid
+cross-contamination and stored into dark containers until further
+analysis in laboratory in order to prevent photodegradation of rhodamine
+dye. Samples were collected from the furthest to the nearest downwind
+distance. Different teams were designated to work at downwind, upwind,
+and in-swath zones, and gloves were changed between application passes.
+
+The targeted wind velocity was between 3.6 to 6.7 m s-1 and ± 30° of
+being perpendicular to the driveline before applying a treatment. When
+necessary, the driveline and application zone was shifted to maintain
+the ± 30° wind direction target. Meteorological conditions (air
+temperature, and relative humidity, wind speed, wind direction) were
+collected at 2 m height and 1-min intervals using a HOBO RX3000 Weather
+Station (Onset Computer Co., Bourne, MA, USA) positioned upwind of the
+sprayed area. The wind speed and direction data were collected using 2D
+WindSonic anemometers (Gill Instruments, Lymington, UK). The
+meteorological data for each respective treatment is listed in Figure 2.
+
+\hypertarget{dye-quantification}{%
+\subsection{Dye quantification}\label{dye-quantification}}
+
+Samples were taken to the laboratory for dye extraction and
+quantification using fluorometry technique. Distilled water was used as
+extraction solution added to each bag using a bottle top dispenser
+(LabSciences Inc., 60000-BTR, Reno, NV). Samples collected downwind were
+rinsed with 50 mL of distilled water, whereas samples collected upwind
+and in-swath were rinsed with 20 mL of distilled water. The samples were
+agitated for 15 s and then a 1.5 mL aliquot from each sample bag was
+drawn to fill a glass cuvette. The cuvette was placed in a rhodamine
+module inside a fluorometer (Trilogy 7200.000, Turner Designs,
+Sunnyvale, CA) using green light. Serial dilutions were performed upon
+each tank sample to generate calibration curves, which allowed the
+conversion of relative fluorescence unit into mg L-1 and further
+expressing data into ɳL cm-2.
+
 Solution, sprayer and nozzle factors were grouped as a single fixed
@@
 inference uses Markov chain Monte Carlo algorithms for sampling a
-probability distribution;\textsuperscript{2} and avoid singular fit from
-frequentist linear models when using complex random effects.
+probability distribution;\textsuperscript{2} and avoids singular fit
+from frequentist linear models when using complex random effects.
 
@@
 Data was fitted to a mixed model using \emph{brm} function. Treatments
-were the fixed effects and block nested within location random effects.
+were the fixed effects and blocks nested within location random effects.
 Model family was gaussian and prior distribution was set to student-t
@@
 posterior summaries (mean and highest posterior density) were estimated
-with \emph{emmeans} function from ``emmeans'' package. Treatment means
-were compared using Bayes Factor (BF).\textsuperscript{3,4} In short, if
-BF \textgreater{} 1 there is evidence for H1 (difference between
-treatments); whereas, if H0 \textless{} 1 there is evidence for H0 (no
-difference between treatments). If BF = 1, there is no evidence. The
-level of evidence (anecdotal, moderate, strong, very strong, and
-extreme) varies as the BF value increase (evidence for H1) or decrease
+with \emph{emmeans} function from the ``emmeans'' package. Treatment
+means were compared using Bayes Factor (BF).\textsuperscript{3,4} In
+short, if BF \textgreater{} 1 there is evidence for H1 (difference
+between treatments); whereas, if H0 \textless{} 1 there is evidence for
+H0 (no difference between treatments). If BF = 1, there is no evidence.
+The level of evidence (anecdotal, moderate, strong, very strong, and
+extreme) varies as the BF value increases (evidence for H1) or decreases
 (evidence for H0).
@@
 meet linearity. A single model was fitted to each treatment. For each
-model, treatments and distance were the fixed effects and block nested
+model, treatments and distance were the fixed effects and blocks nested
 within location random effects. Model family was gaussian and prior
@@
 The area under the curve (AUC) was used to validate the linear models.
-The spray solution deposition across distances within a experimental
+The spray solution deposition across distances within an experimental
 unit were used to calculate the absolute AUC value. The AUC was
-performed with \emph{audps} function from ``agricolae'' package. The AUC
-is commonly used for plant disease progress\textsuperscript{5,6} but has
-been used to calculate herbicide injury.\textsuperscript{7} Data was
+performed with \emph{audps} function from the ``agricolae'' package. The
+AUC is commonly used for plant disease progress\textsuperscript{5,6} but
+has been used to calculate herbicide injury.\textsuperscript{7} Data was
 fitted to a mixed model using \emph{brm} function. Treatments were the
-fixed effects and block nested within location random effects. Model
+fixed effects and blocks nested within location random effects. Model
 family was gaussian and prior distribution was set to student-t with
@@
 summaries (mean and highest posterior density) were estimated with
-\emph{emmeans} function from ``emmeans'' package. Treatment means were
-compared using Bayes Factor (BF) as above-mentioned.
+\emph{emmeans} function from the ``emmeans'' package. Treatment means
+were compared using Bayes Factor (BF) as above-mentioned.
 
@@
 Furthermore, there were less than 0.29 ηL cm\textsuperscript{-2} spray
-deposition at upwind with a strong evidence (BF \textless{} 0.25) of no
-difference between all pairwise treatments contrasts (data not shown).
+deposition at upwind with strong evidence (BF \textless{} 0.25) of no
+difference between all pairwise treatment contrasts (data not shown).
 
@@
 
-Similar trend was observed to AUC. Treatments with Hood or Open sprayer
+Similar trend was observed in AUC. Treatments with Hood or Open sprayer
 strongly impacted on AUC values (Figure 3B). The highest AUC values were
@@
 impact of Open and Hood sprayer is demonstrated in treatments including
-AIXR nozzle. There is a high difference in AUC (50.7) between
+AIXR nozzles. There is a high difference in AUC (50.7) between
 DRA-Open-AIXR vs DRA-Hood-AIXR (BF \textgreater{} 100). Moreover,

### 2021-07-15 manuscript.Rmd
bv

@@
 ---
-title: "Spray particle drift"
-author: Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo Werle
+title: "Off-target spray particle movement"
+author: 
+  - "Rodrigo Werle"
+  - "Bruno C Vieira"
+  - "Maxwel C. Oliveira"
+  - "Guilherme Alves"
+  - "Greg Kruger"
 date: "`r format(Sys.Date())`"
@@
 
+Integrate pest management The off-target particle movement
+
+The introduction of
+
+The objective of this study was to compare
+
 # Materials and Methods
 
-## Experimental sites
+## Field study
 
 Field experiments were conducted in three locations: North Platte, NE (geographic coordinates) on September 11-12/2021; Arlington, WI (geographic coordinates) on September 15-16/2021; and city, MO (geographic coordinates) on September 18-20/2021.
-In NE, WI, and MO, applications were made on bare ground, corn stubble (XX cm height) and ????, respectively.
+Applications were made on bare ground, corn stubble (XX cm height) and ????
+in NE, WI, and MO, respectively.
 The fields were flat and with no surrounding trees.
 Samples were processed and analyzed at the Pesticide Application Technology Laboratory of the University of Nebraska-Lincoln located in North Platte, Nebraska.
-
-## Field study
 
@@
 
-## Application and field layout
+### Application and field layout
 
@@
 
-## Dye quantification
+### Dye quantification
 
@@
 
-Solution, sprayer and nozzle factors were grouped as a single fixed effect (herein treatments) due to missing factor water in Missouri. Resulting in a combination of 12 treatments.
+## Greenhouse study
+
+A completely randomized design
 
@@
 
-### Spray solution deposition at upwind and inswath
+### Field study
+
+Solution, sprayer and nozzle factors were grouped as a single fixed effect (herein treatments) due to missing factor water in Missouri. Resulting in a combination of 12 treatments.
+
+#### Spray solution deposition at upwind and inswath
 
@@
 
-### Spray solution deposition at downwind
+#### Spray solution deposition at downwind
 
@@
 The AUC was performed with *audps* function from the "agricolae" package.
-The AUC is commonly used for plant disease progress [@meenaAreaDiseaseProgress2011; @simkoAreaDiseaseProgress2011] but has been used to calculate herbicide injury @striegelSpraySolutionPH2021.
+The AUC is commonly used for plant disease progress [@meenaAreaDiseaseProgress2011; @simkoAreaDiseaseProgress2011] but has been used to calculate herbicide injury [@striegelSpraySolutionPH2021].
 Data was fitted to a mixed model using *brm* function.
@@
 Model family was gaussian and prior distribution was set to student-t with mean 0.5, standard deviation 3 and 11 degrees of freedom.
-The posterior summaries (mean and highest posterior density) were estimated with *emmeans* function from the "emmeans" package.
-Treatment means were compared using Bayes Factor (BF) as above-mentioned.
+The posterior summaries and treatment means were estimated and compared using Bayes Factor (BF) as above-mentioned.
 
-### Dv, Relative Span
+## Greenouse study
+
+The Dv(10,50,90), RS, and % drifable fines was fitted to a Bayesian linear mixed model using *brm* function.
+In the models, solution and nozzle were set as fixed effects.
+Model family was hurdle gamma and prior distribution was set to student-t with mean 0.5, standard deviation 1 and 2 degrees of freedom.
+For each response variable, two models were fitted: with and without interaction (solution and nozzle).
+A model comparison was made with **bayesfactor_models** from "bayestestR" package[@makowski2019] to investigate interaction significance.
+For all response variables (Dvs, RS and % drifable fines), the best model was with interaction.
+The posterior summaries and treatment means were estimated and compared using Bayes Factor (BF) as above-mentioned.
 

### 2021-07-15 manuscript.tex
bv

@@
 \hypersetup{
-  pdftitle={Spray particle drift},
-  pdfauthor={Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo Werle},
+  pdftitle={Off-target spray particle movement},
+  pdfauthor={Rodrigo Werle; Bruno C Vieira; Maxwel C. Oliveira; Guilherme Alves; Greg Kruger},
   hidelinks,
@@
 
-\title{Spray particle drift}
-\author{Maxwel C. Oliveira, Guilherme Alves, Greg Kruger and Rodrigo
-Werle}
-\date{2021-07-14}
+\title{Off-target spray particle movement}
+\author{Rodrigo Werle \and Bruno C Vieira \and Maxwel C.
+Oliveira \and Guilherme Alves \and Greg Kruger}
+\date{2021-07-15}
 
@@
 
+Integrate pest management The off-target particle movement
+
+The objective of this stu
+
 \hypertarget{materials-and-methods}{%
@@
 
-\hypertarget{experimental-sites}{%
-\subsection{Experimental sites}\label{experimental-sites}}
+\hypertarget{field-study}{%
+\subsection{Field study}\label{field-study}}
 
@@
 (geographic coordinates) on September 15-16/2021; and city, MO
-(geographic coordinates) on September 18-20/2021. In NE, WI, and MO,
-applications were made on bare ground, corn stubble (XX cm height) and
-????, respectively. The fields were flat and with no surrounding trees.
+(geographic coordinates) on September 18-20/2021. Applications were made
+on bare ground, corn stubble (XX cm height) and ???? in NE, WI, and MO,
+respectively. The fields were flat and with no surrounding trees.
 Samples were processed and analyzed at the Pesticide Application
@@
 North Platte, Nebraska.
-
-\hypertarget{field-study}{%
-\subsection{Field study}\label{field-study}}
 
@@
 \hypertarget{application-and-field-layout}{%
-\subsection{Application and field
+\subsubsection{Application and field
 layout}\label{application-and-field-layout}}
@@
 \hypertarget{dye-quantification}{%
-\subsection{Dye quantification}\label{dye-quantification}}
+\subsubsection{Dye quantification}\label{dye-quantification}}
 
@@
 
-Solution, sprayer and nozzle factors were grouped as a single fixed
-effect (herein treatments) due to missing factor water in Missouri.
-Resulting in a combination of 12 treatments.
+\hypertarget{greenhouse-study}{%
+\subsection{Greenhouse study}\label{greenhouse-study}}
+
+A completely randomized design
 
@@
 
+\hypertarget{field-study-1}{%
+\subsubsection{Field study}\label{field-study-1}}
+
+Solution, sprayer and nozzle factors were grouped as a single fixed
+effect (herein treatments) due to missing factor water in Missouri.
+Resulting in a combination of 12 treatments.
+
 \hypertarget{spray-solution-deposition-at-upwind-and-inswath}{%
-\subsubsection{Spray solution deposition at upwind and
+\paragraph{Spray solution deposition at upwind and
 inswath}\label{spray-solution-deposition-at-upwind-and-inswath}}
@@
 \hypertarget{spray-solution-deposition-at-downwind}{%
-\subsubsection{Spray solution deposition at
+\paragraph{Spray solution deposition at
 downwind}\label{spray-solution-deposition-at-downwind}}
@@
 mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior
-summaries (mean and highest posterior density) were estimated with
-\emph{emmeans} function from the ``emmeans'' package. Treatment means
-were compared using Bayes Factor (BF) as above-mentioned.
+summaries and treatment means were estimated and compared using Bayes
+Factor (BF) as above-mentioned.
 
-\hypertarget{dv-relative-span}{%
-\subsubsection{Dv, Relative Span}\label{dv-relative-span}}
+\hypertarget{greenouse-study}{%
+\subsection{Greenouse study}\label{greenouse-study}}
+
+The Dv(10,50,90), RS, and \% drifable fines was fitted to a Bayesian
+linear mixed model using \emph{brm} function. In the models, solution
+and nozzle were set as fixed effects. Model family was hurdle gamma and
+prior distribution was set to student-t with mean 0.5, standard
+deviation 1 and 2 degrees of freedom. For each response variable, two
+models were fitted: with and without interaction (solution and nozzle).
+A model comparison was made with \textbf{bayesfactor\_models} from
+``bayestestR'' package\textsuperscript{8} to investigate interaction
+significance. For all response variables (Dvs, RS and \% drifable
+fines), the best model was with interaction. The posterior summaries and
+treatment means were estimated and compared using Bayes Factor (BF) as
+above-mentioned.
 
@@
 
-\hypertarget{dv-relative-span-1}{%
-\subsection{Dv, Relative Span}\label{dv-relative-span-1}}
+\hypertarget{dv-relative-span}{%
+\subsection{Dv, Relative Span}\label{dv-relative-span}}
 
@@
 
+\leavevmode\hypertarget{ref-makowski2019}{}%
+\CSLLeftMargin{8 }
+\CSLRightInline{Makowski D, Ben-Shachar M, and Lüdecke D, {bayestestR}:
+{Describing Effects} and their {Uncertainty}, {Existence} and
+{Significance} within the {Bayesian Framework}, \emph{JOSS}
+\textbf{4}:1541 (2019).}
+
 \end{CSLReferences}

### 2021-08-04 manuscript.Rmd
as

@@
 csl: pms.csl
-bibliography: biblio.bib
+bibliography: spray-pms.bib
 output:
@@
 
-Integrate pest management The off-target particle movement
+The widespread cases of glyphosate-resistant weeds throughout the US motivated farmers to adopt dicamba and 2,4-D tolerant crops [@behrens2007; @heap2018; @sammons2014; @werle2018; @wright2010].
+As expected, the agricultural usage of dicamba and 2,4-D significantly increased in the US (“United States Department of Agriculture” 2020).
+Applications of dicamba and 2,4-D in new cropping areas during extended time in the growing season has led to increased opportunities for the off-target movement of these herbicides [@soltaniOfftargetMovementAssessment2020; @werle2021].
+Spray drift is one of the main mechanisms of pesticide off-target movement and can be defined as the part of the pesticide application deflected away from the target area during or following applications [@matthews2008].
+Herbicide drift potential is influenced by application technique, environmental conditions, and surrounding vegetation [@alheidary2014; @arvidsson2011; @felsot2010; @hewitt2000; @nordby1974].
 
-The introduction of
+Dicamba and 2,4-D spray drift is a concern because these herbicides are very active on broadleaf vegetation, including soybean and cotton, causing distinctive crop injury and yield loss at very low dose exposures [@egan2014].
+The adoption of best management practices during herbicide applications, including proper nozzle selection and the use of drift reducing adjuvants, are among the main strategies to manage spray droplet size and mitigate spray drift [@etheridge1999; @hewitt2008; @hilz2013].
+New dicamba and 2,4-D products are mostly applied using venturi nozzles with air-inclusion and pre-orifice components that increase spray droplet size and reduce spray drift potential [@creech2015; @dorr2013].
+Despite the advances in nozzle technology [@dorr2013], pesticide formulations and adjuvants [@hilz2013], spraying techniques [@butts2019], strategies to mitigate spray drift [@felsot2010], and education and extension efforts [@butts2021; @werle2018], dicamba and 2,4-D spray drift remains associated with crop injury complaints across the US.
+In addition to this, common practices to mitigate spray drift, such as the use of DRAs with venturi nozzles in combination with lower pressures and boom heights, could potentially compromise spray uniformity, deposition, and weed control [@wolf1993] (Moraes et al.
+2021).
 
-The objective of this study was to compare
+The use of spray shields or hoods is another strategy to mitigate spray drift during pesticide applications [@burnside1968; @foster2018; @ozkan1997; @d.b.smith1982; @wolf1993].
+These devices generally reduce spray drift potential by minimizing spray exposure to wind.
+Foster et al.
+(2018)[@foster2018] reported that a hooded sprayer reduced spray drift potential in approximately 50% regardless of the nozzles used compared to conventional applications.
+The use of spray hoods can potentially extend the available time for applications during windy conditions and allow the use of finer droplets with lower carrier volumes to optimize spray coverage and weed control [@wolf1993].
+Although the benefits of sprayer hoods have been studies and reported since the early fifties, the technique adoption has been relatively low among farmers and applicators [@nordby1974].
+With the increased usage of dicamba and 2,4-D and the spray drift incidents associated with both herbicides, crop protection professionals renewed their interest in spray hoods to further mitigate herbicide off-target movement during applications.
+Therefore, the objective of this study was to evaluate the effectiveness of spray hoods in reducing pesticide drift for spray solutions and nozzles typically used for new auxinic herbicide products.
 
@@
 
-## Spray solution deposition at inswath and upwind
+## Droplet size
+
+As expected, the TTI nozzle produced coarser spray classification compared to the ULD and the AIXR nozzles across all spray solutions tested.
+In a response surface modeling approach in which nozzles were tested at different operational setups, TTI nozzles had greater percentage of operational setups producing Ultra Coarse (90%) spray classification compared to ULD (2%) and AIXR (0%) nozzles [@fritz2016].
+Legleiter et al.
+(2018)[@legleiter2018] reported that glyphosate + 2,4-D (premixture formulation) applications using a TTI11004 nozzle produced coarser spray classification (Ultra Coarse) when compared to AIXR11004 (Very Coarse), TT11004 (Coarse), and XR11004 (Medium) nozzles.
+Alves et al.
+(2020)[@alves2020] reported that applications of different dicamba formulations using a TTI110015 nozzle had larger droplet size across all formulations when compared to applications using an AIXR110015 nozzle.
+Zaric (2020)[@zaric2020] reported that the TTI11004 nozzle consistently produced coarser spray droplet size across multiple spray solutions when compared to the ULD12004 nozzle.
+
+Creech et al.
+(2015)[@creech2015] reported that nozzle design had major effects on spray droplet size, whereas spray solution influenced droplet spectrum to a less extent.
+The addition of DRA increased spray droplet size across all nozzles tested herein.
+Samples et al.
+(2021)[@samples2021] reported that the addition of DRAs (polymer and guargum) increased the spray droplet size of herbicide spray mixtures containing combinations of glyphosate, glufosinate, acetochlor, *S*-metolachlor, dicamba, fomesafen, and/or 2,4-D applied with an AIXR11005 nozzle.
+Zaric (2020)[@zaric2020] reported that the addition of DRAs consistently increased spray droplet size for dicamba applications using TTI1104 and ULD12004 spray nozzles.
+These findings highlight the specific instructions regarding nozzle selection for the new dicamba products (“Engenia Product Label” 2021, “Xtendimax Product Label” 2021), in which nozzles producing Ultra Coarse spray classifications are approved for applications.
+Label instructions for new 2,4-D formulations are more flexible in terms of nozzle selection, where Coarse, Very Coarse, and Extremely Coarse spray classifications are allowed (“Enlist Duo Product Label” 2021, “Enlist One Product Label” 2021).
+New dicamba and 2,4-D product labels also include specific DRAs to be used, especially when products are tank mixed with other pesticides.
+
+## Spray solution deposition in-swath
+
+For conventional applications (open) without DRA, the TTI nozzle had greater in-swath spray deposition volume on petri dishes compared to the ULD and AIXR nozzles.
+It has been previously reported that applications with Ultra Coarse spray had greater in-swath deposition volume on petri dishes compared to finer spray classifications [@vieira2018].
+Finer sprays have a greater percentage of spray volume comprised of small droplets that are more susceptible to spray drift [@dorr2013].
+These small droplets have more aerodynamic drag and lose their initial momentum rapidly, therefore having their trajectory highly influenced by the wind compared to coarser droplets [@knoche1994].
+It is important to highlight that greater spray deposition volume collected on petri dishes does not mean greater spray coverage, as coarser sprays result in reduced spray coverage when compared to finer spray classifications [@knoche1994; @legleiter2018].
+
+For conventional applications (open), the addition of DRA consistently increased in-swath spray deposition volume (petri dishes) compared to applications without DRA.
+Samples et al.
+(2021) [@samples2021] reported that the addition of DRAs (polymer and guargum) to several herbicide tank mixtures had inconsistent deposition results on soybean and cotton when compared to herbicide applications without adjuvants.
+Authors reported that while the addition of polymer and guargam based adjuvants increased cotton spray deposition for glyphosate + dicamba + *S*-Metolachlor spray mixture, the same adjuvants had no effect or decreased cotton spray deposition when mixed to glyphosate + 2,4-D.
+Moraes et al.
+(2021) (Moraes et al.
+2021) reported that the addition of DRAs could have a negative effect on spray uniformity, especially with nozzles producing coarser spray classifications at lower spray pressures.
+
+Results reported herein indicate an inconsistent effect of hooded sprayers on in-swath spray deposition.
+For applications with DRA, the conventional sprayer (open) had greater in-swath deposition compared to hooded applications.
+On the other hand, for applications without DRA, the hooded sprayer had greater in-swath deposition compared to the conventional sprayer.
+Wolf et al.
+(1993) [@wolf1993] observed that solid spray shields generally decreased in-swath deposition uniformity.
+Authors noted that spray solution dripping from sprayer shield walls could increase the in-swath deposition variability during applications.
+Wolf et al (1993) [@wolf1993] and Moraes et al.
+(2021) observations could explain the lower spray deposition obtained for hooded applications with the addition of the DRA, although this hypothesis needs to be further investigated.
 
 ## Spray solution deposition at downwind
+
+For conventional (open) applications without DRA, the TTI nozzle had less drift potential compared to AIXR and ULD nozzles, as expected.
+Alves et al.
+(2020) [@alves2020] reported similar results in a wind tunnel study, where applications of different dicamba formulations using a TTI nozzle had less spray drift compared to applications using an AIXR nozzle.
+Authors reported that soybean plants were still showing 50% biomass reduction from 9.9 to 13.4 m downwind the nozzle for applications with the AIXR nozzle, whereas this distance range was reduced to 6.4 to 7.2 m for applications using the TTI nozzle.
+In another wind tunnel study, Alves et al.
+(2017) [@alves2017] reported that dicamba applications with a TTI nozzle had 0.6% spray drift at 12 m downwind the nozzle, whereas applications with XR, TT, and AIXR nozzles had 13.5, 6.6, and 3.2% drift, respectively.
+As previously reported [@hilz2013; @johnson2006], the addition of DRA reduced spray drift across all nozzles tested herein.
+
+Hooded applications substantially reduced spray drift potential across all treatment scenarios.
+For instance, hooded applications using the AIXR nozzle without DRA had similar drift potential compared to conventional applications using the TTI nozzle with DRA despite the major droplet size differences between these treatments.
+These results indicate that the adoption of spray hoods combined with proper nozzle selection and the addition of DRAs to the spray solution can substantially reduce spray drift potential during pesticide applications.
+Foster et al.
+(2018)[@foster2018] reported that the advent of spray hood considerably reduced spray drift for glyphosate applications using Fine, Medium, Very Coarse, and Ultra Coarse spray qualities.
+In a wind tunnel study, Ozkan et al.
+(1997)[@ozkan1997] reported that several spray shields were effective in reducing spray drift, where a double-foil shield reduced spray drift in 59% compared to applications without shields.
+In laboratory tests, Smith et al.
+(1982) reported that a spray shield could reduce spray drift up to 70%, although field studies indicated an inconsistent performance where spray shields either increased or decreased spray drift during tests.
+
+The results reported in this study highlight the importance of adopting best management practices during pesticide applications to mitigate spray off-target movement to the surrounding environment.
+Hooded applications with AIXR and ULD nozzles resulted in satisfactory spray drift reduction despite the finer droplet spectrum compared to the TTI nozzle.
+This could have implications for weed control as applications with Ultra Coarse droplet spectrum have reduced spray coverage compared to finer spray classifications.
+Legleiter et al.
+(2018)[@legleiter2018] reported that glyphosate + 2,4-D applications with Ultra Coarse (TTI11004) spray had reduced spray coverage on artificial targets (cards) compared to Medium (XR11004), Coarse (TT11004), and Very Coarse (AIXR11004) sprays.
+However, authors reported that spray droplet spectrum did not influence 2,4-D absorption in Palmer amaranth (*Amaranthus palmeri*), waterhemp (*Amaranthus tuberculatus*), giant ragweed (*Ambrosia trifida*), and horseweed (*Erigeron canadensis*).
+Increasing the application carrier volume is one strategy to overcome the reduced coverage from applications using coarser sprays.
+Butts et al.
+(2018) [@butts2018] reported that dicamba applications with Ultra Coarse spray resulted in optimal weed control for applications at 187 L ha-1, whereas Extremely Coarse spray resulted optimal weed control for glufosinate applications.
+However, applications with increased spray carrier volume are less efficient due to additional time and water requirements during the operation [@wolf1993].
+Hooded applications using AIXR and ULD nozzles can provide increased spray coverage compared to TTI nozzles while having low drift potential, which allows for applications at reduced carrier volumes.
+
+Because of the substantial drift reduction, applications with hooded sprayers could also reduce product buffer zone requirements.
+New dicamba formulations provide incentives to the use of qualified hooded sprayers by decreasing the required downwind buffer from 73 m to 33 m (“Engenia Product Label” 2021, “Xtendimax Product Label” 2021).
+Although the benefits associated with hooded sprayers, the technology has not been well accepted by farmers.
+Nordby and Skuterud (1974) [@nordby1974] mentioned that farmers could see spray hoods as cumbersome and expensive devices that do not allow applicators to check nozzles during applications.
+Considering the widespread adoption of dicamba and 2,4-D tolerant crops and the increase in these herbicide usage, hooded sprayers could be a very effective technique to mitigate spray drift during pesticide applications.
 

### 2021-08-04 manuscript.tex
as

@@
 Oliveira \and Guilherme Alves \and Greg Kruger}
-\date{2021-07-15}
+\date{2021-08-04}
 
@@
 
-Integrate pest management The off-target particle movement
+The widespread cases of glyphosate-resistant weeds throughout the US
+motivated farmers to adopt dicamba and 2,4-D tolerant
+crops.\textsuperscript{1--5} As expected, the agricultural usage of
+dicamba and 2,4-D significantly increased in the US (``United States
+Department of Agriculture'' 2020). Applications of dicamba and 2,4-D in
+new cropping areas during extended time in the growing season has led to
+increased opportunities for the off-target movement of these
+herbicides.\textsuperscript{6,7} Spray drift is one of the main
+mechanisms of pesticide off-target movement and can be defined as the
+part of the pesticide application deflected away from the target area
+during or following applications.\textsuperscript{8} Herbicide drift
+potential is influenced by application technique, environmental
+conditions, and surrounding vegetation.\textsuperscript{9--13}
 
-The objective of this stu
+Dicamba and 2,4-D spray drift is a concern because these herbicides are
+very active on broadleaf vegetation, including soybean and cotton,
+causing distinctive crop injury and yield loss at very low dose
+exposures.\textsuperscript{14} The adoption of best management practices
+during herbicide applications, including proper nozzle selection and the
+use of drift reducing adjuvants, are among the main strategies to manage
+spray droplet size and mitigate spray drift.\textsuperscript{15--17} New
+dicamba and 2,4-D products are mostly applied using venturi nozzles with
+air-inclusion and pre-orifice components that increase spray droplet
+size and reduce spray drift potential.\textsuperscript{18,19} Despite
+the advances in nozzle technology,\textsuperscript{19} pesticide
+formulations and adjuvants,\textsuperscript{17} spraying
+techniques,\textsuperscript{20} strategies to mitigate spray
+drift,\textsuperscript{11} and education and extension
+efforts,\textsuperscript{4,21} dicamba and 2,4-D spray drift remains
+associated with crop injury complaints across the US. In addition to
+this, common practices to mitigate spray drift, such as the use of DRAs
+with venturi nozzles in combination with lower pressures and boom
+heights, could potentially compromise spray uniformity, deposition, and
+weed control\textsuperscript{22} (Moraes et al.~2021).
+
+The use of spray shields or hoods is another strategy to mitigate spray
+drift during pesticide applications.\textsuperscript{22--26} These
+devices generally reduce spray drift potential by minimizing spray
+exposure to wind. Foster et al.~(2018)\textsuperscript{24} reported that
+a hooded sprayer reduced spray drift potential in approximately 50\%
+regardless of the nozzles used compared to conventional applications.
+The use of spray hoods can potentially extend the available time for
+applications during windy conditions and allow the use of finer droplets
+with lower carrier volumes to optimize spray coverage and weed
+control.\textsuperscript{22} Although the benefits of sprayer hoods have
+been studies and reported since the early fifties, the technique
+adoption has been relatively low among farmers and
+applicators.\textsuperscript{13} With the increased usage of dicamba and
+2,4-D and the spray drift incidents associated with both herbicides,
+crop protection professionals renewed their interest in spray hoods to
+further mitigate herbicide off-target movement during applications.
+Therefore, the objective of this study was to evaluate the effectiveness
+of spray hoods in reducing pesticide drift for spray solutions and
+nozzles typically used for new auxinic herbicide products.
 
@@
 The statistical analyses were conducted with R statistical software
-version 4.1.0.\textsuperscript{1} Data analyses were performed with
-Bayesian inference with ``brms'' package.\textsuperscript{2} Bayesian
+version 4.1.0.\textsuperscript{27} Data analyses were performed with
+Bayesian inference with ``brms'' package.\textsuperscript{28} Bayesian
 inference uses Markov chain Monte Carlo algorithms for sampling a
-probability distribution;\textsuperscript{2} and avoids singular fit
+probability distribution;\textsuperscript{28} and avoids singular fit
 from frequentist linear models when using complex random effects.
@@
 with \emph{emmeans} function from the ``emmeans'' package. Treatment
-means were compared using Bayes Factor (BF).\textsuperscript{3,4} In
+means were compared using Bayes Factor (BF).\textsuperscript{29,30} In
 short, if BF \textgreater{} 1 there is evidence for H1 (difference
@@
 performed with \emph{audps} function from the ``agricolae'' package. The
-AUC is commonly used for plant disease progress\textsuperscript{5,6} but
-has been used to calculate herbicide injury.\textsuperscript{7} Data was
-fitted to a mixed model using \emph{brm} function. Treatments were the
-fixed effects and blocks nested within location random effects. Model
-family was gaussian and prior distribution was set to student-t with
-mean 0.5, standard deviation 3 and 11 degrees of freedom. The posterior
-summaries and treatment means were estimated and compared using Bayes
-Factor (BF) as above-mentioned.
+AUC is commonly used for plant disease progress\textsuperscript{31,32}
+but has been used to calculate herbicide injury.\textsuperscript{33}
+Data was fitted to a mixed model using \emph{brm} function. Treatments
+were the fixed effects and blocks nested within location random effects.
+Model family was gaussian and prior distribution was set to student-t
+with mean 0.5, standard deviation 3 and 11 degrees of freedom. The
+posterior summaries and treatment means were estimated and compared
+using Bayes Factor (BF) as above-mentioned.
 
@@
 A model comparison was made with \textbf{bayesfactor\_models} from
-``bayestestR'' package\textsuperscript{8} to investigate interaction
+``bayestestR'' package\textsuperscript{34} to investigate interaction
 significance. For all response variables (Dvs, RS and \% drifable
@@
 
-\hypertarget{spray-solution-deposition-at-inswath-and-upwind-1}{%
-\subsection{Spray solution deposition at inswath and
-upwind}\label{spray-solution-deposition-at-inswath-and-upwind-1}}
+\hypertarget{droplet-size}{%
+\subsection{Droplet size}\label{droplet-size}}
+
+As expected, the TTI nozzle produced coarser spray classification
+compared to the ULD and the AIXR nozzles across all spray solutions
+tested. In a response surface modeling approach in which nozzles were
+tested at different operational setups, TTI nozzles had greater
+percentage of operational setups producing Ultra Coarse (90\%) spray
+classification compared to ULD (2\%) and AIXR (0\%)
+nozzles.\textsuperscript{35} Legleiter et al.~(2018)\textsuperscript{36}
+reported that glyphosate + 2,4-D (premixture formulation) applications
+using a TTI11004 nozzle produced coarser spray classification (Ultra
+Coarse) when compared to AIXR11004 (Very Coarse), TT11004 (Coarse), and
+XR11004 (Medium) nozzles. Alves et al.~(2020)\textsuperscript{37}
+reported that applications of different dicamba formulations using a
+TTI110015 nozzle had larger droplet size across all formulations when
+compared to applications using an AIXR110015 nozzle. Zaric
+(2020)\textsuperscript{38} reported that the TTI11004 nozzle
+consistently produced coarser spray droplet size across multiple spray
+solutions when compared to the ULD12004 nozzle.
+
+Creech et al.~(2015)\textsuperscript{18} reported that nozzle design had
+major effects on spray droplet size, whereas spray solution influenced
+droplet spectrum to a less extent. The addition of DRA increased spray
+droplet size across all nozzles tested herein. Samples et
+al.~(2021)\textsuperscript{39} reported that the addition of DRAs
+(polymer and guargum) increased the spray droplet size of herbicide
+spray mixtures containing combinations of glyphosate, glufosinate,
+acetochlor, \emph{S}-metolachlor, dicamba, fomesafen, and/or 2,4-D
+applied with an AIXR11005 nozzle. Zaric (2020)\textsuperscript{38}
+reported that the addition of DRAs consistently increased spray droplet
+size for dicamba applications using TTI1104 and ULD12004 spray nozzles.
+These findings highlight the specific instructions regarding nozzle
+selection for the new dicamba products (``Engenia Product Label'' 2021,
+``Xtendimax Product Label'' 2021), in which nozzles producing Ultra
+Coarse spray classifications are approved for applications. Label
+instructions for new 2,4-D formulations are more flexible in terms of
+nozzle selection, where Coarse, Very Coarse, and Extremely Coarse spray
+classifications are allowed (``Enlist Duo Product Label'' 2021, ``Enlist
+One Product Label'' 2021). New dicamba and 2,4-D product labels also
+include specific DRAs to be used, especially when products are tank
+mixed with other pesticides.
+
+\hypertarget{spray-solution-deposition-in-swath}{%
+\subsection{Spray solution deposition
+in-swath}\label{spray-solution-deposition-in-swath}}
+
+For conventional applications (open) without DRA, the TTI nozzle had
+greater in-swath spray deposition volume on petri dishes compared to the
+ULD and AIXR nozzles. It has been previously reported that applications
+with Ultra Coarse spray had greater in-swath deposition volume on petri
+dishes compared to finer spray classifications.\textsuperscript{40}
+Finer sprays have a greater percentage of spray volume comprised of
+small droplets that are more susceptible to spray
+drift.\textsuperscript{19} These small droplets have more aerodynamic
+drag and lose their initial momentum rapidly, therefore having their
+trajectory highly influenced by the wind compared to coarser
+droplets.\textsuperscript{41} It is important to highlight that greater
+spray deposition volume collected on petri dishes does not mean greater
+spray coverage, as coarser sprays result in reduced spray coverage when
+compared to finer spray classifications.\textsuperscript{36,41}
+
+For conventional applications (open), the addition of DRA consistently
+increased in-swath spray deposition volume (petri dishes) compared to
+applications without DRA. Samples et al.~(2021)\textsuperscript{39}
+reported that the addition of DRAs (polymer and guargum) to several
+herbicide tank mixtures had inconsistent deposition results on soybean
+and cotton when compared to herbicide applications without adjuvants.
+Authors reported that while the addition of polymer and guargam based
+adjuvants increased cotton spray deposition for glyphosate + dicamba +
+\emph{S}-Metolachlor spray mixture, the same adjuvants had no effect or
+decreased cotton spray deposition when mixed to glyphosate + 2,4-D.
+Moraes et al.~(2021) (Moraes et al.~2021) reported that the addition of
+DRAs could have a negative effect on spray uniformity, especially with
+nozzles producing coarser spray classifications at lower spray
+pressures.
+
+Results reported herein indicate an inconsistent effect of hooded
+sprayers on in-swath spray deposition. For applications with DRA, the
+conventional sprayer (open) had greater in-swath deposition compared to
+hooded applications. On the other hand, for applications without DRA,
+the hooded sprayer had greater in-swath deposition compared to the
+conventional sprayer. Wolf et al.~(1993)\textsuperscript{22} observed
+that solid spray shields generally decreased in-swath deposition
+uniformity. Authors noted that spray solution dripping from sprayer
+shield walls could increase the in-swath deposition variability during
+applications. Wolf et al (1993)\textsuperscript{22} and Moraes et
+al.~(2021) observations could explain the lower spray deposition
+obtained for hooded applications with the addition of the DRA, although
+this hypothesis needs to be further investigated.
 
@@
 downwind}\label{spray-solution-deposition-at-downwind-2}}
+
+For conventional (open) applications without DRA, the TTI nozzle had
+less drift potential compared to AIXR and ULD nozzles, as expected.
+Alves et al.~(2020)\textsuperscript{37} reported similar results in a
+wind tunnel study, where applications of different dicamba formulations
+using a TTI nozzle had less spray drift compared to applications using
+an AIXR nozzle. Authors reported that soybean plants were still showing
+50\% biomass reduction from 9.9 to 13.4 m downwind the nozzle for
+applications with the AIXR nozzle, whereas this distance range was
+reduced to 6.4 to 7.2 m for applications using the TTI nozzle. In
+another wind tunnel study, Alves et al.~(2017)\textsuperscript{42}
+reported that dicamba applications with a TTI nozzle had 0.6\% spray
+drift at 12 m downwind the nozzle, whereas applications with XR, TT, and
+AIXR nozzles had 13.5, 6.6, and 3.2\% drift, respectively. As previously
+reported,\textsuperscript{17,43} the addition of DRA reduced spray drift
+across all nozzles tested herein.
+
+Hooded applications substantially reduced spray drift potential across
+all treatment scenarios. For instance, hooded applications using the
+AIXR nozzle without DRA had similar drift potential compared to
+conventional applications using the TTI nozzle with DRA despite the
+major droplet size differences between these treatments. These results
+indicate that the adoption of spray hoods combined with proper nozzle
+selection and the addition of DRAs to the spray solution can
+substantially reduce spray drift potential during pesticide
+applications. Foster et al.~(2018)\textsuperscript{24} reported that the
+advent of spray hood considerably reduced spray drift for glyphosate
+applications using Fine, Medium, Very Coarse, and Ultra Coarse spray
+qualities. In a wind tunnel study, Ozkan et
+al.~(1997)\textsuperscript{25} reported that several spray shields were
+effective in reducing spray drift, where a double-foil shield reduced
+spray drift in 59\% compared to applications without shields. In
+laboratory tests, Smith et al.~(1982) reported that a spray shield could
+reduce spray drift up to 70\%, although field studies indicated an
+inconsistent performance where spray shields either increased or
+decreased spray drift during tests.
+
+The results reported in this study highlight the importance of adopting
+best management practices during pesticide applications to mitigate
+spray off-target movement to the surrounding environment. Hooded
+applications with AIXR and ULD nozzles resulted in satisfactory spray
+drift reduction despite the finer droplet spectrum compared to the TTI
+nozzle. This could have implications for weed control as applications
+with Ultra Coarse droplet spectrum have reduced spray coverage compared
+to finer spray classifications. Legleiter et
+al.~(2018)\textsuperscript{36} reported that glyphosate + 2,4-D
+applications with Ultra Coarse (TTI11004) spray had reduced spray
+coverage on artificial targets (cards) compared to Medium (XR11004),
+Coarse (TT11004), and Very Coarse (AIXR11004) sprays. However, authors
+reported that spray droplet spectrum did not influence 2,4-D absorption
+in Palmer amaranth (\emph{Amaranthus palmeri}), waterhemp
+(\emph{Amaranthus tuberculatus}), giant ragweed (\emph{Ambrosia
+trifida}), and horseweed (\emph{Erigeron canadensis}). Increasing the
+application carrier volume is one strategy to overcome the reduced
+coverage from applications using coarser sprays. Butts et
+al.~(2018)\textsuperscript{44} reported that dicamba applications with
+Ultra Coarse spray resulted in optimal weed control for applications at
+187 L ha-1, whereas Extremely Coarse spray resulted optimal weed control
+for glufosinate applications. However, applications with increased spray
+carrier volume are less efficient due to additional time and water
+requirements during the operation.\textsuperscript{22} Hooded
+applications using AIXR and ULD nozzles can provide increased spray
+coverage compared to TTI nozzles while having low drift potential, which
+allows for applications at reduced carrier volumes.
+
+Because of the substantial drift reduction, applications with hooded
+sprayers could also reduce product buffer zone requirements. New dicamba
+formulations provide incentives to the use of qualified hooded sprayers
+by decreasing the required downwind buffer from 73 m to 33 m (``Engenia
+Product Label'' 2021, ``Xtendimax Product Label'' 2021). Although the
+benefits associated with hooded sprayers, the technology has not been
+well accepted by farmers. Nordby and Skuterud (1974)\textsuperscript{13}
+mentioned that farmers could see spray hoods as cumbersome and expensive
+devices that do not allow applicators to check nozzles during
+applications. Considering the widespread adoption of dicamba and 2,4-D
+tolerant crops and the increase in these herbicide usage, hooded
+sprayers could be a very effective technique to mitigate spray drift
+during pesticide applications.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-behrens2007}{}%
+\CSLLeftMargin{1 }
+\CSLRightInline{Behrens MR, Mutlu N, Chakraborty S, Dumitru R, Jiang WZ,
+LaVallee BJ, \emph{et al.}, Dicamba {Resistance}: {Enlarging} and
+{Preserving Biotechnology}-{Based Weed Management Strategies},
+\emph{Science} \textbf{316}:1185--1188, {American Association for the
+Advancement of Science} (2007).}
+
+\leavevmode\hypertarget{ref-heap2018}{}%
+\CSLLeftMargin{2 }
+\CSLRightInline{Heap I and Duke SO, Overview of glyphosate-resistant
+weeds worldwide, \emph{Pest Management Science} \textbf{74}:1040--1049
+(2018).}
+
+\leavevmode\hypertarget{ref-sammons2014}{}%
+\CSLLeftMargin{3 }
+\CSLRightInline{Sammons RD and Gaines TA, Glyphosate resistance: State
+of knowledge, \emph{Pest Management Science} \textbf{70}:1367--1377
+(2014).}
+
+\leavevmode\hypertarget{ref-werle2018}{}%
+\CSLLeftMargin{4 }
+\CSLRightInline{Werle R, Oliveira MC, Jhala AJ, Proctor CA, Rees J, and
+Klein R, Survey of {Nebraska Farmers}' {Adoption} of
+{Dicamba}-{Resistant Soybean Technology} and {Dicamba Off}-{Target
+Movement}, \emph{Weed Technol} \textbf{32}:754--761 (2018).}
+
+\leavevmode\hypertarget{ref-wright2010}{}%
+\CSLLeftMargin{5 }
+\CSLRightInline{Wright TR, Shan G, Walsh TA, Lira JM, Cui C, Song P,
+\emph{et al.}, Robust crop resistance to broadleaf and grass herbicides
+provided by aryloxyalkanoate dioxygenase transgenes, \emph{Proceedings
+of the National Academy of Sciences} \textbf{107}:20240--20245 (2010).}
+
+\leavevmode\hypertarget{ref-soltaniOfftargetMovementAssessment2020}{}%
+\CSLLeftMargin{6 }
+\CSLRightInline{Soltani N, Oliveira MC, Alves GS, Werle R, Norsworthy
+JK, Sprague CL, \emph{et al.}, Off-target movement assessment of dicamba
+in {North America}, \emph{Weed Technol} \textbf{34}:318--330 (2020).}
+
+\leavevmode\hypertarget{ref-werle2021}{}%
+\CSLLeftMargin{7 }
+\CSLRightInline{Werle R, Mobli A, Striegel S, Arneson N, DeWerff R,
+Brown A, \emph{et al.}, Large {Scale Evaluation} of 2,4-{D Choline
+Off}-target {Movement} and {Injury} in 2,4-{D}-susceptible {Soybean},
+\emph{Weed Technology}:1--22, {Cambridge University Press} (2021).}
+
+\leavevmode\hypertarget{ref-matthews2008}{}%
+\CSLLeftMargin{8 }
+\CSLRightInline{Matthews G, Pesticide {Application Methods}, {John Wiley
+\& Sons} (2008).}
+
+\leavevmode\hypertarget{ref-alheidary2014}{}%
+\CSLLeftMargin{9 }
+\CSLRightInline{Al Heidary M, Douzals JP, Sinfort C, and Vallet A,
+Influence of spray characteristics on potential spray drift of field
+crop sprayers: {A} literature review, \emph{Crop Protection}
+\textbf{63}:120--130 (2014).}
+
+\leavevmode\hypertarget{ref-arvidsson2011}{}%
+\CSLLeftMargin{10 }
+\CSLRightInline{Arvidsson T, Bergström L, and Kreuger J, Spray drift as
+influenced by meteorological and technical factors, \emph{Pest
+Management Science} \textbf{67}:586--598 (2011).}
+
+\leavevmode\hypertarget{ref-felsot2010}{}%
+\CSLLeftMargin{11 }
+\CSLRightInline{Felsot AS, Unsworth JB, Linders JBHJ, Roberts G, Rautman
+D, Harris C, \emph{et al.}, Agrochemical spray drift; assessment and
+mitigation---{A} review*, \emph{Journal of Environmental Science and
+Health, Part B} \textbf{46}:1--23, {Taylor \& Francis} (2010).}
+
+\leavevmode\hypertarget{ref-hewitt2000}{}%
+\CSLLeftMargin{12 }
+\CSLRightInline{Hewitt AJ, Spray drift: Impact of requirements to
+protect the environment, \emph{Crop Protection} \textbf{19}:623--627
+(2000).}
+
+\leavevmode\hypertarget{ref-nordby1974}{}%
+\CSLLeftMargin{13 }
+\CSLRightInline{Nordby A and Skuterud R, The effects of boom height,
+working pressure and wind speed on spray drift, \emph{Weed Research}
+\textbf{14}:385--395 (1974).}
+
+\leavevmode\hypertarget{ref-egan2014}{}%
+\CSLLeftMargin{14 }
+\CSLRightInline{Egan JF, Barlow KM, and Mortensen DA, A
+{Meta}-{Analysis} on the {Effects} of 2,4-{D} and {Dicamba Drift} on
+{Soybean} and {Cotton}, \emph{Weed Science} \textbf{62}:193--206,
+{Cambridge University Press} (2014).}
+
+\leavevmode\hypertarget{ref-etheridge1999}{}%
+\CSLLeftMargin{15 }
+\CSLRightInline{Etheridge RE, Womac AR, and Mueller TC, Characterization
+of the {Spray Droplet Spectra} and {Patterns} of {Four Venturi}-{Type
+Drift Reduction Nozzles}, \emph{Weed Technology} \textbf{13}:765--770,
+{Cambridge University Press} (1999).}
+
+\leavevmode\hypertarget{ref-hewitt2008}{}%
+\CSLLeftMargin{16 }
+\CSLRightInline{Hewitt AJ, Spray optimization through application and
+liquid physical property variables--{I}, \emph{Environmentalist}
+\textbf{28}:25--30 (2008).}
+
+\leavevmode\hypertarget{ref-hilz2013}{}%
+\CSLLeftMargin{17 }
+\CSLRightInline{Hilz E and Vermeer AWP, Spray drift review: {The} extent
+to which a formulation can contribute to spray drift reduction,
+\emph{Crop Protection} \textbf{44}:75--83 (2013).}
+
+\leavevmode\hypertarget{ref-creech2015}{}%
+\CSLLeftMargin{18 }
+\CSLRightInline{Creech CF, Henry RS, Fritz BK, and Kruger GR, Influence
+of {Herbicide Active Ingredient}, {Nozzle Type}, {Orifice Size}, {Spray
+Pressure}, and {Carrier Volume Rate} on {Spray Droplet Size
+Characteristics}, \emph{Weed Technology} \textbf{29}:298--310,
+{Cambridge University Press} (2015).}
+
+\leavevmode\hypertarget{ref-dorr2013}{}%
+\CSLLeftMargin{19 }
+\CSLRightInline{Dorr GJ, Hewitt AJ, Adkins SW, Hanan J, Zhang H, and
+Noller B, A comparison of initial spray characteristics produced by
+agricultural nozzles, \emph{Crop Protection} \textbf{53}:109--117
+(2013).}
+
+\leavevmode\hypertarget{ref-butts2019}{}%
+\CSLLeftMargin{20 }
+\CSLRightInline{Butts TR, Butts LE, Luck JD, Fritz BK, Hoffmann WC, and
+Kruger GR, Droplet size and nozzle tip pressure from a pulse-width
+modulation sprayer, \emph{Biosystems Engineering} \textbf{178}:52--69
+(2019).}
+
+\leavevmode\hypertarget{ref-butts2021}{}%
+\CSLLeftMargin{21 }
+\CSLRightInline{Butts TR, Barber LT, Norsworthy JK, and Davis J, Survey
+of ground and aerial herbicide application practices in {Arkansas}
+agronomic crops, \emph{Weed Technology} \textbf{35}:1--11, {Cambridge
+University Press} (2021).}
+
+\leavevmode\hypertarget{ref-wolf1993}{}%
+\CSLLeftMargin{22 }
+\CSLRightInline{Wolf TM, Grover R, Wallace K, Shewchuk SR, and Maybank
+J, Effect of protective shields on drift and deposition characteristics
+of field sprayers, \emph{Can J Plant Sci} \textbf{73}:1261--1273, {NRC
+Research Press} (1993).}
+
+\leavevmode\hypertarget{ref-burnside1968}{}%
+\CSLLeftMargin{23 }
+\CSLRightInline{Burnside OC, A {Shielded}, {Tractor}-{Mounted Sprayer}
+for {Research Plots}, \emph{Weed Science} \textbf{16}:386--388,
+{Cambridge University Press} (1968).}
+
+\leavevmode\hypertarget{ref-foster2018}{}%
+\CSLLeftMargin{24 }
+\CSLRightInline{Foster HC, Sperry BP, Reynolds DB, Kruger GR, and
+Claussen S, Reducing {Herbicide Particle Drift}: {Effect} of {Hooded
+Sprayer} and {Spray Quality}, \emph{Weed Technology}
+\textbf{32}:714--721, {Cambridge University Press} (2018).}
+
+\leavevmode\hypertarget{ref-ozkan1997}{}%
+\CSLLeftMargin{25 }
+\CSLRightInline{Ozkan H, Miralles A, Sinfort C, Zhu H, and Fox R,
+Shields to {Reduce Spray Drift}, \emph{Journal of Agricultural
+Engineering Research} \textbf{67}:311--322 (1997).}
+
+\leavevmode\hypertarget{ref-d.b.smith1982}{}%
+\CSLLeftMargin{26 }
+\CSLRightInline{D. B. Smith, F. D. Harris, and B. J. Butler, Shielded
+{Sprayer Boom} to {Reduce Drift}, \emph{Transactions of the ASAE}
+\textbf{25}:1136--1140 (1982).}
+
 \leavevmode\hypertarget{ref-LanguageEnvironmentStatistical2021}{}%
-\CSLLeftMargin{1 }
+\CSLLeftMargin{27 }
 \CSLRightInline{R: {A Language} and {Environment} for {Statistical
@@
 \leavevmode\hypertarget{ref-burknerBrmsPackageBayesian2017}{}%
-\CSLLeftMargin{2 }
+\CSLLeftMargin{28 }
 \CSLRightInline{Bürkner P-C, \textbf{Brms} : {An} {\emph{R}} {Package}
@@
 \leavevmode\hypertarget{ref-leeBayesianCognitiveModeling2014}{}%
-\CSLLeftMargin{3 }
+\CSLLeftMargin{29 }
 \CSLRightInline{Lee MD and Wagenmakers E-J, Bayesian {Cognitive
@@
 \leavevmode\hypertarget{ref-kassBayesFactors1995}{}%
-\CSLLeftMargin{4 }
+\CSLLeftMargin{30 }
 \CSLRightInline{Kass RE and Raftery AE, Bayes {Factors}, \emph{Journal
@@
 \leavevmode\hypertarget{ref-meenaAreaDiseaseProgress2011}{}%
-\CSLLeftMargin{5 }
+\CSLLeftMargin{31 }
 \CSLRightInline{Meena PD, Chattopadhyay C, Meena SS, and Kumar A, Area
@@
 \leavevmode\hypertarget{ref-simkoAreaDiseaseProgress2011}{}%
-\CSLLeftMargin{6 }
+\CSLLeftMargin{32 }
 \CSLRightInline{Simko I and Piepho H-P, The {Area Under} the {Disease
@@
 \leavevmode\hypertarget{ref-striegelSpraySolutionPH2021}{}%
-\CSLLeftMargin{7 }
+\CSLLeftMargin{33 }
 \CSLRightInline{Striegel S, Oliveira MC, Arneson N, Conley SP,
@@
 \leavevmode\hypertarget{ref-makowski2019}{}%
-\CSLLeftMargin{8 }
+\CSLLeftMargin{34 }
 \CSLRightInline{Makowski D, Ben-Shachar M, and Lüdecke D, {bayestestR}:
@@
 
+\leavevmode\hypertarget{ref-fritz2016}{}%
+\CSLLeftMargin{35 }
+\CSLRightInline{Fritz B, Hoffman W, and Anderson J, Response {Surface
+Method} for {Evaluation} of the {Performance} of {Agricultural
+Application Spray Nozzles}, \emph{Pesticide Formulation and Delivery
+Systems: 35th Volume, Pesticide Formulations, Adjuvants, and Spray
+Characterization in 2014}, {ASTM International} (2016).}
+
+\leavevmode\hypertarget{ref-legleiter2018}{}%
+\CSLLeftMargin{36 }
+\CSLRightInline{Legleiter TR, Young BG, and Johnson WG, Glyphosate plus
+2,4-{D Deposition}, {Absorption}, and {Efficacy} on
+{Glyphosate}-{Resistant Weed Species} as {Influenced} by {Broadcast
+Spray Nozzle}, \emph{Weed Technology} \textbf{32}:141--149, {Cambridge
+University Press} (2018).}
+
+\leavevmode\hypertarget{ref-alves2020}{}%
+\CSLLeftMargin{37 }
+\CSLRightInline{Alves GS, Vieira BC, Ynfante RS, Santana TM, Moraes JG,
+Golus JA, \emph{et al.}, Tank contamination and simulated drift effects
+of dicamba-containing formulations on soybean cultivars,
+\emph{Agrosystems, Geosciences \& Environment} \textbf{3}:e20065
+(2020).}
+
+\leavevmode\hypertarget{ref-zaric2020}{}%
+\CSLLeftMargin{38 }
+\CSLRightInline{Zaric M, Effects of {Tank Contamination} and {Impact} of
+{Drift}-{Reducing Agents} on {Weed Control} in {Response} to {Dicamba
+Applications}, \emph{Theses, Dissertations, and Student Research in
+Agronomy and Horticulture} (2020).}
+
+\leavevmode\hypertarget{ref-samples2021}{}%
+\CSLLeftMargin{39 }
+\CSLRightInline{Samples CA, Butts TR, Vieira BC, Irby JT, Reynolds DB,
+Catchot A, \emph{et al.}, Effect of {Deposition Aids Tank}-{Mixed} with
+{Herbicides} on {Cotton} and {Soybean Canopy Deposition} and {Spray
+Droplet Parameters}, \emph{Agronomy} \textbf{11}:278, {Multidisciplinary
+Digital Publishing Institute} (2021).}
+
+\leavevmode\hypertarget{ref-vieira2018}{}%
+\CSLLeftMargin{40 }
+\CSLRightInline{Vieira BC, Butts TR, Rodrigues AO, Golus JA, Schroeder
+K, and Kruger GR, Spray particle drift mitigation using field corn
+({Zea} mays {L}.) As a drift barrier, \emph{Pest Management Science}
+\textbf{74}:2038--2046 (2018).}
+
+\leavevmode\hypertarget{ref-knoche1994}{}%
+\CSLLeftMargin{41 }
+\CSLRightInline{Knoche M, Effect of droplet size and carrier volume on
+performance of foliage-applied herbicides, \emph{Crop Protection}
+\textbf{13}:163--178 (1994).}
+
+\leavevmode\hypertarget{ref-alves2017}{}%
+\CSLLeftMargin{42 }
+\CSLRightInline{Alves GS, Kruger GR, Cunha JPAR da, Santana DG de, Pinto
+LAT, Guimarães F, \emph{et al.}, Dicamba {Spray Drift} as {Influenced}
+by {Wind Speed} and {Nozzle Type}, \emph{Weed Technology}
+\textbf{31}:724--731, {Cambridge University Press} (2017).}
+
+\leavevmode\hypertarget{ref-johnson2006}{}%
+\CSLLeftMargin{43 }
+\CSLRightInline{Johnson AK, Roeth FW, Martin AR, and Klein RN,
+Glyphosate {Spray Drift Management} with {Drift}-{Reducing Nozzles} and
+{Adjuvants}, \emph{Weed Technology} \textbf{20}:893--897, {Cambridge
+University Press} (2006).}
+
+\leavevmode\hypertarget{ref-butts2018}{}%
+\CSLLeftMargin{44 }
+\CSLRightInline{Butts TR, Samples CA, Franca LX, Dodds DM, Reynolds DB,
+Adams JW, \emph{et al.}, Spray droplet size and carrier volume effect on
+dicamba and glufosinate efficacy, \emph{Pest Management Science}
+\textbf{74}:2020--2029 (2018).}
+
 \end{CSLReferences}

### 2021-08-17 analysis/bayes_droplet.Rmd
kok

@@
 
-```{r eval= FALSE}
-model10 <- brm(`dv10` ~ 1,
-                  family = hurdle_gamma(link = "log", 
-                                        link_shape = "log", 
-                                        link_hu = "logit"),
-                  data = droplet, save_pars = save_pars(all = TRUE))
-
-model11 <- brm(`dv10` ~ solution,
-                  family = hurdle_gamma(link = "log", 
-                                        link_shape = "log", 
-                                        link_hu = "logit"),
-                  data = droplet, save_pars = save_pars(all = TRUE))
-
-model12 <- brm(`dv10` ~ solution + nozzle,
-                  family = hurdle_gamma(link = "log", 
-                                        link_shape = "log", 
-                                        link_hu = "logit"),
-                  data = droplet, save_pars = save_pars(all = TRUE))
-
-model13 <- brm(`dv10` ~ solution * nozzle,
-                  family = hurdle_gamma(link = "log", 
-                                        link_shape = "log", 
-                                        link_hu = "logit"),
-                  data = droplet, save_pars = save_pars(all = TRUE))
-```
-
-# dv50
-
 ```{r message = FALSE}
@@
 ```{r}
-library(bayestestR)
+#library(bayestestR)
 #bayesfactor_models(model11, model12, model13, denominator = model10)
@@
 ```{r}
-model21 <- brm(`dv50` ~ solution,
-                  family = hurdle_gamma(link = "log", 
-                                        link_shape = "log", 
-                                        link_hu = "logit"),
-               warmup = 1000, iter = 2000, chains = 4,
-               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
-                  data = droplet, save_pars = save_pars(all = TRUE))
-
-model22 <- brm(`dv50` ~ solution + nozzle,
-                  family = hurdle_gamma(link = "log", 
-                                        link_shape = "log", 
-                                        link_hu = "logit"),
-               warmup = 1000, iter = 2000, chains = 4,
-               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
-                  data = droplet, save_pars = save_pars(all = TRUE))
-
 model23 <- brm(`dv50` ~ solution * nozzle,
@@
 # model comparison
-bayesfactor_models(model22, model23, denominator = model21)
+#bayesfactor_models(model22, model23, denominator = model21)
 ```
@@
 ```
+
 ```{r}

### 2021-08-17 analysis/combined.Rmd
kok

@@
 showtext_auto()
-font_add_google("Playfair Display", ## name of Google font
-                "Playfair")  ## name that will be used in R
-font_add_google("Bangers", "Bangers")
+font_add_google("Lato", ## name of Google font
+                "lato")  ## name that will be used in R
+font_add_google("Roboto", "roboto")
 

### 2021-08-17 analysis/droplet.Rmd
kok

@@
 library(car)
-library(brms)
+library(ggthemes)
+library(ggrepel)
+library(ggtext)
+library(patchwork)
+```
+
+```{r}
+library(extrafont)
+library(showtext)
+showtext_auto()
+font_add_google("Lato", ## name of Google font
+                "lato")  ## name that will be used in R
+font_add_google("Roboto", "roboto")
 ```
@@
   mutate(x200 = x200/100) %>% 
-  mutate(rep = row_number()) -> droplet
+  mutate(rep = row_number()) %>% 
+  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
+  group_by(solution, nozzle) %>% 
+  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
+  unite("trt", c(solution, nozzle), sep = "-", remove = FALSE) -> droplet
 ```
@@
 cld1 <- cld(emmeans1, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
-  as_tibble()
+  as_tibble() %>% 
+  mutate(type = "Dv10")
 cld1
@@
 cld2 <- cld(emmeans2, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
-  as_tibble()
+  as_tibble() %>% 
+  mutate(type = "Dv50")
+
 cld2
@@
 ```{r}
-emmeans3 <- emmeans(model3, ~ nozzle * solution, type = "response")
+emmeans3 <- emmeans(model3, ~ nozzle * solution, cont="pairwise", type = "response")
 ```
@@
 ```{r}
-cld3 <- cld(emmeans3, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
-  as_tibble()
+cld3 <- cld(emmeans3$emmeans, alpha=0.05, Letters=letters, 
+            adjust="none", reversed = TRUE) %>% 
+  as_tibble() %>% 
+  mutate(type = "Dv90")
 cld3
+```
+
+```{r}
+cld1 %>% 
+  bind_rows(cld2) %>% 
+  bind_rows(cld3) %>% 
+  group_by(solution, nozzle) %>% 
+  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
+  unite("trt", c(solution, nozzle), sep = "-") %>% 
+  mutate(response = round(response, 1)) -> dv
+```
+
+```{r}
+library(scales)
+show_col(brewer_pal(palette = "Set1")(5))
+show_col(wsj_pal()(9))
+```
+```{r}
+dv
+droplet %>% 
+  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>%
+  pivot_longer(cols = c("dv10", "dv50", "dv90"), names_to = "type",
+                             values_to = "dv") %>% 
+  mutate(type = str_to_title(type)) -> droplet1
+```
+
+```{r}
+dv %>% 
+  ggplot(aes(x = fct_reorder(trt, response), 
+             y = response, 
+             color = trt, 
+             shape = type)) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_linerange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
+                 position = position_dodge2(width = 0.4), 
+                 size = 1.3) +
+  geom_jitter(data = droplet1 %>% 
+                rename(response = dv), 
+                position = position_dodge2(width = 0.4),
+              mapping = aes(color = trt, shape = type), alpha = 0.1, size = 2) +
+  coord_flip() +
+  geom_text_repel(aes(label = response, 
+                         x = trt, color = trt, shape = type),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+#  annotate("text", x = 6, y = 300, label = "Dv10", size = 10,
+#           color = "#E41A1C", fontface = "bold") +
+#  annotate("text", x = 5.5, y = 800, label = "Dv50", size = 10,
+#           color = "#377eb8", fontface = "bold") +
+#  annotate("text", x = 4.5, y = 1250, label = "Dv90", size = 10, 
+#           color = "#4daf4a", fontface = "bold") +
+#  annotate("text", x = 1.2, y = 820, 
+#           label = "There are differences \namong all pairwise trt \ncomparisons within \neach Dv (P <.0001)", size = 7.5, hjust = 0, lineheight = 0.3,
+#           color = 1, fontface = "italic") +
+  labs(x = NULL, y = "Droplet size (µm)", color = NULL, shape = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 1500), breaks = seq(0, 1500, 300)) +
+  scale_shape_manual(values = c(8,9,10)) +
+  theme_few(base_family = "lato") + 
+  theme(legend.position = c(0.8, 0.2),
+        legend.text = element_markdown(size = 20),
+        legend.background = element_blank(),
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) +
+  guides(color = "none") -> fig1
 ```
@@
 ```{r}
-emmeans4 <- emmeans(model4, ~ nozzle * solution, type = "response")
+emmeans4 <- emmeans(model4, ~ nozzle * solution, cont = "pairwise", type = "response")
 ```
@@
 ```{r}
-cld4 <- cld(emmeans4, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
-  as_tibble()
+cld4 <- cld(emmeans4$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
+  as_tibble() %>% 
+  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
+  group_by(solution, nozzle) %>% 
+  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
+  unite("trt", c(solution, nozzle), sep = "-") %>% 
+  mutate(response = round(response, 2))
 cld4
+```
+
+```{r}
+cld4 %>% 
+  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_linerange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
+                 position = position_dodge2(width = 0.4), size = 1.3) +
+  coord_flip() +
+  geom_jitter(data = droplet1 %>% 
+                rename(response = rs), 
+              mapping = aes(color = trt), alpha = 0.1, size = 2) +
+  geom_text_repel(aes(label = response, 
+                         x = trt),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+  annotate("text", x = 5, y = 0.1, label = "There are differences \namong all pairwise trt  \ncomparisons (P <.0001) \nin figures A, B and C", size = 9, hjust = 0, lineheight = 0.3,
+           color = 1, fontface = "italic") +
+  labs(x = NULL, y = "Relative spam", color = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1.2, 0.2)) +
+  theme_few(base_family = "lato") + 
+  theme(legend.position = "none",
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) -> fig2
 ```
@@
 cld5 <- cld(emmeans5, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
-  as_tibble() 
+  as_tibble() %>% 
+  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
+  group_by(solution, nozzle) %>% 
+  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
+  unite("trt", c(solution, nozzle), sep = "-") %>% 
+  mutate(emmean = round(emmean,3))
 cld5
 ```
+
+```{r}
+cld5 %>% 
+  ggplot(aes(x = fct_reorder(trt, emmean*100), y = emmean*100, color = trt)) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_linerange(aes(ymin = asymp.LCL*100, ymax = asymp.UCL*100),
+                 position = position_dodge2(width = 0.4), size = 1.3) +
+  coord_flip() +
+  geom_jitter(data = droplet1 %>% 
+                rename(emmean = x200), 
+              mapping = aes(color = trt), alpha = 0.1, size = 2) +
+  geom_text_repel(aes(label = emmean*100, 
+                         x = trt),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+#  annotate("text", x = 2, y = 3, label = "There are differences \namong all pairwise trt \ncomparisons (P <.0001)", size = 9, hjust = 0, lineheight = 0.3,
+#           color = 1, fontface = "italic") +
+  labs(x = NULL, y = "% drifable fines < 200 µm", color = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 8), breaks = seq(0, 8, 2)) +
+  theme_few(base_family = "lato") + 
+  theme(legend.position = "none",
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) -> fig3
+```
+
+```{r}
+fig1 + fig2 + fig3 +
+  plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 25, hjust = 0, vjust = 0))
+
+ggsave("Figure 4.png", width = 9, height = 3)
+```

### 2021-08-17 analysis/reserva.R

@@ -1,0 +1,46 @@
+
+
+```{r eval= FALSE}
+model10 <- brm(`dv10` ~ 1,
+               family = hurdle_gamma(link = "log", 
+                                     link_shape = "log", 
+                                     link_hu = "logit"),
+               data = droplet, save_pars = save_pars(all = TRUE))
+
+model11 <- brm(`dv10` ~ solution,
+               family = hurdle_gamma(link = "log", 
+                                     link_shape = "log", 
+                                     link_hu = "logit"),
+               data = droplet, save_pars = save_pars(all = TRUE))
+
+model12 <- brm(`dv10` ~ solution + nozzle,
+               family = hurdle_gamma(link = "log", 
+                                     link_shape = "log", 
+                                     link_hu = "logit"),
+               data = droplet, save_pars = save_pars(all = TRUE))
+
+model13 <- brm(`dv10` ~ solution * nozzle,
+               family = hurdle_gamma(link = "log", 
+                                     link_shape = "log", 
+                                     link_hu = "logit"),
+               data = droplet, save_pars = save_pars(all = TRUE))
+```
+
+
+
+
+model21 <- brm(`dv50` ~ solution,
+               family = hurdle_gamma(link = "log", 
+                                     link_shape = "log", 
+                                     link_hu = "logit"),
+               warmup = 1000, iter = 2000, chains = 4,
+               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
+               data = droplet, save_pars = save_pars(all = TRUE))
+
+model22 <- brm(`dv50` ~ solution + nozzle,
+               family = hurdle_gamma(link = "log", 
+                                     link_shape = "log", 
+                                     link_hu = "logit"),
+               warmup = 1000, iter = 2000, chains = 4,
+               prior = set_prior("student_t(0.5, 1, 2)", class = "b"),
+               data = droplet, save_pars = save_pars(all = TRUE))

### 2021-08-17 analysis/combined.Rmd
as

@@
 library(ggpmisc)
-library(cowplot)
 library(patchwork)
-library(multcomp)
 library(ggtext)
@@
                 "lato")  ## name that will be used in R
-font_add_google("Roboto", "roboto")
-
+#font_add_google("Roboto", "roboto")
 ```
@@
 
-model1 <- lmer(deposition ~  trt +
-                (1|block/location), 
-              data = inswath)
+#model1 <- lmer(deposition ~  trt +
+#                (1|block/location), 
+#              data = inswath)
 ```
@@
 ```{r eval=FALSE}
-isSingular(model1)
+#isSingular(model1)
 ```
@@
 ```{r}
+library(ggrepel)
 em %>% as_tibble() %>% 
-  left_join(inswath) %>% 
+  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
+  mutate(emmean = round(emmean, 1)) %>% 
   ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
-             color = trt, shape = sprayer)) +
+             color = trt, shape = sprayer, label = emmean)) +
   geom_point(size = 3) +
@@
   coord_flip() +
+  geom_text_repel(  size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
   scale_shape_manual(values = c(16, 1)) +
   geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
-  ylim(0, 1550) +
-  theme_few() +
+  ylim(0, 2000) +
+  theme_few(base_family = "lato") +
   labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
-  theme(legend.position = "none") -> figA
-figA +
-  ggsave("Figure 1.png", width = 5, height = 5)
+  theme(legend.position = "none",
+        axis.title = element_text(size = 30),
+        axis.text = element_text(size = 25)) -> figA
+
+  ggsave("Figure 1.png", width = 5, height = 4)
 ```
@@
   theme(legend.position = "none") -> figB
-figB +
-  ggsave("Figure 1B.png", width = 10, height = 5)
+
+#  ggsave("Figure 1B.png", width = 10, height = 5)
 ```
@@
   mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
+  mutate(distance_m = round(distance_m, 1)) %>% 
   ggplot(aes(x = fct_reorder(trt, distance_m), 
@@
   geom_point(size = 3, stroke = 1) +
+  geom_text_repel(
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 545) +
   scale_shape_manual(values = c(16, 1)) +
@@
   ylim(0,60) +
-  theme_few() +
-  theme(legend.position = "none")  
+  theme_few(base_family = "lato") +
+  theme(legend.position = "none",
+        legend.text = element_markdown(size = 20),
+        legend.background = element_blank(),
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) 
 c
@@
   scale_shape_manual(values = c(16, 1)) + 
-  theme_few() +
-  geom_label(aes(label = formula), x = 30, y = 20, color = "white") +
+  theme_few(base_family = "lato") +
+  geom_label(aes(label = formula), x = 30, y = 20, color = "white", size = 10) +
   labs(x = "Distance (m)", 
@@
   theme(legend.position = "none",
+        legend.text = element_markdown(size = 20),
+        legend.background = element_blank(),
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25),
         strip.background = element_blank(),
         strip.text = element_textbox(
-          size = 12,
+          size = 30,
           color = "white", 
@@
           padding = margin(2, 0, 1, 0), 
-          margin = margin(3, 3, 3, 3))) +
+          margin = margin(3, 3, 3, 3)))
+
 ggsave("Figure 2.png", width = 6, height = 9)
-figs
 ```
@@
 epred3$emmeans %>% as_tibble() %>% 
-  left_join(auc_data1) %>% 
+  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
+  mutate(emmean = round(emmean, 1)) %>% 
   ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
-             color = trt, shape = sprayer)) +
+             color = trt, shape = sprayer, label = emmean)) +
   geom_point(size = 3) +
@@
   scale_color_viridis_d(option = "H") +
+  geom_text_repel(
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 545) +
   coord_flip() +
@@
   scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
-  theme_few() +
+  theme_few(base_family = "lato") +
   labs(x = NULL, y = "Area under the curve") +
-  theme(legend.position = "none") -> figE
+  theme(legend.position = "none",
+        legend.text = element_markdown(size = 20),
+        legend.background = element_blank(),
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) -> figE
 figE
@@
 ```{r}
-c + figE + plot_annotation(tag_levels = 'A') -> figU
+c + figE +
+  plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0)) -> figU
 
-ggsave("Figure 3.png", width = 10, height = 5)
+ggsave("Figure 3.png", width = 8, height = 4)
 ```

### 2021-08-17 analysis/droplet.Rmd
as

@@
 ```{r}
-readxl::read_excel("droplet_data.xlsx")
+#readxl::read_excel("droplet_data.xlsx")
 ```
@@
   plot_annotation(tag_levels = 'A') & 
-  theme(plot.tag = element_text(size = 25, hjust = 0, vjust = 0))
+  theme(plot.tag = element_text(size = 26, hjust = 0, vjust = 0))
 
-ggsave("Figure 4.png", width = 9, height = 3)
+ggsave("Figure 4.png", width = 11, height = 4)
 ```

### 2021-08-19 analysis/bayes_droplet.Rmd
as

@@
 library(patchwork)
+library(ggrepel)
 library(ggthemes)
@@
 ```{r}
-emmeans1 <- emmeans(model13, ~ nozzle * solution, cont="pairwise", type = "response")
+emmeans1 <- emmeans(model13, ~ nozzle * solution, 
+                    cont="pairwise", type = "response")
 ```
@@
 ```{r}
-options(scipen = 999)
-estimate_contrasts(model13, test = "bf") %>% 
-  as_tibble() -> bf_dv10
-write_csv(x = bf_dv10, file = "bf_dv10.csv")
+#https://easystats.github.io/blog/posts/bayestestr_emmeans/
+dv10_main <- pairs(emmeans(model13, ~ solution * nozzle))
+
+describe_posterior(dv10_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model13) %>% 
+  tibble() -> dv10_bf
+readr::write_csv(path = "../supp_file/data/bf_dv10.csv", x = dv10_bf)
+```
+
+```{r}
+#options(scipen = 999)
+#estimate_contrasts(model13, test = "bf") %>% 
+#  as_tibble() -> bf_dv10
+#write_csv(x = bf_dv10, file = "bf_dv10.csv")
 ```
@@
 ```{r}
-estimate_contrasts(model23, test = "bf")
+#https://easystats.github.io/blog/posts/bayestestr_emmeans/
+dv50_main <- pairs(emmeans(model23, ~ nozzle * solution))
+
+describe_posterior(dv50_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model23) %>% 
+  tibble() -> dv50_bf
+readr::write_csv(path = "../supp_file/data/bf_dv50.csv", x = dv50_bf)
+```
+
+```{r}
+estimate_contrasts(model23, test = "bf", transform = "response")
 ```
@@
 ```{r}
-# model comparison
-#bayesfactor_models(model32, model33, denominator = model31)
+#https://easystats.github.io/blog/posts/bayestestr_emmeans/
+dv90_main <- pairs(emmeans(model33, ~ nozzle * solution))
+
+describe_posterior(dv90_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model33) %>% 
+  tibble() -> dv90_bf
+readr::write_csv(path = "../supp_file/data/bf_dv90.csv", x = dv90_bf)
 ```
@@
 ```{r}
-estimate_contrasts(model43, test = "bf")
+rs_main <- pairs(emmeans(model43, ~ nozzle * solution))
+
+describe_posterior(rs_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model43) %>% 
+  tibble() -> rs_bf
+readr::write_csv(path = "../supp_file/data/bf_rs.csv", x = rs_bf)
 ```
@@
 # <200
-
-# RS
 
@@
 ```{r}
-emmeans5$emmeans %>% 
-  as_tibble() %>% 
-  unite("trt", c("solution", "nozzle"), sep = " - ") %>% 
-  ggplot(aes(x = fct_reorder(trt, response), y = response*100)) +
-  geom_point() +
-  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100)) +
-  coord_flip() +
-  theme_classic() +
-  labs(title = "<200 droptlet")
-```
+duz_main <- pairs(emmeans(model53, ~ nozzle * solution))
 
-```{r}
-estimate_contrasts(model53, test = "bf")
+describe_posterior(duz_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model53) %>% 
+  tibble() -> duz_bf
+readr::write_csv(path = "../supp_file/data/bf_duz.csv", x = duz_bf)
 ```
@@
 ```
--> emm
+
 ```{r}
@@
   bind_rows(em3) %>% 
+  mutate(solution = str_replace(solution, "water", "")) %>% 
   unite("trt", c("solution", "nozzle"), sep = "-") %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>%
+  mutate(trt = str_remove(trt, "Water-")) %>% 
   mutate(type = fct_recode(type,
@@
   unite("trt", c("solution", "nozzle"), sep = "-") %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>%
   dplyr::select(-rs, -x200, -rep) %>% 
+  mutate(trt = str_remove(trt, "Water-")) %>% 
   mutate(type = fct_recode(type,
@@
 ```{r}
-library(ggthemes)
 emm %>% 
-  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
-  geom_point(size = 2) +
-  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.3) +
-  geom_jitter(data = droplet1, alpha = 0.1, size = 2) +
-  facet_grid(~ type) +
+  mutate(response = round(response, 1)) %>% 
+  ggplot(aes(x = fct_reorder(trt, response), 
+             y = response, 
+             color = trt, 
+             shape = type)) +
+  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
+                 position = position_dodge2(width = 0.4), 
+                 size = 1.3, alpha = 0.5) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_jitter(data = droplet1,
+                position = position_dodge2(width = 0.4),
+              mapping = aes(color = trt, shape = type), alpha = 0.1, size = 2) +
   coord_flip() +
-  labs(x = NULL, y = "Droplet size (µm)") +
-  scale_color_viridis_d(option = "C") +
+  geom_text_repel(aes(label = response, 
+                         x = trt, color = trt, shape = type),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+  labs(x = NULL, y = "Droplet size (µm)", color = NULL, shape = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 1500), breaks = seq(0, 1500, 300)) +
+  scale_shape_manual(values = c(8,9,10)) +
   theme_few() + 
-  theme(strip.text = element_markdown(size = 12),
-        legend.position = "none") -> dv
+  theme(legend.position = c(0.85, 0.2),
+        legend.text = element_markdown(size = 20),
+        legend.background = element_blank(),
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) +
+  guides(color = "none") -> fig1
+
+ggsave("fig.png")
+```
+
+```{r warning = FALSE}
+fig1 + fig2 + fig3 +
+  plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0))
+
+ggsave("Figure 5.png", width = 11, height = 4)
 ```
@@
 ```{r}
-emmeans4$emmeans %>% as_tibble() -> em4
+emmeans4$emmeans %>% as_tibble() %>% 
+  mutate(solution = str_replace(solution, "Water", "")) %>% 
+  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
+    mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> em4
 emmeans5$emmeans %>% as_tibble() -> em5
@@
 droplet %>% 
+  mutate(solution = str_replace(solution, "Water", "")) %>% 
   unite("trt", c("solution", "nozzle"), sep = "-") %>% 
   dplyr::select(trt, rs) %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>%
   rename(response = rs) -> droplet2
@@
 em4 %>% 
+  mutate(response = round(response, 2)) %>% 
+  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
+                 position = position_dodge2(width = 0.4), size = 1.3) +
+  coord_flip() +
+  geom_jitter(data = droplet2,
+              mapping = aes(color = trt), alpha = 0.1, size = 2) +
+  geom_text_repel(aes(label = response, 
+                         x = trt),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+#  annotate("text", x = 5, y = 0.1, label = "There are differences \namong all pairwise trt  \ncomparisons (P <.0001) \nin figures A, B and C", size = 9, hjust = 0, lineheight = 0.3,
+#           color = 1, fontface = "italic") +
+  labs(x = NULL, y = "Relative span", color = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1.2, 0.2)) +
+  theme_few() + 
+  theme(legend.position = "none",
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) -> fig2
+```
+
+```{r}
+emmeans5$emmeans %>% as_tibble() %>% 
+  mutate(solution = str_replace(solution, "Water", "")) %>% 
   unite("trt", c("solution", "nozzle"), sep = "-") %>% 
-  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
-  geom_point(size = 2) +
-  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.3) +
-  geom_jitter(data = droplet2, alpha = 0.1, size = 2) +
-  coord_flip() +
-  labs(x = NULL, y = "RS") +
-  scale_color_viridis_d(option = "C") +
-  theme_few() + 
-  theme(strip.text = element_markdown(),
-        legend.position = "none") -> rs
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> em5
 ```
@@
 droplet %>% 
+  mutate(solution = str_replace(solution, "Water", "")) %>% 
   unite("trt", c("solution", "nozzle"), sep = "-") %>% 
   dplyr::select(trt, x200) %>% 
-  rename(response = x200) -> droplet3
+  rename(response = x200) %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> droplet3
 ```
@@
 ```{r}
-(
 em5 %>% 
-  unite("trt", c("solution", "nozzle"), sep = "-") %>% 
+  mutate(response = round(response, 4)) %>% 
   ggplot(aes(x = fct_reorder(trt, response*100), y = response*100, color = trt)) +
-  geom_point(size = 2) +
-  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100), size = 1.3) +
-  geom_jitter(data = droplet3, alpha = 0.1, size = 2) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100),
+                 position = position_dodge2(width = 0.4), size = 1.3) +
   coord_flip() +
-  scale_y_continuous(breaks = c(0, 2, 4, 6, 8)) +
-  labs(x = NULL, y = "% drifable fines < 200 µm") +
-  scale_color_viridis_d(option = "C") +
+  geom_jitter(data = droplet2, 
+              mapping = aes(color = trt), alpha = 0.1, size = 2) +
+  geom_text_repel(aes(label = response*100, 
+                         x = trt),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+#  annotate("text", x = 2, y = 3, label = "There are differences \namong all pairwise trt \ncomparisons (P <.0001)", size = 9, hjust = 0, lineheight = 0.3,
+#           color = 1, fontface = "italic") +
+  labs(x = NULL, y = "% driftable fines < 200 µm", color = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
   theme_few() + 
-  theme(strip.text = element_markdown(),
-        legend.position = "none") -> x200
-)
+  theme(legend.position = "none",
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) -> fig3
 ```
 
-```{r}
-rs + x200 -> fig
-dv / fig -> fig1
+```{r warning = FALSE}
+fig1 + fig2 + fig3 +
+  plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0))
 
-ggsave("Figure 4.png", width = 9, height = 6)
+ggsave("Figure 5.png", width = 11, height = 4)
 ```

### 2021-08-19 analysis/combined.Rmd
as

@@
 new_dt %>% 
+  mutate(solution= str_replace(solution, "Water", "")) %>% 
   unite("trt", c("solution", "sprayer", "nozzle"), 
-        sep = "-", remove = FALSE) -> new_dt 
+        sep = "-", remove = FALSE) %>% 
+  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> new_dt  
 ```
@@
   filter(type == "inswath") %>% 
-  filter(!is.na(deposition)) %>% 
-  mutate(trt = str_replace(trt, "Intact", "DRA")) 
+  filter(!is.na(deposition))
 ```
@@
 #https://www.statisticshowto.com/bayes-factor-definition/
-groups <- emmeans(model1, ~trt)
+groups <- emmeans(model1, ~ trt)
 group_diff <- pairs(groups)
@@
 ```
+```{r}
+#https://easystats.github.io/blog/posts/bayestestr_emmeans/
+inswath_main <- pairs(emmeans(model1, ~ trt))
+
+describe_posterior(inswath_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model1) %>% 
+  tibble() -> inswath_bf
+readr::write_csv(path = "../supp_file/data/inswath_bf.csv", x = inswath_bf)
+```
 
 ```{r}
-estimate_contrasts(model1, test = "bf") -> inswath_bf
-inswath_bf %>% 
-  tibble() -> inswath_bf
-#readr::write_csv(path = "inswath_bf.csv", x = inswath_bf)
+#estimate_contrasts(model1, test = "bf") -> inswath_bf
+#inswath_bf %>% 
+#  tibble() -> inswath_bf
+#readr::write_csv(path = "../supp_file/data/inswath_bf.csv", x = inswath_bf)
 ```
@@
   ylim(0, 2000) +
-  theme_few(base_family = "lato") +
-  labs(x = NULL, y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
+  theme_few() +
+  labs(x = NULL, 
+       y = expression(paste("Spray particle deposition (\u03B7L/cm"^"2",")"))
+       ) +
   theme(legend.position = "none",
         axis.title = element_text(size = 30),
-        axis.text = element_text(size = 25)) -> figA
+        axis.text = element_markdown(size = 25)) -> figA
 
@@
   tibble() -> upwind_bf
-#readr::write_csv(path = "upwind_bf.csv", x = upwind_bf)
+readr::write_csv(path = "../supp_file/data/upwind_bf.csv", x = upwind_bf)
 ```
@@
   scale_shape_manual(values = c(16, 1)) +
-  geom_segment(aes(x= trt, xend= trt, y=0, yend=distance_m), size = 2) +
+  geom_segment(aes(x= trt, xend= trt, y=0, yend=distance_m), size = 1) +
   coord_flip() +
@@
 
+```{r}
+loc <- tibble(trt = "DRA-Open-TTI")
+```
+
 ```{r include=TRUE}
-figs <- fig2 %>% 
+fig2 %>% 
   mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
@@
   scale_shape_manual(values = c(16, 1)) + 
-  theme_few(base_family = "lato") +
-  geom_label(aes(label = formula), x = 30, y = 20, color = "white", size = 10) +
+  theme_few() +
+  geom_text(data = loc, mapping = aes(x = 10, y = 20), 
+            label = "Intercept", inherit.aes = FALSE, size = 10) +
+  geom_text(data = loc, mapping = aes(x = 55, y = 10), 
+            label = "Slope", inherit.aes = FALSE, size = 10) +
+  geom_label(aes(label = formula), x = 30, y = 15, color = "white", size = 12) +
+  geom_curve(data = loc, mapping = aes(x = 25, y = 17,
+             xend = 20, yend = 20),
+             arrow = arrow(length = unit(0.07, "inch")), 
+             color = 1,
+             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
+  geom_curve(data = loc, mapping = aes(x = 42, y = 13,
+             xend = 47, yend = 10),
+             arrow = arrow(length = unit(0.07, "inch")), 
+             color = 1,
+             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
   labs(x = "Distance (m)", 
@@
         legend.background = element_blank(),
-        axis.title = element_markdown(size = 30),
-        axis.text = element_markdown(size = 25),
+        axis.title = element_markdown(size = 32),
+        axis.text = element_markdown(size = 28),
         strip.background = element_blank(),
         strip.text = element_textbox(
-          size = 30,
+          size = 32,
+          face = "bold",
           color = "white", 
@@
 auc_data1 <- auc_data %>% 
-  filter(distance_m == 1) %>% 
-  mutate(trt = str_replace(trt, "Intact", "DRA")) 
+  filter(distance_m == 1)
 ```
@@
   scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
-  theme_few(base_family = "lato") +
+  theme_few() +
   labs(x = NULL, y = "Area under the curve") +
@@
 ```
+```{r}
+#https://easystats.github.io/blog/posts/bayestestr_emmeans/
+auc_main <- pairs(emmeans(auc_model, ~ trt))
+
+describe_posterior(auc_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = auc_model) %>% 
+  tibble() -> auc_bf
+readr::write_csv(path = "../supp_file/data/auc_bf.csv", x = auc_bf)
+```
 
 ```{r}
-estimate_contrasts(auc_model, test = "bf") -> auc_bf
-auc_bf %>% 
-  tibble() -> auc_bf
-readr::write_csv(path = "auc_bf.csv", x = auc_bf)
+#estimate_contrasts(auc_model, test = "bf") -> auc_bf
+#auc_bf %>% 
+#  tibble() -> auc_bf
+#readr::write_csv(path = "../supp_file/data/auc_bf.csv", x = auc_bf)
 ```
@@
 ```{r eval = FALSE}
-library(modelbased)
-estimate_contrasts(auc_model, test = "bf") %>% 
-  kableExtra::kable()
+#library(modelbased)
+#estimate_contrasts(auc_model, test = "bf") %>% 
+#  kableExtra::kable()
 ```

### 2021-08-19 analysis/droplet.Rmd
as

--- 2021-06-21 analysis/droplet.Rmd
@@
 library(car)
-library(brms)
+library(ggthemes)
+library(ggrepel)
+library(ggtext)
+library(patchwork)
 ```
@@
 ```{r}
-readxl::read_excel("droplet_data.xlsx")
+library(extrafont)
+library(showtext)
+showtext_auto()
+font_add_google("Lato", ## name of Google font
+                "lato")  ## name that will be used in R
+font_add_google("Roboto", "roboto")
+```
+
+```{r}
+#readxl::read_excel("droplet_data.xlsx")
 ```
@@
   mutate(x200 = x200/100) %>% 
-  mutate(rep = row_number()) -> droplet
+  mutate(rep = row_number()) %>% 
+  mutate(solution = str_replace_all(solution, "Intact", "DRA"),
+         solution = str_replace_all(solution, "Water", "")) %>% 
+  group_by(solution, nozzle) %>% 
+  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
+  unite("trt", c(solution, nozzle), sep = "-", remove = FALSE) %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) -> droplet
 ```
@@
 ```{r}
-cld3 <- cld(emmeans3, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
-  as_tibble()
+cld3 <- cld(emmeans3$emmeans, alpha=0.05, Letters=letters, 
+            adjust="none", reversed = TRUE) %>% 
+  as_tibble() %>% 
+  mutate(type = "Dv90")
 cld3
+```
+
+```{r}
+cld1 %>% 
+  bind_rows(cld2) %>% 
+  bind_rows(cld3) %>% 
+  group_by(solution, nozzle) %>% 
+  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
+  unite("trt", c(solution, nozzle), sep = "-") %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>% 
+  mutate(response = round(response, 1)) -> dv
+```
+
+```{r}
+library(scales)
+show_col(brewer_pal(palette = "Set1")(5))
+show_col(wsj_pal()(9))
+```
+
+```{r}
+dv
+droplet %>% 
+  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>%
+  pivot_longer(cols = c("dv10", "dv50", "dv90"), names_to = "type",
+                             values_to = "dv") %>% 
+  mutate(type = str_to_title(type)) -> droplet1
+```
+
+```{r}
+dv %>% 
+  mutate(type = fct_recode(type, 
+                           "D<sub>v10</sub>" = "Dv10",
+                           "D<sub>v50</sub>" = "Dv50",
+                           "D<sub>v90</sub>" = "Dv90")) %>% 
+  ggplot(aes(x = fct_reorder(trt, response), 
+             y = response, 
+             color = trt, 
+             shape = type)) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_linerange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
+                 position = position_dodge2(width = 0.4), 
+                 size = 1.3) +
+  geom_jitter(data = droplet1 %>% 
+                mutate(type = fct_recode(type, 
+                           "D<sub>v10</sub>" = "Dv10",
+                           "D<sub>v50</sub>" = "Dv50",
+                           "D<sub>v90</sub>" = "Dv90")) %>% 
+                rename(response = dv), 
+                position = position_dodge2(width = 0.4),
+              mapping = aes(color = trt, shape = type), alpha = 0.1, size = 2) +
+  coord_flip() +
+  geom_text_repel(aes(label = response, 
+                         x = trt, color = trt, shape = type),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+#  annotate("text", x = 6, y = 300, label = "Dv10", size = 10,
+#           color = "#E41A1C", fontface = "bold") +
+#  annotate("text", x = 5.5, y = 800, label = "Dv50", size = 10,
+#           color = "#377eb8", fontface = "bold") +
+#  annotate("text", x = 4.5, y = 1250, label = "Dv90", size = 10, 
+#           color = "#4daf4a", fontface = "bold") +
+#  annotate("text", x = 1.2, y = 820, 
+#           label = "There are differences \namong all pairwise trt \ncomparisons within \neach Dv (P <.0001)", size = 7.5, hjust = 0, lineheight = 0.3,
+#           color = 1, fontface = "italic") +
+  labs(x = NULL, y = "Droplet size (µm)", color = NULL, shape = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 1500), breaks = seq(0, 1500, 300)) +
+  scale_shape_manual(values = c(8,9,10)) +
+  theme_few() + 
+  theme(legend.position = c(0.85, 0.15),
+        legend.text = element_markdown(size = 20),
+        legend.background = element_blank(),
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) +
+  guides(color = "none") -> fig1
 ```
@@
 ```{r}
-cld4 <- cld(emmeans4, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
-  as_tibble()
+cld4 <- cld(emmeans4$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
+  as_tibble() %>% 
+  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
+  group_by(solution, nozzle) %>% 
+  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
+  unite("trt", c(solution, nozzle), sep = "-") %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>%
+  mutate(response = round(response, 2))
 cld4
+```
+
+```{r}
+cld4 %>% 
+  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_linerange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
+                 position = position_dodge2(width = 0.4), size = 1.3) +
+  coord_flip() +
+  geom_jitter(data = droplet1 %>% 
+                rename(response = rs), 
+              mapping = aes(color = trt), alpha = 0.1, size = 2) +
+  geom_text_repel(aes(label = response, 
+                         x = trt),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+  annotate("text", x = 5, y = 0.1, label = "There are differences \namong all pairwise trt  \ncomparisons (P <.0001) \nin figures A, B and C", size = 9, hjust = 0, lineheight = 0.3,
+           color = 1, fontface = "italic") +
+  labs(x = NULL, y = "Relative span", color = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1.2, 0.2)) +
+  theme_few() + 
+  theme(legend.position = "none",
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) -> fig2
 ```
@@
 cld5 <- cld(emmeans5, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>% 
-  as_tibble() 
+  as_tibble() %>% 
+  mutate(solution = str_replace_all(solution, "Intact", "DRA")) %>% 
+  group_by(solution, nozzle) %>% 
+  mutate(nozzle = str_remove_all(nozzle, '[0-9]+')) %>% 
+  unite("trt", c(solution, nozzle), sep = "-") %>% 
+  mutate(trt = str_remove(trt, "^[^a-zA-Z]+")) %>%
+  mutate(emmean = round(emmean,3))
 cld5
 ```
+
+```{r}
+cld5 %>% 
+  ggplot(aes(x = fct_reorder(trt, emmean*100), y = emmean*100, color = trt)) +
+  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
+  geom_linerange(aes(ymin = asymp.LCL*100, ymax = asymp.UCL*100),
+                 position = position_dodge2(width = 0.4), size = 1.3) +
+  coord_flip() +
+  geom_jitter(data = droplet1 %>% 
+                rename(emmean = x200), 
+              mapping = aes(color = trt), alpha = 0.1, size = 2) +
+  geom_text_repel(aes(label = emmean*100, 
+                         x = trt),
+                    size = 8,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 455) +
+#  annotate("text", x = 2, y = 3, label = "There are differences \namong all pairwise trt \ncomparisons (P <.0001)", size = 9, hjust = 0, lineheight = 0.3,
+#           color = 1, fontface = "italic") +
+  labs(x = NULL, y = "% driftable fines < 200 µm", color = NULL) +
+  scale_color_viridis_d(option = "H") +
+  scale_y_continuous(limits = c(0, 8), breaks = seq(0, 8, 2)) +
+  theme_few() + 
+  theme(legend.position = "none",
+        axis.title = element_markdown(size = 30),
+        axis.text = element_markdown(size = 25)) -> fig3
+```
+
+```{r}
+fig1 + fig2 + fig3 +
+  plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0))
+
+ggsave("Figure 4.png", width = 11, height = 4)
+```

### 2021-08-19 supp_file/supp_file.Rmd
as

@@
 output:
+  html_document:
+    df_print: paged
   pdf_document: default
@@
 ```{r}
-read_csv("bf.csv") %>% 
+read_csv("data/bf.csv") %>% 
   kableExtra::kable(., booktabs = T, longtable = T, 
@@
 ```{r echo=FALSE}
-read_csv("inswath_bf.csv") %>% 
+read_csv("data/inswath_bf.csv") %>% 
   mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
@@
 ```{r echo=FALSE}
-read_csv("auc_bf.csv") %>% 
+read_csv("data/auc_bf.csv") %>% 
   mutate_if(is.double, ~round(., 2)) %>% 

### 2021-08-19 supp_file/table.Rmd
as

@@
   reactable(., theme = fivethirtyeight(), 
-            filterable = TRUE,
+            filterable = FALSE,
             resizable = TRUE,
@@
 $$\\[0.1in]$$
-The treatment contrasts of inswath spray solution deposition are compared (Table 2). See the BF and make an interpretation based on Table 1.
-
-$$\\[0.1in]$$
 
 ```{r}
-read_csv("data/inswath_bf.csv") %>% 
-  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
-  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
-  dplyr::select(-"Std_Difference") %>% 
+read_csv("data/bf_dv10.csv") %>% 
+  mutate(Parameter = str_remove_all(Parameter, "\\(|\\)")) %>% 
+  mutate(log_BF = as.double(log_BF)) %>% 
+  rename(BF = log_BF) %>% 
+  mutate(BF = exp(BF)) %>% 
+  mutate(Parameter = str_remove_all(Parameter, "Water ")) %>% 
+  mutate_if(is.double, ~ round(., 2)) %>% 
   reactable(., theme = fivethirtyeight(),
@@
             wrap = TRUE,
-            groupBy = "Level1",
             searchable = FALSE,
@@
             columns = list(
-            Level1 = colDef(filterable = TRUE),
-            Level2 = colDef(filterable = TRUE),
-            BF = colDef(
-              #cell = #function(value) {
-#                if (value > 1) paste0("+", value) 
-#                else value
-#                },
-              style = function(value) {
-                color <- if (value > 1) {
-                  "#008000"
-                  } else if (value < 1) {
-                    "#e00000"
-                  }
-                list(fontWeight = 600, color = color)}),
-            Difference = colDef(align = "center", 
-                                cell = data_bars_pos_neg(., 
-                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
-  add_title("Table 2. Treatment contrasts for inswath spray solution deposition. Bayes Factor is used to test contrast hypothesis", font_size = 15)
-```
-
-$$\\[0.1in]$$
-The treatment contrasts of Area Under the Curve are compared (Table 3). See the BF and make an interpretation based on Table 1.
-$$\\[0.1in]$$
-
-```{r}
-read_csv("data/auc_bf.csv") %>% 
-  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
-  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
-  dplyr::select(-"Std_Difference") %>% 
-  mutate_if(is.double, ~round(.,2)) %>% 
-  reactable(., theme = fivethirtyeight(),
-            filterable = FALSE,
-            resizable = TRUE,
-            pagination = FALSE,
-            wrap = TRUE,
-            groupBy = "Level1",
-            searchable = FALSE,
-            defaultPageSize = 20,
-             showSortable = TRUE,
-            columns = list(
-            Level1 = colDef(filterable = TRUE),
-            Level2 = colDef(filterable = TRUE),
             BF = colDef(
@@
 #                                                         "red"))),
-            Difference = colDef(align = "center", 
+            Parameter = colDef(align = "center", filterable = TRUE,
                                 cell = data_bars_pos_neg(., 
                                                          colors = c("#ff3030", "#1e90ff"))))) %>% 
-  add_title("Table 3. Treatment contrasts for Area Under the Curve. Bayes Factor is used to test contrast hypothesis", font_size = 15)
+  add_title("Table 2. Treatment contrasts for DV10. Bayes Factor is used to test contrast hypothesis", font_size = 15)
 ```
@@
 read_csv("data/bf_dv10.csv") %>% 
-  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
-  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
-  dplyr::select(-"Std_Difference") %>% 
-  mutate_if(is.double, ~round(.,2)) %>% 
+  mutate(Parameter = str_remove_all(Parameter, "\\(|\\)")) %>% 
+  mutate(log_BF = as.double(log_BF)) %>% 
+  rename(BF = log_BF) %>% 
+  mutate(BF = exp(BF)) %>% 
+  mutate_if(is.double, ~ round(., 2)) %>% 
+  mutate(Parameter = str_remove_all(Parameter, "Water ")) %>% 
   reactable(., theme = fivethirtyeight(),
@@
             columns = list(
-            Level1 = colDef(filterable = TRUE),
-            Level2 = colDef(filterable = TRUE),
             BF = colDef(
@@
 #                                                         "red"))),
-            Difference = colDef(align = "center", 
+            Parameter = colDef(align = "center", filterable = TRUE,
                                 cell = data_bars_pos_neg(., 
                                                          colors = c("#ff3030", "#1e90ff"))))) %>% 
-  add_title("Table 3. Treatment contrasts for DV10. Bayes Factor is used to test contrast hypothesis", font_size = 15)
+  add_title("Table 3. Treatment contrasts for DV50. Bayes Factor is used to test contrast hypothesis", font_size = 15)
 ```
@@
 ```{r}
-read_csv("data/bf_dv50.csv") %>% 
-  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
-  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
-  dplyr::select(-"Std_Difference") %>% 
-  mutate_if(is.double, ~round(.,2)) %>% 
+read_csv("data/bf_dv10.csv") %>% 
+  mutate(Parameter = str_remove_all(Parameter, "\\(|\\)")) %>% 
+  mutate(log_BF = as.double(log_BF)) %>% 
+  rename(BF = log_BF) %>% 
+  mutate(BF = exp(BF)) %>% 
+  mutate_if(is.double, ~ round(., 2)) %>% 
+  mutate(Parameter = str_remove_all(Parameter, "Water ")) %>% 
   reactable(., theme = fivethirtyeight(),
@@
 #                                                         "red"))),
-            Difference = colDef(align = "center", 
+            Parameter = colDef(align = "center", filterable = TRUE,
                                 cell = data_bars_pos_neg(., 
                                                          colors = c("#ff3030", "#1e90ff"))))) %>% 
-  add_title("Table 4. Treatment contrasts for DV50. Bayes Factor is used to test contrast hypothesis", font_size = 15)
+  add_title("Table 4. Treatment contrasts for DV90. Bayes Factor is used to test contrast hypothesis", font_size = 15)
 ```
@@
 ```{r}
-read_csv("data/bf_dv90.csv") %>% 
-  mutate_if(is_character, ~str_replace(., "[)]", "")) %>% 
-  mutate_if(is_character, ~str_replace(., "[(]", "")) %>% 
-  dplyr::select(-"Std_Difference") %>% 
-  mutate_if(is.double, ~round(.,2)) %>% 
+read_csv("data/bf_rs.csv") %>% 
+  mutate(Parameter = str_remove_all(Parameter, "\\(|\\)")) %>% 
+  mutate(log_BF = as.double(log_BF)) %>% 
+  rename(BF = log_BF) %>% 
+  mutate(BF = exp(BF)) %>% 
+  mutate_if(is.double, ~ round(., 2)) %>% 
+  mutate(Parameter = str_remove_all(Parameter, "Water ")) %>% 
   reactable(., theme = fivethirtyeight(),
@@
 #                                                         "red"))),
-            Difference = colDef(align = "center", 
+            Parameter = colDef(align = "center", filterable = TRUE,
                                 cell = data_bars_pos_neg(., 
                                                          colors = c("#ff3030", "#1e90ff"))))) %>% 
-  add_title("Table 5. Treatment contrasts for DV90. Bayes Factor is used to test contrast hypothesis", font_size = 15)
+  add_title("Table 5. Treatment contrasts for relative span. Bayes Factor is used to test contrast hypothesis", font_size = 15)
+```
+
+```{r}
+read_csv("data/bf_duz.csv") %>% 
+  mutate(Parameter = str_remove_all(Parameter, "\\(|\\)")) %>% 
+  mutate(log_BF = as.double(log_BF)) %>% 
+  rename(BF = log_BF) %>% 
+  mutate(BF = exp(BF)) %>% 
+  mutate_if(is.double, ~ round(., 2)) %>% 
+  mutate(Parameter = str_remove_all(Parameter, "Water ")) %>% 
+  reactable(., theme = fivethirtyeight(),
+            filterable = FALSE,
+            resizable = TRUE,
+            pagination = FALSE,
+            wrap = TRUE,
+            searchable = FALSE,
+            defaultPageSize = 20,
+             showSortable = TRUE,
+            columns = list(
+            BF = colDef(
+              #cell = #function(value) {
+#                if (value > 1) paste0("+", value) 
+#                else value
+#                },
+              style = function(value) {
+                color <- if (value > 1) {
+                  "#008000"
+                  } else if (value < 1) {
+                    "#e00000"
+                  }
+                list(fontWeight = 600, color = color)}),
+#            BF = colDef(align = "center",
+#                        cell = color_tiles(., colors = ifelse(. > 1.00, "blue",
+#                                                         "red"))),
+            Parameter = colDef(align = "center", filterable = TRUE,
+                                cell = data_bars_pos_neg(., 
+                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
+  add_title("Table 6. Treatment contrasts for % driftable fines < 200. Bayes Factor is used to test contrast hypothesis", font_size = 15)
+```
+
+The treatment contrasts of inswath spray solution deposition are compared (Table 2). See the BF and make an interpretation based on Table 1.
+
+$$\\[0.1in]$$
+
+```{r}
+read_csv("data/inswath_bf.csv") %>%
+  mutate(Parameter = str_remove_all(Parameter, "\\(|\\)")) %>% 
+  mutate(log_BF = as.double(log_BF)) %>% 
+  rename(BF = log_BF) %>% 
+  mutate(BF = exp(BF)) %>% 
+  mutate_if(is.double, ~ round(., 2)) %>% 
+  reactable(., theme = fivethirtyeight(),
+            filterable = FALSE,
+            resizable = TRUE,
+            pagination = FALSE,
+            wrap = TRUE,
+#            groupBy = "Level1",
+            searchable = FALSE,
+            defaultPageSize = 20,
+            showSortable = TRUE,
+            columns = list(
+            BF = colDef(
+              #cell = #function(value) {
+#                if (value > 1) paste0("+", value) 
+#                else value
+#                },
+              style = function(value) {
+                color <- if (value > 1) {
+                  "#008000"
+                  } else if (value < 1) {
+                    "#e00000"
+                  }
+                list(fontWeight = 600, color = color)}),
+            Parameter = colDef(align = "center", filterable = TRUE, 
+                                cell = data_bars_pos_neg(., 
+                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
+  add_title("Table 7. Treatment contrasts for in-swath spray solution deposition. Bayes Factor is used to test contrast hypothesis", font_size = 15)
+```
+
+$$\\[0.1in]$$
+The treatment contrasts of Area Under the Curve are compared (Table 3). See the BF and make an interpretation based on Table 1.
+$$\\[0.1in]$$
+
+```{r}
+read_csv("data/auc_bf.csv") %>% 
+  mutate(Parameter = str_remove_all(Parameter, "\\(|\\)")) %>% 
+  mutate(log_BF = as.double(log_BF)) %>% 
+  mutate_if(is.double, ~ round(., 2)) %>% 
+  rename(BF = log_BF) %>% 
+  mutate(BF = exp(BF)) %>% 
+  reactable(., theme = fivethirtyeight(),
+            filterable = FALSE,
+            resizable = TRUE,
+            pagination = FALSE,
+            wrap = TRUE,
+            searchable = FALSE,
+            defaultPageSize = 20,
+             showSortable = TRUE,
+            columns = list(
+            BF = colDef(
+              #cell = #function(value) {
+#                if (value > 1) paste0("+", value) 
+#                else value
+#                },
+              style = function(value) {
+                color <- if (value > 1) {
+                  "#008000"
+                  } else if (value < 1) {
+                    "#e00000"
+                  }
+                list(fontWeight = 600, color = color)}),
+#            BF = colDef(align = "center",
+#                        cell = color_tiles(., colors = ifelse(. > 1.00, "blue",
+#                                                         "red"))),
+            Parameter = colDef(align = "center", filterable = TRUE,
+                                cell = data_bars_pos_neg(., 
+                                                         colors = c("#ff3030", "#1e90ff"))))) %>% 
+  add_title("Table 8. Treatment contrasts for Area Under the Curve. Bayes Factor is used to test contrast hypothesis", font_size = 15)
 ```

### 2021-08-20 analysis/bayes_droplet.Rmd
nb

@@
   theme(legend.position = c(0.85, 0.2),
-        legend.text = element_markdown(size = 20),
+        legend.text = element_markdown(size = 25),
+        legend.margin = margin(0, 0, 0, 0),
+        legend.spacing.x = unit(0, "mm"),
+        legend.spacing.y = unit(0, "mm"),
         legend.background = element_blank(),
@@
   ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
+  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
+                 position = position_dodge2(width = 0.4), 
+                 size = 1.3, alpha = 0.5) +
   geom_point(size = 2, position = position_dodge2(width = 0.4)) +
-  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
-                 position = position_dodge2(width = 0.4), size = 1.3) +
   coord_flip() +
@@
   ggplot(aes(x = fct_reorder(trt, response*100), y = response*100, color = trt)) +
+  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100),
+                 position = position_dodge2(width = 0.4), 
+                 size = 1.3, alpha = 0.5) +
   geom_point(size = 2, position = position_dodge2(width = 0.4)) +
-  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100),
-                 position = position_dodge2(width = 0.4), size = 1.3) +
   coord_flip() +

### 2021-08-20 supp_file/supplemental_file.Rmd
nb

---
title: "Hooded broadcast sprayer for particle drift reduction"
subtitle: "Supplemental File"
output: hrbrthemes::ipsum_pdf
---

This is a supplemental material for the manuscript entitled: "Hooded broadcast sprayer for particle drift reduction" authored by Bruno C. Vieira^1^, Maxwel Coura Oliveira^1^, Guilherme Souza Alves^2^, Jeffrey A. Golus^2^, Kasey Schroeder^2^, Reid J. Smeda^3^, Ryan J. Rector^4^, Greg R. Kruger^2^, Rodrigo Werle^1^.

^1^ Department of Agronomy, University of Wisconsin–Madison, Madison, WI, USA  
^2^ West Central Research and Extension Center, University of Nebraska-Lincoln, North Platte, NE, USA  
^3^ Plant Science Division, University of Missouri, Columbia, MO, USA  
^4^ Bayer Crop Science, St. Louis, MO, USA

Author for correspondence:  
Rodrigo Werle, Department of Agronomy, University of Wisconsin–Madison, Madison, WI, USA. E-mail: rwerle@wisc.edu

## Bayes Factor

The Bayes Factor (BF) interpretation is based on Lee and Wagenmakers (2014). The H~0~ and H~1~ mean that treatments are the same (null hypothesis) or different, respectively.

Table 1. Bayes Factor interpretation

| Bayes Factor  | Interpretation               	|
|--------------	|------------------------------	|
| > 100        	| Extreme evidence for H~1~     	|
| 30 – 100     	| Very strong evidence for H~1~ 	|
| 10 – 30      	| Strong evidence for H~1~      	|
| 3 – 10       	| Moderate evidence for H~1~    	|
| 1 – 3        	| Anecdotal evidence for H~0~    	|
| 1            	| No evidence                  	|
| 1/3 – 1      	| Anecdotal evidence for H~0~   	|
| 1/3 – 1/10   	| Moderate evidence for H~0~    	|
| 1/10 – 1/30  	| Strong evidence for H~0~      	|
| 1/30 – 1/100 	| Very strong evidence for H~0~ 	|
| < 1/100      	| Extreme evidence for H~0~     	|

## Tables

The tables correspond the pairwise comparisons between treatments presented in the manuscript figures. Some pairwise comparisons (mean) are different from the actual values in the figures due to non-transformed data (logit scale) or rounding numbers.

### Figure 3

This section has the BF tables corresponding the Figure 3 in the manuscript.

Table  2. Treatment contrasts for D~V10~. Bayes Factor is used to test pairwise treatment contrasts. This table represents figure 3A in the manuscript

|Parameter              |  Mean |   SD |         95% CI |     Bayes Factor
|----------------------|-------|------|----------------|-------|
DRA-AIXR vs AIXR  |  0.14 | 0.04 | [ 0.07,  0.21] |   4.11
DRA-AIXR vs DRA-TTI     | -0.71 | 0.04 | [-0.79, -0.64] | > 1000
DRA-AIXR vs TTI   | -0.49 | 0.04 | [-0.56, -0.41] | > 1000
DRA-AIXR vs DRA-ULD     | -0.23 | 0.04 | [-0.30, -0.15] | 765.49
DRA-AIXR vs ULD   |  0.10 | 0.04 | [ 0.03,  0.18] |  0.115
AIXR vs DRA-TTI   | -0.86 | 0.04 | [-0.93, -0.79] | > 1000
AIXR vs TTI | -0.63 | 0.04 | [-0.71, -0.56] | > 1000
AIXR vs DRA-ULD   | -0.37 | 0.04 | [-0.45, -0.30] | 224.41
AIXR vs ULD | -0.04 | 0.04 | [-0.11,  0.03] |  0.009
DRA-TTI vs TTI    |  0.23 | 0.04 | [ 0.16,  0.30] |  90.53
DRA-TTI vs DRA-ULD      |  0.49 | 0.04 | [ 0.41,  0.56] | > 1000
DRA-TTI vs ULD    |  0.82 | 0.04 | [ 0.74,  0.89] | > 1000
TTI vs DRA-ULD    |  0.26 | 0.04 | [ 0.19,  0.34] | 265.14
TTI vs ULD  |  0.59 | 0.04 | [ 0.52,  0.67] | > 1000
DRA-ULD vs ULD    |  0.33 | 0.04 | [ 0.25,  0.40] | > 1000

Table  3. Treatment contrasts for D~V50~. Bayes Factor is used to test pairwise treatment contrasts. This table represents figure 3A in the manuscript

Parameter              |  Mean |   SD |         95% CI |     BF
-----------------------|-------|------|----------------|-------|
DRA-AIXR vs DRA-TTI     | -0.60 | 0.04 | [-0.67, -0.53] | > 1000
DRA-AIXR vs DRA-ULD     | -0.19 | 0.04 | [-0.26, -0.12] | 102.08
DRA-AIXR vs AIXR  |  0.19 | 0.04 | [ 0.12,  0.26] |  34.92
DRA-AIXR vs TTI   | -0.42 | 0.04 | [-0.49, -0.34] | > 1000
DRA-AIXR vs ULD   |  0.14 | 0.04 | [ 0.06,  0.21] |  0.451
DRA-TTI vs DRA-ULD      |  0.41 | 0.04 | [ 0.33,  0.48] | > 1000
DRA-TTI vs AIXR   |  0.79 | 0.04 | [ 0.72,  0.86] | > 1000
DRA-TTI vs TTI    |  0.18 | 0.04 | [ 0.11,  0.26] |  12.54
DRA-TTI vs ULD    |  0.74 | 0.04 | [ 0.66,  0.80] | > 1000
DRA-ULD vs AIXR   |  0.38 | 0.04 | [ 0.31,  0.45] | > 1000
DRA-ULD vs TTI    | -0.22 | 0.04 | [-0.30, -0.15] |  29.85
DRA-ULD vs ULD    |  0.33 | 0.04 | [ 0.26,  0.40] | > 1000
AIXR vs TTI | -0.60 | 0.04 | [-0.67, -0.53] | > 1000
AIXR vs ULD | -0.05 | 0.04 | [-0.13,  0.02] |  0.011
TTI vs ULD  |  0.55 | 0.04 | [ 0.48,  0.62] | > 1000

Table 4. Treatment contrasts for D~V90~. Bayes Factor is used to test pairwise treatment contrasts. This table represents figure 3A in the manuscript

Parameter              |  Mean |   SD |         95% CI |     BF
-----------------------|-------|------|----------------|-------|
DRA-AIXR vs DRA-TTI     | -0.51 | 0.04 | [-0.59, -0.44] | > 1000
DRA-AIXR vs DRA-ULD     | -0.16 | 0.04 | [-0.23, -0.09] |   5.25
DRA-AIXR vs AIXR  |  0.24 | 0.04 | [ 0.17,  0.32] | > 1000
DRA-AIXR vs TTI   | -0.34 | 0.04 | [-0.41, -0.26] | > 1000
DRA-AIXR vs ULD   |  0.09 | 0.04 | [ 0.02,  0.17] |  0.049
DRA-TTI vs DRA-ULD      |  0.35 | 0.04 | [ 0.27,  0.42] | > 1000
DRA-TTI vs AIXR   |  0.75 | 0.04 | [ 0.68,  0.83] | > 1000
DRA-TTI vs TTI    |  0.17 | 0.04 | [ 0.10,  0.25] |   4.42
DRA-TTI vs ULD    |  0.60 | 0.04 | [ 0.53,  0.67] | > 1000
DRA-ULD vs AIXR   |  0.40 | 0.04 | [ 0.33,  0.47] | > 1000
DRA-ULD vs TTI    | -0.18 | 0.04 | [-0.24, -0.10] |   4.14
DRA-ULD vs ULD    |  0.25 | 0.04 | [ 0.17,  0.32] | 101.19
AIXR vs TTI | -0.58 | 0.04 | [-0.66, -0.51] | > 1000
AIXR vs ULD | -0.15 | 0.04 | [-0.23, -0.08] |   1.30
TTI vs ULD  |  0.43 | 0.04 | [ 0.36,  0.50] | > 1000

Table 5. Treatment contrasts for relative span. Bayes Factor is used to test pairwise treatment contrasts. This table represents figure 3B in the manuscript

Parameter              |  Mean |   SD |         95% CI |    BF
-----------------------|-------|------|----------------|-------|
DRA-AIXR vs DRA-TTI     |  0.20 | 0.04 | [ 0.13,  0.27] | 26.20
DRA-AIXR vs DRA-ULD     |  0.07 | 0.04 | [ 0.00,  0.14] | 0.009
DRA-AIXR vs AIXR  |  0.11 | 0.04 | [ 0.04,  0.19] | 0.579
DRA-AIXR vs TTI   |  0.15 | 0.04 | [ 0.09,  0.23] | 0.434
DRA-AIXR vs ULD   | -0.05 | 0.04 | [-0.12,  0.02] | 0.001
DRA-TTI vs DRA-ULD      | -0.14 | 0.04 | [-0.20, -0.06] | 0.154
DRA-TTI vs AIXR   | -0.09 | 0.04 | [-0.16, -0.02] | 0.036
DRA-TTI vs TTI    | -0.05 | 0.04 | [-0.12,  0.02] | 0.011
DRA-TTI vs ULD    | -0.25 | 0.04 | [-0.32, -0.18] | 32.47
DRA-ULD vs AIXR   |  0.04 | 0.04 | [-0.03,  0.12] | 0.002
DRA-ULD vs TTI    |  0.09 | 0.04 | [ 0.01,  0.16] | 0.005
DRA-ULD vs ULD    | -0.11 | 0.04 | [-0.18, -0.04] | 0.329
AIXR vs TTI |  0.04 | 0.04 | [-0.03,  0.12] | 0.005
AIXR vs ULD | -0.16 | 0.04 | [-0.23, -0.08] | 0.569
TTI vs ULD  | -0.20 | 0.04 | [-0.27, -0.12] |  1.92

Table 6. Treatment contrasts for % driftable fines < 200 µm. Bayes Factor is used to test pairwise treatment contrasts. This table represents figure 3C in the manuscript

Parameter              |  Mean |   SD |         95% CI |     BF
-----------------------|-------|------|----------------|-------|
DRA-AIXR vs DRA-TTI     |  2.38 | 0.33 | [ 1.74,  3.03] | > 1000
DRA-AIXR vs DRA-ULD     |  0.66 | 0.19 | [ 0.26,  1.00] |   2.72
DRA-AIXR vs AIXR  | -0.45 | 0.14 | [-0.75, -0.19] |   3.53
DRA-AIXR vs TTI   |  1.57 | 0.26 | [ 1.07,  2.09] |  89.16
DRA-AIXR vs ULD   | -0.27 | 0.15 | [-0.59,  0.02] |  0.015
DRA-TTI vs DRA-ULD      | -1.73 | 0.35 | [-2.40, -1.05] |  34.33
DRA-TTI vs AIXR   | -2.83 | 0.33 | [-3.45, -2.18] | > 1000
DRA-TTI vs TTI    | -0.81 | 0.36 | [-1.52, -0.09] |  0.404
DRA-TTI vs ULD    | -2.66 | 0.32 | [-3.25, -1.97] | > 1000
DRA-ULD vs AIXR   | -1.10 | 0.18 | [-1.44, -0.73] | 865.69
DRA-ULD vs TTI    |  0.91 | 0.28 | [ 0.40,  1.48] |  0.598
DRA-ULD vs ULD    | -0.93 | 0.18 | [-1.29, -0.58] | 390.26
AIXR vs TTI |  2.01 | 0.25 | [ 1.55,  2.54] | > 1000
AIXR vs ULD |  0.17 | 0.13 | [-0.09,  0.44] |  0.008
TTI vs ULD  | -1.84 | 0.25 | [-2.34, -1.37] | > 1000

### Figure 4

This section has the BF tables corresponding the Figure 4 in the manuscript.

Table 7. Treatment contrasts for spray droplet deposition in-swath. Bayes Factor is used to test pairwise treatment contrasts. This table represents figure 4 in the manuscript

Parameter                         |    Mean |    SD |             95% CI |     BF
----------------------------------|--------|------|------------------|-------|
DRA-Hood-AIXR vs DRA-Hood-TTI  |   -1.44 | 21.01 | [ -45.09,   45.07] |  0.794
DRA-Hood-AIXR vs DRA-Hood-ULD  |  -15.97 | 27.44 | [ -85.43,   24.72] |  0.754
DRA-Hood-AIXR vs DRA-Open-AIXR | -215.26 | 44.73 | [-298.79, -123.68] | > 1000
DRA-Hood-AIXR vs DRA-Open-TTI  | -186.40 | 46.99 | [-277.66,  -93.77] | 634.87
DRA-Hood-AIXR vs DRA-Open-ULD  | -325.08 | 44.87 | [-413.96, -239.35] | > 1000
DRA-Hood-AIXR vs Hood-AIXR     |   -5.27 | 25.44 | [ -64.64,   50.17] |  0.758
DRA-Hood-AIXR vs Hood-TTI      | -156.91 | 61.20 | [-265.01,  -16.18] |  14.74
DRA-Hood-AIXR vs Hood-ULD      |  -91.58 | 62.35 | [-201.17,    9.32] |   2.33
DRA-Hood-AIXR vs Open-AIXR     |   39.76 | 49.63 | [ -24.16,  145.93] |   1.24
DRA-Hood-AIXR vs Open-TTI      |   26.24 | 41.40 | [ -27.06,  126.79] |  0.466
DRA-Hood-AIXR vs Open-ULD      |   84.50 | 61.48 | [ -12.00,  194.84] |   2.76
DRA-Hood-TTI vs DRA-Hood-ULD   |  -14.53 | 31.54 | [ -86.24,   42.22] |  0.582
DRA-Hood-TTI vs DRA-Open-AIXR  | -213.82 | 44.48 | [-297.30, -126.39] | > 1000
DRA-Hood-TTI vs DRA-Open-TTI   | -184.96 | 46.84 | [-280.66,  -97.81] | 826.26
DRA-Hood-TTI vs DRA-Open-ULD   | -323.64 | 45.12 | [-411.79, -237.53] | > 1000
DRA-Hood-TTI vs Hood-AIXR      |   -3.83 | 30.80 | [ -68.17,   59.57] |  0.558
DRA-Hood-TTI vs Hood-TTI       | -155.47 | 60.45 | [-271.17,  -25.40] |  15.50
DRA-Hood-TTI vs Hood-ULD       |  -90.14 | 61.48 | [-203.15,   18.42] |   2.23
DRA-Hood-TTI vs Open-AIXR      |   41.20 | 49.76 | [ -32.65,  150.27] |  0.862
DRA-Hood-TTI vs Open-TTI       |   27.68 | 43.17 | [ -51.08,  121.26] |  0.411
DRA-Hood-TTI vs Open-ULD       |   85.94 | 60.36 | [ -15.99,  199.57] |   2.16
DRA-Hood-ULD vs DRA-Open-AIXR  | -199.29 | 46.68 | [-286.98, -106.17] | 880.98
DRA-Hood-ULD vs DRA-Open-TTI   | -170.43 | 48.45 | [-270.63,  -81.11] | 219.31
DRA-Hood-ULD vs DRA-Open-ULD   | -309.11 | 47.02 | [-400.98, -216.78] | > 1000
DRA-Hood-ULD vs Hood-AIXR      |   10.70 | 34.60 | [ -55.47,   91.69] |  0.622
DRA-Hood-ULD vs Hood-TTI       | -140.94 | 61.83 | [-254.13,   -8.62] |  11.30
DRA-Hood-ULD vs Hood-ULD       |  -75.61 | 61.82 | [-197.84,   27.93] |   1.47
DRA-Hood-ULD vs Open-AIXR      |   55.73 | 51.24 | [ -24.48,  159.61] |   1.39
DRA-Hood-ULD vs Open-TTI       |   42.21 | 45.78 | [ -27.83,  140.73] |  0.530
DRA-Hood-ULD vs Open-ULD       |  100.47 | 61.30 | [ -12.54,  210.22] |   3.26
DRA-Open-AIXR vs DRA-Open-TTI  |   28.86 | 53.19 | [ -70.04,  137.77] |   1.29
DRA-Open-AIXR vs DRA-Open-ULD  | -109.82 | 52.36 | [-215.70,   -9.56] |  11.11
DRA-Open-AIXR vs Hood-AIXR     |  209.99 | 47.84 | [ 112.79,  298.86] | > 1000
DRA-Open-AIXR vs Hood-TTI      |   58.36 | 63.51 | [ -56.37,  189.54] |   2.10
DRA-Open-AIXR vs Hood-ULD      |  123.69 | 63.17 | [  -0.92,  242.85] |   9.00
DRA-Open-AIXR vs Open-AIXR     |  255.03 | 56.19 | [ 148.51,  368.25] | > 1000
DRA-Open-AIXR vs Open-TTI      |  241.50 | 51.29 | [ 142.56,  343.39] | > 1000
DRA-Open-AIXR vs Open-ULD      |  299.77 | 63.04 | [ 180.75,  420.52] | > 1000
DRA-Open-TTI vs DRA-Open-ULD   | -138.68 | 52.65 | [-248.46,  -39.66] |  47.27
DRA-Open-TTI vs Hood-AIXR      |  181.13 | 49.42 | [  77.25,  272.71] | 310.87
DRA-Open-TTI vs Hood-TTI       |   29.50 | 63.67 | [ -85.35,  166.03] |   1.24
DRA-Open-TTI vs Hood-ULD       |   94.82 | 64.25 | [ -30.23,  212.72] | > 1000
DRA-Open-TTI vs Open-AIXR      |  226.16 | 57.98 | [ 119.40,  347.49] | > 1000
DRA-Open-TTI vs Open-TTI       |  212.64 | 53.25 | [ 111.92,  319.67] | 827.50
DRA-Open-TTI vs Open-ULD       |  270.91 | 66.16 | [ 144.87,  392.34] | > 1000
DRA-Open-ULD vs Hood-AIXR      |  319.81 | 47.51 | [ 223.23,  407.05] | > 1000
DRA-Open-ULD vs Hood-TTI       |  168.17 | 63.27 | [  40.86,  289.99] |  51.22
DRA-Open-ULD vs Hood-ULD       |  233.50 | 63.76 | [ 113.05,  353.87] | 534.21
DRA-Open-ULD vs Open-AIXR      |  364.84 | 55.84 | [ 262.96,  480.54] | > 1000
DRA-Open-ULD vs Open-TTI       |  351.32 | 52.07 | [ 245.37,  449.40] | > 1000
DRA-Open-ULD vs Open-ULD       |  409.58 | 65.10 | [ 292.63,  537.36] | > 1000
Hood-AIXR vs Hood-TTI          | -151.63 | 61.89 | [-263.92,  -15.08] |  11.29
Hood-AIXR vs Hood-ULD          |  -86.31 | 63.67 | [-205.70,   23.84] |   2.14
Hood-AIXR vs Open-AIXR         |   45.04 | 51.35 | [ -30.75,  158.70] |   1.09
Hood-AIXR vs Open-TTI          |   31.51 | 45.30 | [ -39.51,  139.25] |  0.527
Hood-AIXR vs Open-ULD          |   89.78 | 62.35 | [ -18.03,  211.02] |   2.41
Hood-TTI vs Hood-ULD           |   65.33 | 73.15 | [ -73.07,  207.01] |   1.86
Hood-TTI vs Open-AIXR          |  196.67 | 67.69 | [  63.51,  329.08] |  54.93
Hood-TTI vs Open-TTI           |  183.15 | 65.15 | [  51.22,  309.26] |  35.40
Hood-TTI vs Open-ULD           |  241.41 | 73.13 | [ 100.86,  383.13] | 386.49
Hood-ULD vs Open-AIXR          |  131.34 | 68.67 | [  -8.10,  250.92] |   7.11
Hood-ULD vs Open-TTI           |  117.82 | 65.76 | [  -7.88,  236.05] |   2.80
Hood-ULD vs Open-ULD           |  176.08 | 73.82 | [  27.35,  314.48] |  30.00
Open-AIXR vs Open-TTI          |  -13.52 | 57.10 | [-136.83,   98.28] |  0.591
Open-AIXR vs Open-ULD          |   44.74 | 65.02 | [ -81.47,  172.33] |   1.49
Open-TTI vs Open-ULD           |   58.27 | 65.17 | [ -57.33,  188.38] |  0.826

### Figure 6

This section has the BF tables corresponding the Figure 6 in the manuscript.

Table 8. Treatment contrasts for area under the curve. Bayes Factor is used to test pairwise treatment contrasts. This table represents the figure 6B in the manuscript

Parameter                         |   Mean |   SD |           95% CI |     BF
----------------------------------|--------|------|------------------|-------|
DRA-Hood-AIXR vs DRA-Hood-TTI  |   8.15 | 6.47 | [ -3.91,  21.29] |  0.605
DRA-Hood-AIXR vs DRA-Hood-ULD  |   7.57 | 6.32 | [ -3.75,  20.51] |  0.615
DRA-Hood-AIXR vs DRA-Open-AIXR | -50.83 | 6.61 | [-63.81, -38.02] | > 1000
DRA-Hood-AIXR vs DRA-Open-TTI  |  -5.98 | 5.50 | [-16.38,   5.44] |  0.474
DRA-Hood-AIXR vs DRA-Open-ULD  | -11.53 | 6.20 | [-23.68,   0.16] |   1.61
DRA-Hood-AIXR vs Hood-AIXR     |  -9.79 | 6.92 | [-23.85,   2.94] |  0.930
DRA-Hood-AIXR vs Hood-TTI      |  -5.56 | 6.35 | [-18.71,   6.73] |  0.391
DRA-Hood-AIXR vs Hood-ULD      |  -9.20 | 6.83 | [-23.31,   3.17] |  0.983
DRA-Hood-AIXR vs Open-AIXR     | -65.79 | 7.87 | [-81.46, -50.03] | > 1000
DRA-Hood-AIXR vs Open-TTI      | -18.55 | 7.86 | [-34.12,  -4.28] |  12.59
DRA-Hood-AIXR vs Open-ULD      | -51.21 | 7.94 | [-67.21, -35.70] | > 1000
DRA-Hood-TTI vs DRA-Hood-ULD   |  -0.58 | 7.26 | [-15.42,  13.16] |  0.166
DRA-Hood-TTI vs DRA-Open-AIXR  | -58.98 | 7.30 | [-74.22, -45.43] | > 1000
DRA-Hood-TTI vs DRA-Open-TTI   | -14.13 | 6.97 | [-27.64,  -0.10] |   1.31
DRA-Hood-TTI vs DRA-Open-ULD   | -19.68 | 7.30 | [-33.93,  -5.44] |   4.21
DRA-Hood-TTI vs Hood-AIXR      | -17.94 | 8.03 | [-33.99,  -2.33] |   2.41
DRA-Hood-TTI vs Hood-TTI       | -13.71 | 7.82 | [-29.19,   1.04] |  0.735
DRA-Hood-TTI vs Hood-ULD       | -17.35 | 8.05 | [-32.54,  -1.96] |   2.38
DRA-Hood-TTI vs Open-AIXR      | -73.94 | 8.58 | [-91.43, -57.94] | > 1000
DRA-Hood-TTI vs Open-TTI       | -26.70 | 8.59 | [-42.28,  -8.55] |  26.84
DRA-Hood-TTI vs Open-ULD       | -59.36 | 8.59 | [-75.66, -42.26] | > 1000
DRA-Hood-ULD vs DRA-Open-AIXR  | -58.39 | 7.34 | [-72.77, -44.18] | > 1000
DRA-Hood-ULD vs DRA-Open-TTI   | -13.55 | 6.82 | [-26.48,  -0.18] |  0.895
DRA-Hood-ULD vs DRA-Open-ULD   | -19.10 | 7.07 | [-32.45,  -4.60] |   5.92
DRA-Hood-ULD vs Hood-AIXR      | -17.36 | 7.88 | [-31.87,  -1.27] |   2.12
DRA-Hood-ULD vs Hood-TTI       | -13.13 | 7.88 | [-29.07,   1.88] |  0.655
DRA-Hood-ULD vs Hood-ULD       | -16.77 | 7.76 | [-30.91,  -1.26] |   2.30
DRA-Hood-ULD vs Open-AIXR      | -73.36 | 8.35 | [-89.24, -56.45] | > 1000
DRA-Hood-ULD vs Open-TTI       | -26.12 | 8.59 | [-43.46,  -9.26] |  16.34
DRA-Hood-ULD vs Open-ULD       | -58.77 | 8.54 | [-75.85, -42.42] | > 1000
DRA-Open-AIXR vs DRA-Open-TTI  |  44.85 | 6.97 | [ 31.76,  58.69] | > 1000
DRA-Open-AIXR vs DRA-Open-ULD  |  39.29 | 7.34 | [ 24.12,  52.80] | > 1000
DRA-Open-AIXR vs Hood-AIXR     |  41.04 | 8.09 | [ 23.42,  55.34] | 845.05
DRA-Open-AIXR vs Hood-TTI      |  45.27 | 7.96 | [ 27.69,  59.61] | > 1000
DRA-Open-AIXR vs Hood-ULD      |  41.63 | 8.05 | [ 25.89,  57.11] | > 1000
DRA-Open-AIXR vs Open-AIXR     | -14.96 | 8.59 | [-32.79,   1.12] |  0.649
DRA-Open-AIXR vs Open-TTI      |  32.28 | 8.50 | [ 15.33,  48.67] |  69.52
DRA-Open-AIXR vs Open-ULD      |  -0.38 | 8.55 | [-16.80,  16.74] |  0.157
DRA-Open-TTI vs DRA-Open-ULD   |  -5.55 | 6.68 | [-18.11,   7.89] |  0.178
DRA-Open-TTI vs Hood-AIXR      |  -3.81 | 7.57 | [-19.14,   9.92] |  0.137
DRA-Open-TTI vs Hood-TTI       |   0.42 | 7.45 | [-14.04,  15.26] |  0.136
DRA-Open-TTI vs Hood-ULD       |  -3.22 | 7.65 | [-18.74,  11.49] |  0.216
DRA-Open-TTI vs Open-AIXR      | -59.81 | 8.37 | [-76.17, -42.91] | > 1000
DRA-Open-TTI vs Open-TTI       | -12.57 | 8.31 | [-28.57,   3.39] |  0.493
DRA-Open-TTI vs Open-ULD       | -45.23 | 8.43 | [-61.65, -29.14] | > 1000
DRA-Open-ULD vs Hood-AIXR      |   1.74 | 7.82 | [-13.25,  17.00] |  0.167
DRA-Open-ULD vs Hood-TTI       |   5.97 | 7.57 | [ -8.61,  20.91] |  0.198
DRA-Open-ULD vs Hood-ULD       |   2.33 | 7.85 | [-12.58,  17.91] |  0.229
DRA-Open-ULD vs Open-AIXR      | -54.26 | 8.55 | [-72.07, -38.83] | > 1000
DRA-Open-ULD vs Open-TTI       |  -7.02 | 8.43 | [-23.39,   9.59] |  0.266
DRA-Open-ULD vs Open-ULD       | -39.67 | 8.46 | [-56.13, -23.26] | 235.20
Hood-AIXR vs Hood-TTI          |   4.23 | 8.11 | [-11.09,  20.13] |  0.143
Hood-AIXR vs Hood-ULD          |   0.59 | 8.43 | [-16.42,  16.69] |  0.192
Hood-AIXR vs Open-AIXR         | -56.00 | 9.17 | [-73.39, -38.37] | > 1000
Hood-AIXR vs Open-TTI          |  -8.76 | 8.84 | [-25.93,   8.44] |  0.255
Hood-AIXR vs Open-ULD          | -41.42 | 8.81 | [-58.48, -23.90] | 171.06
Hood-TTI vs Hood-ULD           |  -3.64 | 8.24 | [-19.70,  12.48] |  0.204
Hood-TTI vs Open-AIXR          | -60.23 | 8.74 | [-77.71, -43.38] | > 1000
Hood-TTI vs Open-TTI           | -12.99 | 8.71 | [-30.18,   4.14] |  0.557
Hood-TTI vs Open-ULD           | -45.65 | 8.69 | [-62.48, -28.60] | > 1000
Hood-ULD vs Open-AIXR          | -56.59 | 8.98 | [-75.74, -40.10] | > 1000
Hood-ULD vs Open-TTI           |  -9.35 | 9.05 | [-26.98,   8.48] |  0.443
Hood-ULD vs Open-ULD           | -42.01 | 8.86 | [-59.38, -24.73] | 287.61
Open-AIXR vs Open-TTI          |  47.24 | 9.29 | [ 28.97,  65.17] | > 1000
Open-AIXR vs Open-ULD          |  14.59 | 9.29 | [ -2.80,  33.29] |  0.445
Open-TTI vs Open-ULD           | -32.66 | 9.26 | [-49.69, -13.41] |  27.60

## References

- Lee M.D. and Wagenmakers E.J. (2014) Bayesian Cognitive Modeling: A Practical Course. Cambridge University Press. ISBN: 9781107018457, 1107018455

### 2021-08-31 analysis/combined.Rmd
nbn

@@
   labs(x = NULL, 
-       y = expression(paste("Spray particle deposition (\u03B7L/cm"^"2",")"))
+       y = expression(paste("In-swath spray deposition  (\u03B7L/cm"^"2",")"))
        ) +
@@
   theme_few() +
-  geom_text(data = loc, mapping = aes(x = 10, y = 20), 
-            label = "Intercept", inherit.aes = FALSE, size = 10) +
-  geom_text(data = loc, mapping = aes(x = 55, y = 10), 
-            label = "Slope", inherit.aes = FALSE, size = 10) +
+#  geom_text(data = loc, mapping = aes(x = 10, y = 20), 
+#            label = "Intercept", inherit.aes = FALSE, size = 10) +
+#  geom_text(data = loc, mapping = aes(x = 55, y = 10), 
+##            label = "Slope", inherit.aes = FALSE, size = 10) +
   geom_label(aes(label = formula), x = 30, y = 15, color = "white", size = 12) +
-  geom_curve(data = loc, mapping = aes(x = 25, y = 17,
-             xend = 20, yend = 20),
-             arrow = arrow(length = unit(0.07, "inch")), 
-             color = 1,
-             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
-  geom_curve(data = loc, mapping = aes(x = 42, y = 13,
-             xend = 47, yend = 10),
-             arrow = arrow(length = unit(0.07, "inch")), 
-             color = 1,
-             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
+#  geom_curve(data = loc, mapping = aes(x = 25, y = 17,
+#             xend = 20, yend = 20),
+#             arrow = arrow(length = unit(0.07, "inch")), 
+#             color = 1,
+#             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
+#  geom_curve(data = loc, mapping = aes(x = 42, y = 13,
+#             xend = 47, yend = 10),
+#             arrow = arrow(length = unit(0.07, "inch")), 
+#             color = 1,
+#             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
   labs(x = "Distance (m)", 
@@
         axis.text = element_markdown(size = 25)) -> figE
-figE
+#figE
+
+ggsave("Figure 3.png", width = 5, height = 4)
 ```
+
 ```{r}
@@
 ```{r}
-c + figE +
-  plot_annotation(tag_levels = 'A') & 
-  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0)) -> figU
+#c + figE +
+#  plot_annotation(tag_levels = 'A') & 
+#  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0)) -> figU
 
-ggsave("Figure 3.png", width = 8, height = 4)
+#ggsave("Figure 3.png", width = 8, height = 4)
 ```

### 2021-09-01 supp_file/supplemental_file.Rmd
,m

@@
 | 3 – 10       	| Moderate evidence for H~1~    	|
-| 1 – 3        	| Anecdotal evidence for H~0~    	|
+| 1 – 3        	| Anecdotal evidence for H~1~    	|
 | 1            	| No evidence                  	|

### 2021-10-20 analysis/combined.Rmd
as

@@
 params %>% 
-
   pivot_wider(id_cols = trt,
@@
 ```{r}
+library(tidyverse)
 fig2 <- fig1 %>% 
